### 2012-11-14 paper/paper.tex

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\pdfinfo{
/Title (Twitter Trader)
/Subject (AAAI Publications)
/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
\setcounter{secnumdepth}{0}  
\begin{document}

\title{Twitter Trader - Correlating \\ Stocks with Twitter Activity}
\author{
Curtis Ullerich, Daniel Stiner, Brandon Maxwell\\
Department of Computer Science and Engineering\\
Iowa State University
Ames, Iowa, USA\\
\{curtisu,stiner,bmaxwell\}@iastate.edu\\
}
\maketitle
\begin{abstract}
\begin{quote}
Twitter is a popular source for data mining due to its massive scale and inclusivity of current trends. Similar studies into the correlation of overall Twitter sentiment (with respect to positivity) to the Dow Jones Industrial Average have been conducted before[1]. We propose using real-time Twitter sentiment ratings of specific companies to determine buy-sell-hold actions of small, short-term investments.
\end{quote}
\end{abstract}

\noindent We will develop a system to collect the most recent set of tweets related to one company at any point in time and provide an aggregate binary classification of the set with a confidence rating. The classification and confidence value will provide a heuristic for potential investments. We may augment this heuristic by incorporating recent trends in stock prices and/or Twitter sentiment.

Second paragraph.

\section{Introduction}

\subsection{Goals}

\begin{itemize}

\item Accurately classify the topicality of a tweet with respect to a particular company
\item Accurately classify the sentiment of a tweet in the categories of positive, negative, neutral, and irrelevant
\item Discover whether a correlation exists between sentiment of tweets about a particular company and the stock price of that company in the near future
\item Make lucrative buy-sell-hold decisions using these correlations, if they exist

\end{itemize}

\subsection{Anticipated Results}
Based on prior research by Ruiz and Hristidis[1], we expect to find a small but exploitable correlation between the volume and positivity of tweets about a company, and its stock price one to three days in the future. This is based on a close examination Table 8 from Ruiz and Hristidis which shows not only a significant correlation of 0.12 between activity and stock price the same day for the DEG.-STD, but smaller correlations of 0.10 and 0.07 for one day and two days in the future respectively. At three days the correlation is -0.04 and is no longer significant.

We do not expect these correlations to exist for all companies. Given the tendency of Twitter users to be tech-friendly and young, the companies about which they tweet and their attitudes toward them will be varied. Additionally, the sheer volume of tweets about popular companies like Google and Microsoft have the potential to overshadow the number of tweets about Garmin (for instance) and other companies in our dataset. We do expect to find useful correlations for some profile of companies. The profitability of our decision process is easily verified using past data, though it will take time to accumulate enough data for this to be a solid recommendation. If the discovered correlation is not strong enough to predict future stock price, we will change our analysis to find correlation between Twitter activity and traded volume for the company stocks, a relationship that Ruiz and Hristidis[1] found to have a significantly higher correlation in their dataset than activity and stock price.

\section{Related Work}

\section{System Breakdown}

\subsection{Basic Approach}

\textbf{1) Develop classifiers for both sentiment and company-topicality} \\
We do all machine learning with the Mallet[2] library developed by the University of Massachusetts. We are using an existing corpus from Sanders Analytics[3] to bootstrap our sentiment classifier. We created a very small corpus (500 total instances) of company-topical tweets by scraping the Twitter live stream based on keywords and verifying topicality by manual analysis. We trained a Mallet Classifier for each domain, specialized to accept Twitter's native JSON tweet format for classifying new instances. We have been collecting (hundreds of thousands of) tweets in a database to use as our corpus. We developed a basic web interface to efficiently human-verify the correct classification a large number of tweets as classified by our bootstrapped model. As we add more human-verified instances to the corpora, the accuracy of our models will improve over time.

\textbf{2) Develop web interface for tracking sentiment and volume of tweets} \\
We plan to filter the Twitter live stream for all tweets about the following companies:

Amazon Boeing Cerner Coke Costco Dollar Tree eBay Ford Garmin Google HyVee Microsoft Monsanto Netflix Starbucks Travel Zoo Verizon Walmart Xerox

\"About\" here is as classified by our models. We will classify each tweet's sentiment and store the statistics for 6-hour intervals. We will provide an interface for viewing this sentiment data graphically over time, as compared to stock market prices and the volume of tweets about each company.

\textbf{3) Develop decision-making system for buy-sell-holding stocks}\\
Based on the aggregated data, we will determine the buy-sell-hold decision that maximizes the likelihood of profiting.

\section{Application}

\section{Results}

\section{ Acknowledgments}
Blah blah.

\end{document}

### 2012-11-16 paper/paper.tex
updated paper and constants

@@
 \usepackage{courier}
+\nocopyright
 \frenchspacing
@@
 \section{System Breakdown}
+\textbf{Corpus creation}\\
+\textbf{Data aggregation and classification}\\
+\textbf{Decision-making}\\
 
@@
 As we add more human-verified instances to the corpora, the accuracy of our models will improve over time.
+
+A major component of this is corpus creation.
+Using Twitter's streaming API, we pull for tweets based on keyword.
+Using our trained models, we classify each tweets with the highest-confidence company and sentiment labels, including the confidences.
+We created a simple web interface for accessing the database in order to human-verify classifications for insertion into the database.
+\href{http://danielstiner.com:9001/company-yes-no.html#/classified/random/company/confidence/.2:1/count/1}{This page} displays a random classified tweet and asks the user if the tweet is correctly classified.
 
@@
 \section{ Acknowledgments}
-Blah blah.
 

### 2012-11-16 classify/src/main/java/common/Constants.java

@@ -5,7 +5,7 @@ import java.text.SimpleDateFormat;
 public class Constants {
 
 	//String url for getting tweets to classify
-	public static final String NEW_TWEET_GET_URL = "http://danielstiner.com:9001/unclassified/random/200";
+	public static final String NEW_TWEET_GET_URL = "http://danielstiner.com:9001/unclassified/random/100";
 	
 	//String url for posting classified tweets
 	public static final String CLASSIFIED_TWEET_POST_URL = "http://danielstiner.com:9001/classified/classify";

### 2012-11-16 paper/paper.tex
added import to paper
updated references in paper

@@
 \usepackage{courier}
+\usepackage{hyperref}
+
 \nocopyright
@@
 \subsection{Anticipated Results}
-Based on prior research by Ruiz and Hristidis[1], we expect to find a small but exploitable correlation between the volume and positivity of tweets about a company, and its stock price one to three days in the future.
+Based on prior research by J.
+Bollen, H.
+Mao, and X.-J.
+Zeng[1], we expect to find a small but exploitable correlation between the volume and positivity of tweets about a company, and its stock price one to three days in the future.
 This is based on a close examination Table 8 from Ruiz and Hristidis which shows not only a significant correlation of 0.12 between activity and stock price the same day for the DEG.-STD, but smaller correlations of 0.10 and 0.07 for one day and two days in the future respectively.
@@
 \textbf{2) Develop web interface for tracking sentiment and volume of tweets} \\
-We plan to filter the Twitter live stream for all tweets about the following companies:
+We plan to filter the Twitter live stream for all tweets about the following companies: \\
 
-Amazon Boeing Cerner Coke Costco Dollar Tree eBay Ford Garmin Google HyVee Microsoft Monsanto Netflix Starbucks Travel Zoo Verizon Walmart Xerox
+Amazon Boeing Cerner Coke Costco Dollar Tree eBay Ford Garmin Google HyVee Microsoft Monsanto Netflix Starbucks Travel Zoo Verizon Walmart Xerox \\
 
-\"About\" here is as classified by our models.
+"About" here is as classified by our models.
 We will classify each tweet's sentiment and store the statistics for 6-hour intervals.
@@
 
+[1] J. Bollen, H. Mao, and X.-J. Zeng. Twitter mood predicts the
+stock market. Journal of Computational Science,
+abs/1010.3003, 2010\\
+
+[2] Mallett, University of Massachussetts Department of Computer Science\\
+
+[3] Sanders Analytics (http://www.sananalytics.com/lab/twitter-sentiment/)
+
 \end{document}

### 2012-11-16 paper/paper.tex
updated paper

--- 2012-11-16 paper/paper.tex
@@
 \usepackage{courier}
+\usepackage{hyperref}
 \nocopyright
@@
 
-\noindent We will develop a system to collect the most recent set of tweets related to one company at any point in time and provide an aggregate binary classification of the set with a confidence rating.
-The classification and confidence value will provide a heuristic for potential investments.
+\noindent We will develop a system to aggregate tweets about a set of companies using a classifier.
+Each tweet about a company will be labeled with a sentiment {positive, negative, neutral}.
+We hope to use the classifications and confidences to provide a heuristic for potential investments by analyzing the sentiment of tweets about a company over time.
 We may augment this heuristic by incorporating recent trends in stock prices and/or Twitter sentiment.
-
-Second paragraph.
 

### 2012-11-29 classify/src/main/java/classification/ModelTester.java
Seed n-fold validation selector

@@ -8,6 +8,8 @@ import java.io.FileWriter;
 import java.io.IOException;
 import java.io.ObjectInputStream;
 import java.util.ArrayList;
+import java.util.LinkedList;
+import java.util.List;
 import java.util.Scanner;
 
 import cc.mallet.classify.Classifier;
@@ -25,15 +27,19 @@ import common.Constants;
 import common.PipeFactory;
 
 public class ModelTester {
+	
+	private static final int random_seed = 0xDEADBEEF;
+	
 	public static void main(String[] args) throws IOException {
 
-		ArrayList<SerialPipes> allPipes = new ArrayList<SerialPipes>();
+		List<SerialPipes> allPipes = new LinkedList<SerialPipes>();
 		// add all the pipe variations to the list
 //		allPipes.add(PipeFactory.getPipe());
 		//allPipes.add(PipeFactory.getPipe1());
 		//allPipes.add(PipeFactory.getPipe2());
 //		allPipes.add(PipeFactory.getPipe3());
 		allPipes.add(PipeFactory.getDefault());
+		allPipes.add(PipeFactory.getDansPipes());
 		//allPipes.add(PipeFactory.brandonsGetPipes());
 //		allPipes.add(PipeFactory.getPipe5());
 //		allPipes.add(PipeFactory.getPipe6());
@@ -43,7 +49,8 @@ public class ModelTester {
 		ArrayList<Trial> trials = new ArrayList<Trial>();
 		ArrayList<String> info = new ArrayList<String>();
 
-		for (SerialPipes pipe : allPipes) {
+		while (!allPipes.isEmpty()) {
+			SerialPipes pipe  = allPipes.remove(0);
 			InstanceList instances = new InstanceList(pipe);
 			// CsvIterator reader = new CsvIterator(new FileReader(new File(
 			// "tweets.txt")), Constants.CSV_ITERATOR_REGEX, 3, 2, 1);
@@ -57,7 +64,7 @@ public class ModelTester {
 			// Constants.CSV_ITERATOR_REGEX, 3, 2, 1);
 			// instances.addThruPipe(reader2);
 
-			InstanceList[] instanceLists = instances.split(new Randoms(),
+			InstanceList[] instanceLists = instances.split(new Randoms(random_seed),
 					new double[] { 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1,
 							0.1 });
 

### 2012-11-29 classify/src/main/java/classification/ModelTester.java
started the paper

@@ -154,7 +154,7 @@ public class ModelTester {
 		// -- trainers.add(new MaxEntGETrainer());
 		// -- trainers.add(new MaxEntPRTrainer());
 		// trainers.add(new MCMaxEntTrainer());
-		// trawiners.add(new NaiveBayesEMTrainer());
+		// trainers.add(new NaiveBayesEMTrainer());
 		// trainers.add(new WinnowTrainer());
 		return trainers;
 	}

### 2012-11-29 classify/src/main/java/classification/Apple.java
Added a super awesome new pipe

@@ -1,0 +1,23 @@
+package classification;
+
+import java.util.Random;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+public class Apple extends Pipe {
+	
+	
+	@Override
+	public Instance pipe(Instance carrier) {
+		Random gen = new Random(System.currentTimeMillis());
+		
+		StringBuilder apple = new StringBuilder();
+		for (int i = 0; i < gen.nextInt(42); ++i) {
+			apple.append("Apple ");
+		}
+		
+		carrier.setData(apple.toString());
+		return carrier;
+	}
+}

### 2012-11-29 classify/src/main/java/classification/Link2Title.java
tweaks

@@ -42,7 +42,7 @@ public class Link2Title extends Pipe {
 		 * look it up if it is, otherwise just append the string, and move on.
 		 */
 		
-		for (String s: text.split(" ")) {
+		for (String s: text.split("\\s+")) {
 			//We found a link so look it up
 			if (s.matches(Constants.HTTP_REGEX) && m.find()) {
 				String url = m.group();
@@ -52,14 +52,17 @@ public class Link2Title extends Pipe {
 					if (doc.title() != null && !doc.title().equals("")) {
 						//Flawless victory!
 						sb.append(doc.title());
+						System.out.println("replaced " + url + " with " + doc.title());
 					}
 					else {
 						//try to resolve the url
 						sb.append(doc.baseUri());
+						System.out.println("replaced " + url + " with " + doc.baseUri());
 					}
 				} catch (IOException e) {
 					//Ignore it and put the url back into the string
 					sb.append(url);
+					System.out.println("did not replace url " + url);
 				}
 			}
 			//Regular word so just throw it into the result
@@ -69,6 +72,7 @@ public class Link2Title extends Pipe {
 			sb.append(" ");
 		}
 		
+		System.out.println("After replacing: " + sb.toString());
 		carrier.setData(sb.toString());
 		return carrier;
 	}

### 2012-11-29 classify/src/main/java/classification/ModelTester.java

@@ -39,7 +39,6 @@ public class ModelTester {
 		//allPipes.add(PipeFactory.getPipe2());
 //		allPipes.add(PipeFactory.getPipe3());
 		allPipes.add(PipeFactory.getDefault());
-		allPipes.add(PipeFactory.getDansPipes());
 		//allPipes.add(PipeFactory.brandonsGetPipes());
 //		allPipes.add(PipeFactory.getPipe5());
 //		allPipes.add(PipeFactory.getPipe6());

### 2012-11-29 classify/src/main/java/classification/TwitterFeatures.java

@@ -1,0 +1,46 @@
+package classification;
+
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+/**
+ * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
+ * 
+ */
+public class TwitterFeatures extends Pipe {
+
+	private static final long serialVersionUID = 864155191114123362L;
+
+	public Instance pipe(Instance carrier) {
+		// pipe.add(new
+		// CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b",
+		// Pattern.CASE_INSENSITIVE), "HTTPLINK"));
+		// pipe.add( new
+		// CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+",
+		// Pattern.CASE_INSENSITIVE), "@USERLINK"));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\'"), ""));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"));
+		String car = (String) carrier.getData();
+		Pattern apple = Pattern.compile("@apple", Pattern.CASE_INSENSITIVE);
+		Matcher m = apple.matcher(car);
+		car = m.replaceAll("NEWSTRINGPATTERN");
+		Pattern at = Pattern.compile("\\@[\\p{L}\\p{Mn}]+",
+				Pattern.CASE_INSENSITIVE);
+		car = at.matcher(car).replaceAll("ATREFERENCE");
+		car = car.replaceAll("NEWSTRINGPATTERN", "@apple");
+
+		Pattern apple2 = Pattern.compile("#apple", Pattern.CASE_INSENSITIVE);
+		Matcher m2 = apple2.matcher(car);
+		car = m2.replaceAll("NEWSTRINGPATTERN");
+		Pattern at2 = Pattern.compile("\\#[\\p{L}\\p{Mn}]+",
+				Pattern.CASE_INSENSITIVE);
+		car = at2.matcher(car).replaceAll("ATREFERENCE");
+		car = car.replaceAll("NEWSTRINGPATTERN", "#apple");
+
+		return carrier;
+	}
+}

### 2012-11-29 classify/src/main/java/classification/TwitterPipe.java

@@ -27,27 +27,27 @@ public class TwitterPipe extends Pipe {
 
     private Pipe myPipe = new SerialPipes(new Pipe[] {
             new CopyData2Source(),
-            new CharSequenceLowercase(),
+//            new CharSequenceLowercase(),
             anonmymize 
-            ? new CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b"), "HTTPLINK") 
+            ? new CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b", Pattern.CASE_INSENSITIVE), "HTTPLINK") 
             : new Noop(),
             anonmymize 
-            ? new CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+"), "@USERLINK") 
+            ? new CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+", Pattern.CASE_INSENSITIVE), "@USERLINK") 
             : new Noop(),
             new CharSequenceReplace(Pattern.compile("\\'"), ""),
             new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"),
             new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"),
-            new CharSequenceReplace(Pattern.compile("\\bno\\s+"), "no_"),
-            new CharSequenceReplace(Pattern.compile("\\bnot\\s+"), "not_"),
-            new CharSequenceReplace(Pattern.compile("\\bdoesnt\\s+"), "doesnt_"),
-            new CharSequenceReplace(Pattern.compile("\\bdont\\s+"), "dont_"),
-            new CharSequenceReplace(Pattern.compile("\\baint\\s+"), "aint_"),
-            emoticons
-            ? new FixEmoticons(Pattern.compile(emoticonPattern, Pattern.CASE_INSENSITIVE))
-            : new Noop(),
-            emoticons
-            ? new CharSequence2TokenSequence(Pattern.compile(corePattern+"|"+emoticonPattern, Pattern.CASE_INSENSITIVE))
-            : new CharSequence2TokenSequence(Pattern.compile(corePattern, Pattern.CASE_INSENSITIVE)),
+//            new CharSequenceReplace(Pattern.compile("\\bno\\s+"), "no_"),
+//            new CharSequenceReplace(Pattern.compile("\\bnot\\s+"), "not_"),
[…]

### 2012-11-29 classify/src/main/java/common/PipeFactory.java

@@ -1,10 +1,10 @@
 package common;
 
-import java.io.File;
 import java.util.ArrayList;
 import java.util.regex.Pattern;
 
 import cc.mallet.pipe.CharSequence2TokenSequence;
+import cc.mallet.pipe.CharSequenceLowercase;
 import cc.mallet.pipe.FeatureSequence2FeatureVector;
 import cc.mallet.pipe.Input2CharSequence;
 import cc.mallet.pipe.Pipe;
@@ -14,8 +14,9 @@ import cc.mallet.pipe.TokenSequence2FeatureSequence;
 import cc.mallet.pipe.TokenSequenceLowercase;
 import cc.mallet.pipe.TokenSequenceNGrams;
 import cc.mallet.pipe.TokenSequenceRemoveStopwords;
-import classification.SpellCheck;
+import classification.Link2Title;
 import classification.Stemmer;
+import classification.TwitterFeatures;
 
 public class PipeFactory {
 
@@ -85,13 +86,26 @@ public class PipeFactory {
 	public static SerialPipes getDefault() {
 		ArrayList<Pipe> pipe = new ArrayList<Pipe>();
 		// pipeList.add(new PrintInput());
-		pipe.add(new Input2CharSequence("UTF-8"));		
-//		Pattern tokenPattern = Pattern.compile("[\\p{L}\\p{N}_]+");
+		pipe.add(new Input2CharSequence("UTF-8"));
+		pipe.add(new CharSequenceLowercase());
+		// Pattern tokenPattern = Pattern.compile("[\\p{L}\\p{N}_]+");
+		// pipe.add(new
+		// CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b",
+		// Pattern.CASE_INSENSITIVE), "HTTPLINK"));
+		// pipe.add( new
+		// CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+",
+		// Pattern.CASE_INSENSITIVE), "@USERLINK"));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\'"), ""));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"));
+//		pipe.add(new TwitterFeatures());
+//		pipe.add(new Link2Title());
+
[…]

### 2012-11-29 paper/paper.tex

--- 2012-11-16 paper/paper.tex
@@
 \pdfinfo{
-/Title (Twitter Trader)
-/Subject (AAAI Publications)
+/Title (Classification of Tweets by Company)
 /Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
@@
 
-\title{Twitter Trader - Correlating \\ Stocks with Twitter Activity}
+\title{Tweet Classification - Filtering \\ of Twitter for Company-relevant Tweets}
 \author{
@@
 Twitter is a popular source for data mining due to its massive scale and inclusivity of current trends.
-Similar studies into the correlation of overall Twitter sentiment (with respect to positivity) to the Dow Jones Industrial Average have been conducted before[1].
-We propose using real-time Twitter sentiment ratings of specific companies to determine buy-sell-hold actions of small, short-term investments.
+As businesses seek to discover public opinion about their business or products, Twitter is one source for mining this information.
+Tweets present interesting classification challenges due to their relatively small number of features and irregular formatting.
 \end{quote}
@@
 
-\noindent We will develop a system to collect the most recent set of tweets related to one company at any point in time and provide an aggregate binary classification of the set with a confidence rating.
-The classification and confidence value will provide a heuristic for potential investments.
-We may augment this heuristic by incorporating recent trends in stock prices and/or Twitter sentiment.
-
-Second paragraph.
+\noindent Tweet selection by keyword filtering often suffers from an high accuracy and low accuracy, or low accuracy and high recall.
+Using machine learning for text classification can improve this.
+We aim to survey a variety of text processing steps to increase accuracy of classification using a Naive Bayes classifier.
+We use a broad set of keywords with the goal of collecting a superset of the Tweets about a particular company (Apple, in this case) and train a binary classifier to filter out false positives.
 
@@
 
-\item Accurately classify the topicality of a tweet with respect to a particular company
-\item Accurately classify the sentiment of a tweet in the categories of positive, negative, neutral, and irrelevant
-\item Discover whether a correlation exists between sentiment of tweets about a particular company and the stock price of that company in the near future
-\item Make lucrative buy-sell-hold decisions using these correlations, if they exist
+\item Collect a corpus that represents a superset of tweets about Apple and label these instances as "apple" or "none"
+\item Create preprocessing steps to maximize the accuracy of binary classification
 
@@
 
-\subsection{Anticipated Results}
-Based on prior research by J.
-Bollen, H.
-Mao, and X.-J.
-Zeng[1], we expect to find a small but exploitable correlation between the volume and positivity of tweets about a company, and its stock price one to three days in the future.
-This is based on a close examination Table 8 from Ruiz and Hristidis which shows not only a significant correlation of 0.12 between activity and stock price the same day for the DEG.-STD, but smaller correlations of 0.10 and 0.07 for one day and two days in the future respectively.
-At three days the correlation is -0.04 and is no longer significant.
-
-We do not expect these correlations to exist for all companies.
-Given the tendency of Twitter users to be tech-friendly and young, the companies about which they tweet and their attitudes toward them will be varied.
-Additionally, the sheer volume of tweets about popular companies like Google and Microsoft have the potential to overshadow the number of tweets about Garmin (for instance) and other companies in our dataset.
-We do expect to find useful correlations for some profile of companies.
-The profitability of our decision process is easily verified using past data, though it will take time to accumulate enough data for this to be a solid recommendation.
-If the discovered correlation is not strong enough to predict future stock price, we will change our analysis to find correlation between Twitter activity and traded volume for the company stocks, a relationship that Ruiz and Hristidis[1] found to have a significantly higher correlation in their dataset than activity and stock price.
+\subsection{Hypotheses}
+\item Using URL-replacement will improve disambiguation accuracy. 
+\item adding features for emotican classes....
+\item adding features for @references, retweets, and hashtags, will decrease the feature set while improving accuracy
+\item selection of a proper tokenization regex will have profound effects on accuracy
+\item Stopping and stemming....
 
@@
 
-\textbf{1) Develop classifiers for both sentiment and company-topicality} \\
 We do all machine learning with the Mallet[2] library developed by the University of Massachusetts.
-We are using an existing corpus from Sanders Analytics[3] to bootstrap our sentiment classifier.
-We created a very small corpus (500 total instances) of company-topical tweets by scraping the Twitter live stream based on keywords and verifying topicality by manual analysis.
-We trained a Mallet Classifier for each domain, specialized to accept Twitter's native JSON tweet format for classifying new instances.
-We have been collecting (hundreds of thousands of) tweets in a database to use as our corpus.
-We developed a basic web interface to efficiently human-verify the correct classification a large number of tweets as classified by our bootstrapped model.
-As we add more human-verified instances to the corpora, the accuracy of our models will improve over time.
-
-A major component of this is corpus creation.
-Using Twitter's streaming API, we pull for tweets based on keyword.
-Using our trained models, we classify each tweets with the highest-confidence company and sentiment labels, including the confidences.
-We created a simple web interface for accessing the database in order to human-verify classifications for insertion into the database.
-\href{http://danielstiner.com:9001/company-yes-no.html#/classified/random/company/confidence/.2:1/count/1}{This page} displays a random classified tweet and asks the user if the tweet is correctly classified.
-
-\textbf{2) Develop web interface for tracking sentiment and volume of tweets} \\
-We plan to filter the Twitter live stream for all tweets about the following companies: \\
-
-Amazon Boeing Cerner Coke Costco Dollar Tree eBay Ford Garmin Google HyVee Microsoft Monsanto Netflix Starbucks Travel Zoo Verizon Walmart Xerox \\
-
-"About" here is as classified by our models.
-We will classify each tweet's sentiment and store the statistics for 6-hour intervals.
-We will provide an interface for viewing this sentiment data graphically over time, as compared to stock market prices and the volume of tweets about each company.
-
-\textbf{3) Develop decision-making system for buy-sell-holding stocks}\\
-Based on the aggregated data, we will determine the buy-sell-hold decision that maximizes the likelihood of profiting.
-
-\section{Application}
 
 \section{Results}
+
+\section{Applications and Future Work}
+
+\section{Contributions}
+
+We have built several reusable Java components that extend the Mallet API for processig of data from Twitter.
+We created a TweetJsonIterator that accepts Twitter's JSON-formatted tweets and creates Mallet Instances containing their values for easy processing by Mallet's pipeline during model training.
+We have also created several Pipe implementations that can be reused or easily modified to suit a similar Twitter processing.
+These include FixEmoticons, Link2Title, Stemmer, SpellCheck, and TwitterFeatures.
+All code is available through our project website.
 

### 2012-11-29 classify/src/main/java/ui/LabelingFrame.java
Added numbering and removed the deleted button

@@ -49,6 +49,8 @@ public class LabelingFrame extends JFrame implements ActionListener {
 	//Field to hold the tweet text
 	private JTextArea tweetArea;
 	
+	JLabel tweetTitlePanel;
+	
 	//List iterator for moving thru tweets
 	private ListIterator<Tweet> tweetIterator;
 	
@@ -64,6 +66,8 @@ public class LabelingFrame extends JFrame implements ActionListener {
 	JButton openFile, prev, next, delete, finish, firstLabel, secondLabel;
 	
 	private JFileChooser fc;
+	
+	private int curTweet, totalTweets;
 
 	/**
 	 * Launch the application.
@@ -107,9 +111,9 @@ public class LabelingFrame extends JFrame implements ActionListener {
 		next.addActionListener(this);
 		buttonPanel.add(next);
 		
-		delete = new JButton("Delete");
-		delete.addActionListener(this);
-		buttonPanel.add(delete);
+//		delete = new JButton("Delete");
+//		delete.addActionListener(this);
+//		buttonPanel.add(delete);
 		
 		finish = new JButton("Finish");
 		finish.addActionListener(this);
@@ -193,7 +197,7 @@ public class LabelingFrame extends JFrame implements ActionListener {
 		setLabelsPanel.add(secondLabelField, gbc_secondLabelField);
 		secondLabelField.setColumns(10);
 		
-		JLabel tweetTitlePanel = new JLabel("Tweet");
+		tweetTitlePanel = new JLabel("Tweet");
 		tweetTitlePanel.setHorizontalAlignment(SwingConstants.LEFT);
 		labelPanel.add(tweetTitlePanel, BorderLayout.NORTH);
 		
@@ -218,8 +222,8 @@ public class LabelingFrame extends JFrame implements ActionListener {
 		else if (e.getSource() == prev) {
 			if (tweetIterator != null && tweetIterator.hasPrevious()) {
 				currentTweet = tweetIterator.previous();
+				--curTweet;
 				this.updateUi(currentTweet);
-				this.repaint();
 			}
 			else {
 				JOptionPane.showMessageDialog(this, "You can't do that!", "User Error",
@@ -229,6 +233,7 @@ public class LabelingFrame extends JFrame implements ActionListener {
 		else if (e.getSource() == next) {
 			if (tweetIterator != null && tweetIterator.hasNext()) {
 				currentTweet = tweetIterator.next(); 
+				++curTweet;
 				this.updateUi(currentTweet);
 			}
[…]

### 2012-12-01 classify/src/main/java/ui/LabelingFrame.java
Changed fonts to make the ui easier to read

@@ -14,6 +14,7 @@ import java.io.File;
 import java.io.FileReader;
 import java.io.FileWriter;
 import java.io.IOException;
+import java.util.ArrayList;
 import java.util.HashSet;
 import java.util.LinkedList;
 import java.util.List;
@@ -32,6 +33,9 @@ import javax.swing.JTextField;
 import javax.swing.SwingConstants;
 import javax.swing.border.EmptyBorder;
 import javax.swing.filechooser.FileFilter;
+import java.awt.Color;
+import java.awt.event.FocusAdapter;
+import java.awt.event.FocusEvent;
 
 
 public class LabelingFrame extends JFrame implements ActionListener {
@@ -41,6 +45,8 @@ public class LabelingFrame extends JFrame implements ActionListener {
 	 */
 	private static final long serialVersionUID = -2225603632488216748L;
 	private JPanel contentPane;
+	
+	List<Tweet> tweets;
 	
 	//Fields holding the two types of labels for labeling
 	private JTextField firstLabelField;
@@ -63,7 +69,7 @@ public class LabelingFrame extends JFrame implements ActionListener {
 	//Dummy tweet for beginning and ending
 	private Tweet defaultTweet;
 	
-	JButton openFile, prev, next, delete, finish, firstLabel, secondLabel;
+	JButton openFile, prev, next, delete, finish, firstLabel, secondLabel, check;
 	
 	private JFileChooser fc;
 	
@@ -90,24 +96,35 @@ public class LabelingFrame extends JFrame implements ActionListener {
 	 */
 	public LabelingFrame() {
 		setDefaultCloseOperation(JFrame.EXIT_ON_CLOSE);
-		setBounds(100, 100, 450, 300);
+		setBounds(100, 100, 500, 350);
 		contentPane = new JPanel();
+		contentPane.setBackground(new Color(0, 0, 0));
 		contentPane.setBorder(new EmptyBorder(5, 5, 5, 5));
 		contentPane.setLayout(new BorderLayout(0, 0));
 		setContentPane(contentPane);
 		
 		Panel buttonPanel = new Panel();
+		buttonPanel.setBackground(new Color(0, 0, 0));
 		contentPane.add(buttonPanel, BorderLayout.SOUTH);
 		
 		openFile = new JButton("Open File");
+		openFile.setFont(new Font("Verdana", Font.PLAIN, 11));
[…]

### 2012-12-01 classify/src/main/java/classification/ModelTester.java
updated pipes

@@ -27,45 +27,30 @@ import common.Constants;
 import common.PipeFactory;
 
 public class ModelTester {
-	
+
 	private static final int random_seed = 0xDEADBEEF;
-	
+
 	public static void main(String[] args) throws IOException {
 
 		List<SerialPipes> allPipes = new LinkedList<SerialPipes>();
 		// add all the pipe variations to the list
-//		allPipes.add(PipeFactory.getPipe());
-		//allPipes.add(PipeFactory.getPipe1());
-		//allPipes.add(PipeFactory.getPipe2());
-//		allPipes.add(PipeFactory.getPipe3());
 		allPipes.add(PipeFactory.getDefault());
-		//allPipes.add(PipeFactory.brandonsGetPipes());
-//		allPipes.add(PipeFactory.getPipe5());
-//		allPipes.add(PipeFactory.getPipe6());
-//		allPipes.add(PipeFactory.getPipe7());
-//		allPipes.add(PipeFactory.getPipe8());
+		// allPipes.add(PipeFactory.brandonsGetPipes());
 
 		ArrayList<Trial> trials = new ArrayList<Trial>();
 		ArrayList<String> info = new ArrayList<String>();
 
 		while (!allPipes.isEmpty()) {
-			SerialPipes pipe  = allPipes.remove(0);
+			SerialPipes pipe = allPipes.remove(0);
 			InstanceList instances = new InstanceList(pipe);
-			// CsvIterator reader = new CsvIterator(new FileReader(new File(
-			// "tweets.txt")), Constants.CSV_ITERATOR_REGEX, 3, 2, 1);
-			// File file = new File("../corpus/sentiment.txt");
-			// File file2 = new File("../corpus/tweets.txt");
 			File file = new File("../corpus/appleBinaryFiltered.txt");
 			CsvIterator reader = new CsvIterator(new FileReader(file),
 					Constants.CSV_ITERATOR_REGEX, 3, 1, 2);
 			instances.addThruPipe(reader);
-			// CsvIterator reader2 = new CsvIterator(new FileReader(file2),
-			// Constants.CSV_ITERATOR_REGEX, 3, 2, 1);
-			// instances.addThruPipe(reader2);
 
-			InstanceList[] instanceLists = instances.split(new Randoms(random_seed),
-					new double[] { 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1,
[…]

### 2012-12-01 classify/src/main/java/classification/UnescapeHTML.java

@@ -18,6 +18,7 @@ public class UnescapeHTML extends Pipe {
 
 	public Instance pipe(Instance carrier) {
 		String str = (String) carrier.getData();
+		System.out.println("----------------------------------------------");
 		System.out.println("Before UnescapeHTML: " + str);
 		String str2 = StringEscapeUtils.unescapeHtml(str);
 		if (!str2.equals(str)) {
@@ -34,7 +35,7 @@ public class UnescapeHTML extends Pipe {
 		for (int i = 0; i < split.length; i++) {
 			if (split[i].equals(split[i].toUpperCase())) {
 				sb.append(split[i]);
-			} else if (!split[i].contains("http://")) {
+			} else if (!split[i].contains("http://") && !split[i].equalsIgnoreCase("apple")) {
 				sb.append(split[i].toLowerCase());
 			} else {
 				sb.append(split[i]);
@@ -43,7 +44,6 @@ public class UnescapeHTML extends Pipe {
 		}
 		carrier.setData(sb.toString());
 		System.out.println("After UnescapeHTML: " + sb);
-		System.out.println("----------------------------------------------");
 		return carrier;
 	}
 }

### 2012-12-01 classify/src/main/java/classification/UnescapeHTML.java
removed printing

@@ -18,8 +18,8 @@ public class UnescapeHTML extends Pipe {
 
 	public Instance pipe(Instance carrier) {
 		String str = (String) carrier.getData();
-		System.out.println("----------------------------------------------");
-		System.out.println("Before UnescapeHTML: " + str);
+//		System.out.println("----------------------------------------------");
+//		System.out.println("Before UnescapeHTML: " + str);
 		String str2 = StringEscapeUtils.unescapeHtml(str);
 		if (!str2.equals(str)) {
 			// System.out.println(str);
@@ -27,23 +27,23 @@ public class UnescapeHTML extends Pipe {
 			// System.out.println("----------------");
 			carrier.setData(str2);
 		}
-		str2 = str2.replaceAll("([A-Za-z])\\1{3,}", "$1$1$1").replaceAll(
-				"\\.{2,}", " ... ");
-
-		String split[] = str2.split("\\s+");
-		StringBuilder sb = new StringBuilder();
-		for (int i = 0; i < split.length; i++) {
-			if (split[i].equals(split[i].toUpperCase())) {
-				sb.append(split[i]);
-			} else if (!split[i].contains("http://") && !split[i].equalsIgnoreCase("apple")) {
-				sb.append(split[i].toLowerCase());
-			} else {
-				sb.append(split[i]);
-			}
-			sb.append(" ");
-		}
+//		str2 = str2.replaceAll("([A-Za-z])\\1{3,}", "$1$1$1").replaceAll(
+//				"\\.{2,}", " ... ");
+//
+//		String split[] = str2.split("\\s+");
+//		StringBuilder sb = new StringBuilder();
+//		for (int i = 0; i < split.length; i++) {
+//			if (split[i].equals(split[i].toUpperCase())) {
+//				sb.append(split[i]);
+//			} else if (!split[i].contains("http://") && !split[i].equalsIgnoreCase("apple")) {
+//				sb.append(split[i].toLowerCase());
+//			} else {
+//				sb.append(split[i]);
+//			}
+//			sb.append(" ");
+//		}
 		carrier.setData(sb.toString());
-		System.out.println("After UnescapeHTML: " + sb);
+//		System.out.println("After UnescapeHTML: " + sb);
 		return carrier;
 	}
 }

### 2012-12-01 classify/src/main/java/classification/ModelTester.java
Use mallet n-fold iterator

@@ -10,8 +10,10 @@ import java.io.ObjectInputStream;
 import java.util.ArrayList;
 import java.util.LinkedList;
 import java.util.List;
+import java.util.Random;
 import java.util.Scanner;
 
+import cc.mallet.classify.Classification;
 import cc.mallet.classify.Classifier;
 import cc.mallet.classify.ClassifierTrainer;
 import cc.mallet.classify.MaxEntTrainer;
@@ -20,6 +22,8 @@ import cc.mallet.classify.Trial;
 import cc.mallet.pipe.Pipe;
 import cc.mallet.pipe.SerialPipes;
 import cc.mallet.pipe.iterator.CsvIterator;
+import cc.mallet.types.CrossValidationIterator;
+import cc.mallet.types.Instance;
 import cc.mallet.types.InstanceList;
 import cc.mallet.util.Randoms;
 
@@ -27,29 +31,32 @@ import common.Constants;
 import common.PipeFactory;
 
 public class ModelTester {
-	
+
 	private static final int random_seed = 0xDEADBEEF;
 	
+	private static final int folds = 10;
+
 	public static void main(String[] args) throws IOException {
 
 		List<SerialPipes> allPipes = new LinkedList<SerialPipes>();
 		// add all the pipe variations to the list
-//		allPipes.add(PipeFactory.getPipe());
-		//allPipes.add(PipeFactory.getPipe1());
-		//allPipes.add(PipeFactory.getPipe2());
-//		allPipes.add(PipeFactory.getPipe3());
+		// allPipes.add(PipeFactory.getPipe());
+		// allPipes.add(PipeFactory.getPipe1());
+		// allPipes.add(PipeFactory.getPipe2());
+		// allPipes.add(PipeFactory.getPipe3());
 		allPipes.add(PipeFactory.getDefault());
-		//allPipes.add(PipeFactory.brandonsGetPipes());
-//		allPipes.add(PipeFactory.getPipe5());
-//		allPipes.add(PipeFactory.getPipe6());
-//		allPipes.add(PipeFactory.getPipe7());
-//		allPipes.add(PipeFactory.getPipe8());
+		// allPipes.add(PipeFactory.getDansPipes());
+		// allPipes.add(PipeFactory.brandonsGetPipes());
+		// allPipes.add(PipeFactory.getPipe5());
+		// allPipes.add(PipeFactory.getPipe6());
+		// allPipes.add(PipeFactory.getPipe7());
[…]

### 2012-12-01 classify/src/main/java/classification/ModelTester.java
merged

@@ -40,17 +40,8 @@ public class ModelTester {
 
 		List<SerialPipes> allPipes = new LinkedList<SerialPipes>();
 		// add all the pipe variations to the list
-		// allPipes.add(PipeFactory.getPipe());
-		// allPipes.add(PipeFactory.getPipe1());
-		// allPipes.add(PipeFactory.getPipe2());
-		// allPipes.add(PipeFactory.getPipe3());
 		allPipes.add(PipeFactory.getDefault());
-		// allPipes.add(PipeFactory.getDansPipes());
 		// allPipes.add(PipeFactory.brandonsGetPipes());
-		// allPipes.add(PipeFactory.getPipe5());
-		// allPipes.add(PipeFactory.getPipe6());
-		// allPipes.add(PipeFactory.getPipe7());
-		// allPipes.add(PipeFactory.getPipe8());
 
 		ArrayList<Trial> trials = new ArrayList<Trial>();
 		ArrayList<String> info = new ArrayList<String>();
@@ -58,22 +49,12 @@ public class ModelTester {
 		while (!allPipes.isEmpty()) {
 			SerialPipes pipe = allPipes.remove(0);
 			InstanceList instances = new InstanceList(pipe);
-			// CsvIterator reader = new CsvIterator(new FileReader(new File(
-			// "tweets.txt")), Constants.CSV_ITERATOR_REGEX, 3, 2, 1);
-			// File file = new File("../corpus/sentiment.txt");
-			// File file2 = new File("../corpus/tweets.txt");
 			File file = new File("../corpus/appleBinaryFiltered.txt");
 			CsvIterator reader = new CsvIterator(new FileReader(file),
 					Constants.CSV_ITERATOR_REGEX, 3, 1, 2);
 			instances.addThruPipe(reader);
-			// CsvIterator reader2 = new CsvIterator(new FileReader(file2),
-			// Constants.CSV_ITERATOR_REGEX, 3, 2, 1);
-			// instances.addThruPipe(reader2);
-			
-			CrossValidationIterator cvi = new CrossValidationIterator(instances, folds, new Random(random_seed));
 
-//			InstanceList[] instanceLists = instances.split(new Randoms(),
-//					new double[] { 0.3, 0.4, 0.3 });
+			CrossValidationIterator cvi = new CrossValidationIterator(instances, folds, new Random(random_seed));
 
 			String description = "";
 			for (Pipe p : pipe.pipes()) {

### 2012-12-01 classify/src/main/java/classification/ModelTester.java
pipe changes

@@ -8,24 +8,23 @@ import java.io.FileWriter;
 import java.io.IOException;
 import java.io.ObjectInputStream;
 import java.util.ArrayList;
+import java.util.Iterator;
 import java.util.LinkedList;
 import java.util.List;
 import java.util.Random;
 import java.util.Scanner;
 
-import cc.mallet.classify.Classification;
 import cc.mallet.classify.Classifier;
 import cc.mallet.classify.ClassifierTrainer;
 import cc.mallet.classify.MaxEntTrainer;
+import cc.mallet.classify.NaiveBayes;
 import cc.mallet.classify.NaiveBayesTrainer;
 import cc.mallet.classify.Trial;
 import cc.mallet.pipe.Pipe;
 import cc.mallet.pipe.SerialPipes;
 import cc.mallet.pipe.iterator.CsvIterator;
 import cc.mallet.types.CrossValidationIterator;
-import cc.mallet.types.Instance;
 import cc.mallet.types.InstanceList;
-import cc.mallet.util.Randoms;
 
 import common.Constants;
 import common.PipeFactory;
@@ -33,8 +32,8 @@ import common.PipeFactory;
 public class ModelTester {
 
 	private static final int random_seed = 0xDEADBEEF;
-	
-	private static final int folds = 10;
+
+	private static final int folds = 6;
 
 	public static void main(String[] args) throws IOException {
 
@@ -42,6 +41,12 @@ public class ModelTester {
 		// add all the pipe variations to the list
 		allPipes.add(PipeFactory.getDefault());
 		// allPipes.add(PipeFactory.brandonsGetPipes());
+
+		Iterator<SerialPipes> pipesIterator = PipeFactory.getPipes();
+
+		while (pipesIterator.hasNext()) {
+			SerialPipes pipes = pipesIterator.next();
+		}
 
 		ArrayList<Trial> trials = new ArrayList<Trial>();
 		ArrayList<String> info = new ArrayList<String>();
@@ -54,7 +59,8 @@ public class ModelTester {
 					Constants.CSV_ITERATOR_REGEX, 3, 1, 2);
 			instances.addThruPipe(reader);
 
-			CrossValidationIterator cvi = new CrossValidationIterator(instances, folds, new Random(random_seed));
+			CrossValidationIterator cvi = new CrossValidationIterator(
+					instances, folds, new Random(random_seed));
 
 			String description = "";
 			for (Pipe p : pipe.pipes()) {
[…]

### 2012-12-01 classify/src/main/java/classification/UnescapeHTML.java

@@ -42,7 +42,7 @@ public class UnescapeHTML extends Pipe {
 //			}
 //			sb.append(" ");
 //		}
-		carrier.setData(sb.toString());
+		//carrier.setData(sb.toString());
 //		System.out.println("After UnescapeHTML: " + sb);
 		return carrier;
 	}

### 2012-12-01 classify/src/main/java/common/PipeFactory.java

@@ -1,31 +1,67 @@
 package common;
 
 import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.Iterator;
 import java.util.regex.Pattern;
 
+import com.google.common.collect.Iterators;
+
 import cc.mallet.pipe.CharSequence2TokenSequence;
+import cc.mallet.pipe.CharSequenceLowercase;
 import cc.mallet.pipe.FeatureSequence2FeatureVector;
 import cc.mallet.pipe.Input2CharSequence;
 import cc.mallet.pipe.Pipe;
-import cc.mallet.pipe.PrintInputAndTarget;
 import cc.mallet.pipe.SerialPipes;
 import cc.mallet.pipe.Target2Label;
 import cc.mallet.pipe.TokenSequence2FeatureSequence;
 import cc.mallet.pipe.TokenSequenceNGrams;
 import cc.mallet.pipe.TokenSequenceRemoveStopwords;
 import classification.Stemmer;
-import classification.Tokenizer;
 import classification.UnescapeHTML;
 
 public class PipeFactory {
 
-	
+	public static Iterator<SerialPipes> getPipes() {
+		return new SetCombiner<SerialPipes, Pipe>() {
+
+			@Override
+			public SerialPipes combine(Iterable<Pipe> in) {
+				return new SerialPipes(Iterators.toArray(in.iterator(),
+						Pipe.class));
+			}
+
+		}.add(new SetFactory<Pipe>() {
+
+			@Override
+			public Iterable<Pipe> build() {
+				ArrayList<Pipe> pipes = new ArrayList<Pipe>();
+				pipes.add(new Input2CharSequence("UTF-8"));
+				pipes.add(new UnescapeHTML());
+				pipes.add(new CharSequenceLowercase());
+				return pipes;
+			}
+
+		}).add(new SetFactory<Pipe>() {
+
+			@Override
+			public Iterable<Pipe> build() {
+
+				return Arrays.asList(new Pipe[] {
+						new CharSequence2TokenSequence(Pattern.compile("[\\p{L}\\p{N}_]+")),
+						new CharSequence2TokenSequence(Pattern.compile("[^\\s]+"))
+				});
+			}
+
+		}).iterator();
+	}
+
 	public static SerialPipes getDefault() {
 		ArrayList<Pipe> pipe = new ArrayList<Pipe>();
 		// pipeList.add(new PrintInput());
[…]

### 2012-12-01 classify/src/main/java/classification/UnescapeHTML.java
updated tokenizer

@@ -42,7 +42,7 @@ public class UnescapeHTML extends Pipe {
 //			}
 //			sb.append(" ");
 //		}
-		carrier.setData(sb.toString());
+//		carrier.setData(sb.toString());
 //		System.out.println("After UnescapeHTML: " + sb);
 		return carrier;
 	}

### 2012-12-01 classify/src/main/java/classification/Tokenizer.java
tweaked regex

@@ -98,12 +98,16 @@ public class Tokenizer extends Pipe {
 			s = s.replaceAll("\\.{2,}", " ... ");
 			String spl[] = s.split("\\s+");
 			for (String ss : spl) {
-				if (!ss.equals(ss.toUpperCase())) {
+				if (!ss.toLowerCase().contains("apple")) { //!ss.equals(ss.toUpperCase())) {
 					ss = ss.toLowerCase();
+				} else {
+					//do it anyway!
+//					ss = ss.toLowerCase();
 				}
+				
 				ss = ss.replaceAll("([A-Za-z])\\1{3,}", "$1$1$1");
-				ss = ss.replaceAll("^[^\\w]", "");
-				ss = ss.replaceAll("[^\\w]$", "");
+				ss = ss.replaceAll("^[\\W]+", "");
+				ss = ss.replaceAll("[\\W]+$", "");
 				if (ss.length() > 0) {
 					ts.add(ss);
 					System.out.println(ss);

### 2012-12-01 classify/src/main/java/common/PipeFactory.java

@@ -49,9 +49,10 @@ public class PipeFactory {
 			public Iterable<Pipe> build() {
 
 				return Arrays.asList(new Pipe[] {
-						new CharSequence2TokenSequence(Pattern.compile("[\\p{L}\\p{N}_]+")),
-						new CharSequence2TokenSequence(Pattern.compile("[^\\s]+"))
-				});
+						new CharSequence2TokenSequence(Pattern
+								.compile("[\\p{L}\\p{N}_]+")),
+						new CharSequence2TokenSequence(Pattern
+								.compile("[^\\s]+")) });
 			}
 
 		}).iterator();
@@ -62,7 +63,6 @@ public class PipeFactory {
 		// pipeList.add(new PrintInput());
 		pipe.add(new Input2CharSequence("UTF-8"));
 		pipe.add(new UnescapeHTML());
-		pipe.add(new CharSequenceLowercase());
 		// Pattern tokenPattern = Pattern.compile("[\\p{L}\\p{N}_]+");
 		// pipe.add(new
 		// CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b",
@@ -76,8 +76,8 @@ public class PipeFactory {
 		// pipe.add(new TwitterFeatures());
 		// pipe.add(new Link2Title());
 
-		Pattern tokenPattern = Pattern.compile("[^\\s]+");
-		//pipe.add(new CharSequence2TokenSequence(tokenPattern));
+		// Pattern tokenPattern = Pattern.compile("[^\\s]+");
+		// pipe.add(new CharSequence2TokenSequence(tokenPattern));
 		pipe.add(new Tokenizer());
 		pipe.add(new TokenSequenceRemoveStopwords());
 		pipe.add(new Stemmer());

### 2012-12-01 classify/src/main/java/classification/Tokenizer.java
tokenizer and corpus updates

@@ -19,19 +19,10 @@ public class Tokenizer extends Pipe {
 	private static final String emoticons = "([<>]?[:;=8][\\-o\\*\\']?[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\\\]|[\\)\\]\\(\\[dDP/\\:\\}\\{@\\|\\\\][\\-o\\*\\']?[:;=8][<>]?)";
 	private static final String usernames = "@[\\w_]+";
 	private static final String hashtags = "\\#[\\w_]+[\\w\\'_\\-]*[\\w_]+";
-	private static final String links = "\\b(((ht|f)tp(s?)\\:\\/\\/|~\\/|\\/)|www.)"
-			+ "(\\w+:\\w+@)?(([-\\w]+\\.)+(com|org|net|gov"
-			+ "|mil|biz|info|mobi|name|aero|jobs|museum"
-			+ "|travel|[a-z]{2}))(:[\\d]{1,5})?"
-			+ "(((\\/([-\\w~!$+|.,=]|%[a-f\\d]{2})+)+|\\/)+|\\?|#)?"
-			+ "((\\?([-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?"
-			+ "([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)"
-			+ "(&(?:[-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?"
-			+ "([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)*)*"
-			+ "(#([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)?\\b"; // "http\\:\\/\\/.*?\\s";
[…]

### 2012-12-01 paper/paper.tex
updated paper

@@
 As businesses seek to discover public opinion about their business or products, Twitter is one source for mining this information.
-Tweets present interesting classification challenges due to their relatively small number of features and irregular formatting.
+Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
+Tweet selection by keyword filtering often suffers from an high accuracy and low recall, or low accuracy and high recall.
+Using machine learning for text classification can improve this.
+We aim to survey a variety of text processing steps, focusing on the effects of tokenization, to increase accuracy of classification using a Naive Bayes classifier.
+We use a broad set of keywords with the goal of collecting a superset of the Tweets about a particular company (Apple, in this case) and train a binary classifier to filter out false positives.
 \end{quote}
 \end{abstract}
-
-\noindent Tweet selection by keyword filtering often suffers from an high accuracy and low accuracy, or low accuracy and high recall.
-Using machine learning for text classification can improve this.
-We aim to survey a variety of text processing steps to increase accuracy of classification using a Naive Bayes classifier.
-We use a broad set of keywords with the goal of collecting a superset of the Tweets about a particular company (Apple, in this case) and train a binary classifier to filter out false positives.
 
@@
 \item Using URL-replacement will improve disambiguation accuracy. 
-\item adding features for emotican classes....
+\item adding features for emoticon classes....
 \item adding features for @references, retweets, and hashtags, will decrease the feature set while improving accuracy
@@
 \section{Related Work}
+DUALIST is a system that extends Mallet by user-interactive feedback during training[Settles]. Included in their implementation was a TwitterPipe that performed some simple feature extraction. 
+Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing \cite{potts2011}.
+A good deal of research has been done into sentiment classification of tweets \cite{Pak10}
 
@@
 \textbf{Corpus creation}\\
+By accessing the Twitter "Firehose" stream through their public API, we harvested tens of thousands of tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
+This provides us a smaller set of features in the overal corpus.
+The keywords used for the company of choice during this round of testing, Apple, were collected from information on the company's website and the Wikipedia page about Apple:\\
+...\\
+\\
+This set of keywords clearly allows in a large number of false positives:\\
+nice fish and chip.. good pie apple :-) http://t.co/KVDN5r5l \\
+20 chicken nuggets, chips, big mac, and a vanilla milkshake LIFE IS GOOD \\
+1 more day whoop plus safari ride yay \\
+shley staples an apple.  "AHHHH!!!!  Apple juice in my eye!" \\
+I ain't seen uncle Mac in a while\\
+\\
+During the time period of our data collection (give time period), the ratio was 40\% topical and 60\% false positives [need to analyze this for sure].
+On Twitter, a single message posted is often reposted, or "re-tweeted," many more times in a very short timespan.
+To reduce the effects of temporal overfitting, in which our model would overfit the data for a particular time slice, we filtered the data to remove retweets and near-duplicates.
+Tweets automatically osted by applications, iPad games, for instance, are often near-duplicates, so we removed these from the data set as well.
+This reduced a collection of 100,000 tweets by 50\%.
+\\
+A computer-posted tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP #ipad, #ipadgames, #gameinsight\\
+A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an _Apple_ _store_ soon! \\
+\\
+We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. \\
+Data sets and scripts used for processing text data are available on the project website.
+
 \textbf{Data aggregation and classification}\\
-\textbf{Decision-making}\\
 
@@
 We do all machine learning with the Mallet[2] library developed by the University of Massachusetts.
+Mallet includes abstractions for a data processing pipeline, during which we use pre-built and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format.
+We built several Pipes to analyze the effect of different filters and processes on the accuracy of classification:
+SpellCheck\\
+
+Stemmer\\
+
+Tokenizer\\
+Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenizing system due to the relatively small number of features present and high level of noise in the feature set [citation and more details].
+Features on twitter include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, emoticons, and hashtags, to name a few.
+
+Cool ranch , 4 berry sundae , apple juice #yessuh #latenight #snack http://t.co/ttc3vujp \\
+I just poured apple juice on my cereal.. Gah. #SoTired \\
+I hate Siri.. -___- \\
+
+We approach this problem using a layered feature extraction system using regular expressions.
+Some features will often contain ambiguous or incorrect matches to other tokens.
+A prime example of this is the emoticon :/, which appears in every http link: http:/t.co/p9weubf [bold the emoticon somehow].
+To alleviate such problems, we begin by tokenizing in order: URLs, emoticons, usernames, and hashtags.
+At this point, we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings.
+As done by Potts (2011) we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.\\
+
+#news can't wait for my signed #OoRITE2OutNow it's emotional here right now loooool #OoRITE2OutNow https://t.co/r4n4cn6C \\
+
+Capitalization\\
+As presented in our results, because of irregular capitalization, two tokens likely to be semantically identical with respect to company classification may be represented in multiple cases: {Nooo, NOOO, nooo, NoOo}.
+To alleviate this, we attempt three different approaches.
+In the first, we simply lowercase all remaining text (note that many URLs become invalid after modifying case).
+In the second, we lowercase any text that is not in all caps.
+This serves to retain acronyms.
+In the third, we lowercase everything, leaving the case of all strings containing "apple" (case insensitive) alone.
+We made this decision based on the semantic difference between the capitalization of Apple the company and apple the fruit.
+This can be generalized to a larger set of keywords and applied to other companies in a similar fashion.
+
+Miscenalaneous\\
+
+Unescape HTML\\
+
+N-grams\\
+
+Link2Title\\
+
+Stopword Removal\\
 
@@
 
+Discussion of accuracy etc
+
 \section{Applications and Future Work}
+
+Things that could be done....
 
@@
 
+\begin{thebibliography}{99}
+@article{potts2011,
+    author    = "Christopher Potts",
+    title     = "Sentiment Symposium Tutorial: Tokenizing",
+    journal   = "",
+    year      = "2011"
+}
+@inproceedings{Pak10,
+  added-at = {2010-06-01T10:23:44.000+0200},
+  address = {Valletta, Malta},
+  author = {Pak, Alexander and Paroubek, Patrick},
+  biburl = {http://www.bibsonomy.org/bibtex/25656c3bb1adf00c58a85e3204096961c/frederik},
+  booktitle = {Proceedings of the Seventh conference on International Language Resources and Evaluation (LREC'10)},
+  date = {19-21},
+  interhash = {ac930b0459a3c8a2fc2d74c52a475026},
+  intrahash = {5656c3bb1adf00c58a85e3204096961c},
+  isbn = {2-9517408-6-7},
+  keywords = {imported},
+  language = {english},
+  month = may,
+  publisher = {European Language Resources Association (ELRA)},
+  timestamp = {2010-06-01T10:23:44.000+0200},
+  title = {Twitter as a Corpus for Sentiment Analysis and Opinion Mining},
+  url = {http://www.lrec-conf.org/proceedings/lrec2010/pdf/385_Paper.pdf},
+  year = 2010
+}
+\end{thebibliography}
+
 [1] J. Bollen, H. Mao, and X.-J. Zeng. Twitter mood predicts the

### 2012-12-01 classify/src/main/java/classification/ModelTester.java

@@ -79,9 +79,9 @@ public class ModelTester {
 
 					Classifier classifier = trainer.train(train);
 
-					System.err.println(((NaiveBayes) classifier).getPriors());
+//					System.err.println(((NaiveBayes) classifier).getPriors());
 
-					((NaiveBayes) classifier).printWords(30);
+	//				((NaiveBayes) classifier).printWords(30);
 
 					Trial trial = new Trial(classifier, test);
 

### 2012-12-01 classify/src/main/java/classification/Tokenizer.java

@@ -64,10 +64,10 @@ public class Tokenizer extends Pipe {
 
 	public Instance pipe(Instance carrier) {
 		TokenSequence ts = new TokenSequence();
-
+		
 		String str = (String) carrier.getData();
 		System.out.println(str);
-
+		str = str.replaceAll("( RT )(^RT)( RT:)", "");
 		str = str.replaceAll("\\.{2,}", " ... ");
 		List<String> supersuperA = match(specialcases, ts, str, false, null);
 		List<String> superA = new ArrayList<String>();

### 2012-12-01 classify/src/main/java/common/PipeFactory.java
cleaned up files

@@ -47,10 +47,11 @@ public class PipeFactory {
 			protected void build() {
 				this.add(
 						new CharSequence2TokenSequence(Pattern
-								.compile("[\\p{L}\\p{N}_]+")), "p{L}\\p{N}");
+								.compile("[\\p{L}\\p{N}_]+")), "numdig tokenizer");
 				this.add(
 						new CharSequence2TokenSequence(Pattern
-								.compile("[^\\s]+")), "\\s");
+								.compile("[^\\s]+")), "whitespace tokenizer");
+				this.add(new Tokenizer(), "twitter tokenizer");
 			}
 
 		}).add(new SetFactory<Pipe>() {
@@ -85,18 +86,6 @@ public class PipeFactory {
 		// pipeList.add(new PrintInput());
 		pipe.add(new Input2CharSequence("UTF-8"));
 		pipe.add(new UnescapeHTML());
-		// Pattern tokenPattern = Pattern.compile("[\\p{L}\\p{N}_]+");
-		// pipe.add(new
-		// CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b",
-		// Pattern.CASE_INSENSITIVE), "HTTPLINK"));
-		// pipe.add( new
-		// CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+",
-		// Pattern.CASE_INSENSITIVE), "@USERLINK"));
-		// pipe.add(new CharSequenceReplace(Pattern.compile("\\'"), ""));
-		// pipe.add(new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"));
-		// pipe.add(new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"));
-		// pipe.add(new TwitterFeatures());
-		// pipe.add(new Link2Title());
 
 		Pattern tokenPattern = Pattern.compile("[^\\s]+");
 		// pipe.add(new CharSequence2TokenSequence(tokenPattern));

### 2012-12-01 happyfuntokenizing.py

@@ -1,0 +1,223 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+"""
+This code implements a basic, Twitter-aware tokenizer.
+
+A tokenizer is a function that splits a string of text into words. In
+Python terms, we map string and unicode objects into lists of unicode
+objects.
+
+There is not a single right way to do tokenizing. The best method
+depends on the application.  This tokenizer is designed to be flexible
+and this easy to adapt to new domains and tasks.  The basic logic is
+this:
+
+1. The tuple regex_strings defines a list of regular expression
+   strings.
+
+2. The regex_strings strings are put, in order, into a compiled
+   regular expression object called word_re.
+
+3. The tokenization is done by word_re.findall(s), where s is the
+   user-supplied string, inside the tokenize() method of the class
+   Tokenizer.
+
+4. When instantiating Tokenizer objects, there is a single option:
+   preserve_case.  By default, it is set to True. If it is set to
+   False, then the tokenizer will downcase everything except for
+   emoticons.
+
+The __main__ method illustrates by tokenizing a few examples.
+
+I've also included a Tokenizer method tokenize_random_tweet(). If the
+twitter library is installed (http://code.google.com/p/python-twitter/)
+and Twitter is cooperating, then it should tokenize a random
+English-language tweet.
+"""
+
+__author__ = "Christopher Potts"
+__copyright__ = "Copyright 2011, Christopher Potts"
+__credits__ = []
+__license__ = "Creative Commons Attribution-NonCommercial-ShareAlike 3.0 Unported License: http://creativecommons.org/licenses/by-nc-sa/3.0/"
+__version__ = "1.0"
+__maintainer__ = "Christopher Potts"
+__email__ = "See the author's website"
+
+######################################################################
+
+import re
+import htmlentitydefs
+
+######################################################################
+# The following strings are components in the regular expression
+# that is used for tokenizing. It's important that phone_number
+# appears first in the final regex (since it can contain whitespace).
+# It also could matter that tags comes after emoticons, due to the
+# possibility of having text like
+#
+#     <:| and some text >:)
+#
+# Most imporatantly, the final element should always be last, since it
+# does a last ditch whitespace-based tokenization of whatever is left.
+
+# This particular element is used in a couple ways, so we define it
+# with a name:
[…]

### 2012-12-01 paper/paper.tex
updated paper with new outline

@@
 
-\title{Tweet Classification - Filtering \\ of Twitter for Company-relevant Tweets}
+\title{Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets}
 \author{
@@
 \section{Introduction}
-
-\subsection{Goals}
-
-\begin{itemize}
-
-\item Collect a corpus that represents a superset of tweets about Apple and label these instances as "apple" or "none"
-\item Create preprocessing steps to maximize the accuracy of binary classification
-
-\end{itemize}
-
-\subsection{Hypotheses}
-\item Using URL-replacement will improve disambiguation accuracy. 
-\item adding features for emoticon classes....
-\item adding features for @references, retweets, and hashtags, will decrease the feature set while improving accuracy
-\item selection of a proper tokenization regex will have profound effects on accuracy
-\item Stopping and stemming....
+Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on sentiment \cite{Ruiz:2012:CFT:2124295.2124358}, ... [ADD MORE]
+In many cases, the problem of determining which tweets are relevant for a particular application is prerequisite to meaningful results.
+In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interest natural language processing problem in many cases.
+We present a system to disambiguate tweets about the company Apple.
 
@@
 Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing \cite{potts2011}.
-A good deal of research has been done into sentiment classification of tweets \cite{Pak10}
+A good deal of research has been done into sentiment classification of tweets, which requires very similar text processing and tokenization \cite{Pak10}.
 
-\section{System Breakdown}
-\textbf{Corpus creation}\\
-By accessing the Twitter "Firehose" stream through their public API, we harvested tens of thousands of tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
-This provides us a smaller set of features in the overal corpus.
-The keywords used for the company of choice during this round of testing, Apple, were collected from information on the company's website and the Wikipedia page about Apple:\\
+\section{Method}
+\subsection{Corpus creation}\\
+By accessing the Twitter "Firehose" stream through their public API, we harvested 115,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
+This provides us a smaller set of features in the overall corpus.
+The keywords used for the company of choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
 ...\\
 \\
-This set of keywords clearly allows in a large number of false positives:\\
+This set of keywords clearly allows a large number of false positives:\\
 nice fish and chip.. good pie apple :-) http://t.co/KVDN5r5l \\
@@
 \\
-During the time period of our data collection (give time period), the ratio was 40\% topical and 60\% false positives [need to analyze this for sure].
+We define a tweet to be "about" Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers.
+We make the assumption that spam will be filtered from the testing set.
+This could be done via an existing Naive Bayes classifier, but we simply did not include instances of spam in our corpus during the manual labeling process.
+We collected our tweets over the course of twelve hours.
 On Twitter, a single message posted is often reposted, or "re-tweeted," many more times in a very short timespan.
-To reduce the effects of temporal overfitting, in which our model would overfit the data for a particular time slice, we filtered the data to remove retweets and near-duplicates.
-Tweets automatically osted by applications, iPad games, for instance, are often near-duplicates, so we removed these from the data set as well.
-This reduced a collection of 100,000 tweets by 50\%.
-\\
-A computer-posted tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP #ipad, #ipadgames, #gameinsight\\
+Because of the small timespan of our data collection, a large number of retweets (effectively duplicates) appeared in the dataset.
+We filtered these duplicates out of the dataset as well to prevent over-fitting in our model.
+After filtering, our original set of 115,000 tweets was reduced to 65,000.
+A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].
+A computer-posted spam tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP #ipad, #ipadgames, #gameinsight\\
 A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an _Apple_ _store_ soon! \\
@@
 
-\textbf{Data aggregation and classification}\\
-
-\subsection{Basic Approach}
+\subsection{Preprocessing Pipeline}
 
 We do all machine learning with the Mallet[2] library developed by the University of Massachusetts.
-Mallet includes abstractions for a data processing pipeline, during which we use pre-built and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format.
+Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format.
 We built several Pipes to analyze the effect of different filters and processes on the accuracy of classification:
-SpellCheck\\
 
-Stemmer\\
+\subsubsection{Feature-space Enrichment}
+Stopword removal:
+N-grams:
+Fix emoticons:
+HTML corrections: 
+URL replacement:
+Spell checking:
 
-Tokenizer\\
+\subsubsection{Disambiguation}
+Lowercasing:
+Stemming:
+
+\subsubsection{Tokenization}
 Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenizing system due to the relatively small number of features present and high level of noise in the feature set [citation and more details].
@@
 
-Miscenalaneous\\
-
-Unescape HTML\\
-
-N-grams\\
-
-Link2Title\\
-
-Stopword Removal\\
+\section{Experimental Setup}
+...constant-size test set with sliced training
+...comparison to n-fold validation
 
 \section{Results}
+...baseline using priors
+  baseline using whitespace splitting in naive bayes.
+  select interesting improvements.
+  graphs of both validation types
+  most useful features for classification
 
-Discussion of accuracy etc
-
-\section{Applications and Future Work}
+\section{Conclusion and Future Work}
 
 Things that could be done....
+
+[These guys] demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification.
 
@@
 \section{ Acknowledgments}
+Thank you to Dr. Jin Tian and our TA Ru He for their guidance during this research project. We also extend our thanks to our friends for their help in manual labeling of tweets.
 
+\section{References}
 \begin{thebibliography}{99}
@@
 }
+@inproceedings{Ruiz:2012:CFT:2124295.2124358,
+ author = {Ruiz, Eduardo J. and Hristidis, Vagelis and Castillo, Carlos and Gionis, Aristides and Jaimes, Alejandro},
+ title = {Correlating financial time series with micro-blogging activity},
+ booktitle = {Proceedings of the fifth ACM international conference on Web search and data mining},
+ series = {WSDM '12},
+ year = {2012},
+ isbn = {978-1-4503-0747-5},
+ location = {Seattle, Washington, USA},
+ pages = {513--522},
+ numpages = {10},
+ url = {http://doi.acm.org/10.1145/2124295.2124358},
+ doi = {10.1145/2124295.2124358},
+ acmid = {2124358},
+ publisher = {ACM},
+ address = {New York, NY, USA},
+ keywords = {financial time series, micro-blogging, social networks},
+} 
 \end{thebibliography}

### 2012-12-02 paper/paper.tex
Added stuff for the pipes I implemented

@@
 \subsubsection{Feature-space Enrichment}
-Stopword removal:
+Stopword removal: In order to improve accuracy of classification we decided to run each tweet through a pipe that would remove stopwords.
+Stopwords are generally known as adverbs, conjunctions, pronouns, and prepositions commonly found in English sentences, By removing these words, we hoped that the classifiers would be able to focus more on the relevant text and less on meaningless parts of the tweets.
+Since this is a common task for natural language processing we were able to make use of one of Mallet's stopwords pipes, using a default list of stopwords.
 N-grams:
@@
 URL replacement:
-Spell checking:
+Spell checking: Since twitter is an informal form of communication, we found that a fair number of tweets were being classified that had misspelled words.
+We decided that performing a spell check on the tweet might help the classifier work, since then it would only have to process proper English.
+In order to perform the spell check, we made use of an api that would return suggestions for misspelled words.
+Along with the suggested correct spellings of words, we were also given a "confidence" level for each suggestion.
+By using this value we were able to choose the best suggestion, and also filter out any suggestions that were too far from the original word.
 
@@
 Lowercasing:
-Stemming:
+Stemming: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
+Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not a real word.
+We believed that by reducing each word in the tweet to a its stem, we would be able to improve the classifying algorithm's ability to classify.
+In order to add stemming we made use of an api that used a Porter stemming algorithm to find the stem of each word.
 

### 2012-12-02 paper/paper.tex
updated formatting and content of paper

--- 2012-12-01 paper/paper.tex
@@
 \section{Method}
-\subsection{Corpus creation}\\
+\subsection{Corpus creation}
 By accessing the Twitter "Firehose" stream through their public API, we harvested 115,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
@@
 ...\\
-\\
+
 This set of keywords clearly allows a large number of false positives:\\
@@
 1 more day whoop plus safari ride yay \\
-shley staples an apple.  "AHHHH!!!!  Apple juice in my eye!" \\
+Ashley staples an apple.  "AHHHH!!!!  Apple juice in my eye!" \\
 I ain't seen uncle Mac in a while\\
-\\
+
 We define a tweet to be "about" Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers.
@@
 A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].
-A computer-posted spam tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP #ipad, #ipadgames, #gameinsight\\
-A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an _Apple_ _store_ soon! \\
-\\
+A computer-posted spam tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
+A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
+
 We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. \\
-Data sets and scripts used for processing text data are available on the project website.
+Data sets and scripts used for processing text data are available on the project website.\\
 
@@
 
-We do all machine learning with the Mallet[2] library developed by the University of Massachusetts.
+We do all machine learning with the Mallet\cite{McCallumMALLET} library developed by the University of Massachusetts.
 Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format.
-We built several Pipes to analyze the effect of different filters and processes on the accuracy of classification:
+We built several Pipes to analyze the effect of different filters and processes on the accuracy of classification.
+Not every Pipe proved to increase accuracy--some decreased it.
+We present the descriptions of and motivations for these Pipes here.
 
@@
 \subsubsection{Tokenization}
-Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenizing system due to the relatively small number of features present and high level of noise in the feature set [citation and more details].
-Features on twitter include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, emoticons, and hashtags, to name a few.
+Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenization system due to the high level of noise in the feature set [citation and more details].
+Tweets are limited to 140 characters, which limits the total number of features possible.
+Some of the many natural language processing dilemmas present in tweets include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, and hashtags, to name a few.
 
-Cool ranch , 4 berry sundae , apple juice #yessuh #latenight #snack http://t.co/ttc3vujp \\
-I just poured apple juice on my cereal.. Gah. #SoTired \\
-I hate Siri.. -___- \\
+Cool ranch , 4 berry sundae , apple juice \#yessuh \#latenight \#snack http://t.co/ttc3vujp 
+I just poured apple juice on my cereal.. Gah. \#SoTired 
+I hate Siri.. -\_\_\_-
 
-We approach this problem using a layered feature extraction system using regular expressions.
-Some features will often contain ambiguous or incorrect matches to other tokens.
-A prime example of this is the emoticon :/, which appears in every http link: http:/t.co/p9weubf [bold the emoticon somehow].
-To alleviate such problems, we begin by tokenizing in order: URLs, emoticons, usernames, and hashtags.
-At this point, we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings.
-As done by Potts (2011) we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.\\
+We approach this problem using a layered token extraction system.
+Using regular expressions, we begin by searching for tokens that may include other, more general tokens.
+A prime example of this is an emoticon appearing in a URL.
 
-#news can't wait for my signed #OoRITE2OutNow it's emotional here right now loooool #OoRITE2OutNow https://t.co/r4n4cn6C \\
+Searching for emoticons in this tweet will extract :/ as an emoticon, effectively breaking up the URL.
 
-Capitalization\\
-As presented in our results, because of irregular capitalization, two tokens likely to be semantically identical with respect to company classification may be represented in multiple cases: {Nooo, NOOO, nooo, NoOo}.
+Now on my iphone ?? http://t.co/Rqr1RL2R
+
+Additionally, users often include emoticons or links after text with no delimiting whitespace.
+
+I listen to my iPod every day and it's just broke omg:(!!
+
+Extracting tokens using this layered approach eliminates many of these problems.
+
+After tokenizing these special features in order (URLs, emoticons, usernames, and hashtags) we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings.
+As done by Potts (2011) we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
+In the following tweet, "loooool" is normalized to "loool".
+
+\#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now loooool \#OoRITE2OutNow https://t.co/r4n4cn6C
+
+Note that such repetitions are often valid in URLs and some emoticons. Normalizing them prior to this step would make URLs invalid if using our link replacement Pipe.
+
+As presented in our results, because of irregular capitalization, two tokens likely to be semantically identical with respect to company classification may be represented in multiple cases: {Nooo, NOOO, nooo, NoOo} is a prime example.
 To alleviate this, we attempt three different approaches.
-In the first, we simply lowercase all remaining text (note that many URLs become invalid after modifying case).
+In the first, we simply lowercase all remaining tokens (note that many URLs become invalid after modifying case).
 In the second, we lowercase any text that is not in all caps.
 This serves to retain acronyms.
-In the third, we lowercase everything, leaving the case of all strings containing "apple" (case insensitive) alone.
+In the third, we change all remaining tokens to lowercase, leaving the case of all strings containing "apple" (case insensitive) alone.
 We made this decision based on the semantic difference between the capitalization of Apple the company and apple the fruit.
-This can be generalized to a larger set of keywords and applied to other companies in a similar fashion.
+While correct capitalization is naturally not always present for this token, this is one case where capitalization serves to disambiguate.
+This same principle can be generalized to a larger set of keywords and applied to other companies in a similar fashion.
 
@@
 \section{Contributions}
-
-We have built several reusable Java components that extend the Mallet API for processig of data from Twitter.
-We created a TweetJsonIterator that accepts Twitter's JSON-formatted tweets and creates Mallet Instances containing their values for easy processing by Mallet's pipeline during model training.
-We have also created several Pipe implementations that can be reused or easily modified to suit a similar Twitter processing.
-These include FixEmoticons, Link2Title, Stemmer, SpellCheck, and TwitterFeatures.
+We have built several reusable Java components that extend the Mallet API for processing of data from Twitter.
+We created a TweetJsonIterator that accepts a file of Twitter's JSON-formatted tweets and creates training Instances containing their values for easy processing during model training.
+We have implemented several Pipes that can be reused or easily modified to suit a similar Twitter processing purpose.
+These include FixEmoticons, Link2Title, Stemmer, SpellCheck, and Tokenize, which serves as a more extensible tokenizer than Mallet's default.
 All code is available through our project website.
+We also provide a corpus of 115,000 tweets selected by Apple-related keyword and our labeled data set of 2000 tweets.
+The bash scripts used to filter the data for near-duplicates and spam are also available for download.
 
@@
   title = {Twitter as a Corpus for Sentiment Analysis and Opinion Mining},
-  url = {http://www.lrec-conf.org/proceedings/lrec2010/pdf/385_Paper.pdf},
+  url = {http://www.lrec-conf.org/proceedings/lrec2010/pdf/385\_Paper.pdf},
   year = 2010
@@
 } 
+@unpublished{McCallumMALLET,
+    author = "Andrew Kachites McCallum",
+    title = "MALLET: A Machine Learning for Language Toolkit",
+    note = "http://mallet.cs.umass.edu",
+    year = 2002,
+}
+
 \end{thebibliography}
@@
 
-[2] Mallett, University of Massachussetts Department of Computer Science\\
-
-[3] Sanders Analytics (http://www.sananalytics.com/lab/twitter-sentiment/)
-
 \end{document}

### 2012-12-02 paper/paper.tex

@@
 \subsubsection{Feature-space Enrichment}
-Stopword removal: 
+Stopword removal: In order to improve accuracy of classification we decided to run each tweet through a pipe that would remove stopwords.
+Stopwords are generally known as adverbs, conjunctions, pronouns, and prepositions commonly found in English sentences, By removing these words, we hoped that the classifiers would be able to focus more on the relevant text and less on meaningless parts of the tweets.
+Since this is a common task for natural language processing we were able to make use of one of Mallet's stopwords pipes, using a default list of stopwords.
 N-grams:

### 2012-12-02 paper/paper.tex
added new pipe package

@@
 This set of keywords clearly allows a large number of false positives:\\
+\begin{quote}
 nice fish and chip.. good pie apple :-) http://t.co/KVDN5r5l \\
@@
 Ashley staples an apple.  "AHHHH!!!!  Apple juice in my eye!" \\
-I ain't seen uncle Mac in a while\\
+I ain't seen uncle Mac in a while \\
+\end{quote}
 
@@
 A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].
+\begin{quote}
 A computer-posted spam tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
 A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
+\end{quote}
 
@@
 \subsubsection{Feature-space Enrichment}
-Stopword removal: In order to improve accuracy of classification we decided to run each tweet through a pipe that would remove stopwords.
+~\\
+\textit{Stopword removal}: In order to improve accuracy of classification we decided to run each tweet through a pipe that would remove stopwords.
 Stopwords are generally known as adverbs, conjunctions, pronouns, and prepositions commonly found in English sentences, By removing these words, we hoped that the classifiers would be able to focus more on the relevant text and less on meaningless parts of the tweets.
-Since this is a common task for natural language processing we were able to make use of one of Mallet's stopwords pipes, using a default list of stopwords.
-N-grams:
-Fix emoticons:
-HTML corrections: 
-URL replacement:
-Spell checking: Since twitter is an informal form of communication, we found that a fair number of tweets were being classified that had misspelled words.
+Since this is a common task for natural language processing we were able to make use of one of Mallet's stopwords pipes, using a default list of stopwords.\\
+\textit{N-grams}:\\
+\textit{Fix emoticons}:\\
+\textit{HTML corrections}:\\ 
+\textit{URL replacement}:\\
+Spell checking: Since Twitter is an informal form of communication, we found that a fair number of tweets were being classified that had misspelled words.
 We decided that performing a spell check on the tweet might help the classifier work, since then it would only have to process proper English.
@@
 Along with the suggested correct spellings of words, we were also given a "confidence" level for each suggestion.
-By using this value we were able to choose the best suggestion, and also filter out any suggestions that were too far from the original word.
+By using this value we were able to choose the best suggestion, and also filter out any suggestions that were too far from the original word.\\
 
 \subsubsection{Disambiguation}
-Lowercasing:
+~\\
+\textit{Lowercasing}:\\
 Stemming: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
@@
 We believed that by reducing each word in the tweet to a its stem, we would be able to improve the classifying algorithm's ability to classify.
-In order to add stemming we made use of an api that used a Porter stemming algorithm to find the stem of each word.
+In order to add stemming we made use of an api that used a Porter stemming algorithm to find the stem of each word.\\
 
 \subsubsection{Tokenization}
+~\\
 Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenization system due to the high level of noise in the feature set [citation and more details].
 Tweets are limited to 140 characters, which limits the total number of features possible.
-Some of the many natural language processing dilemmas present in tweets include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, and hashtags, to name a few.
+Some of the many natural language processing dilemmas present in tweets include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, and hashtags, to name a few.\\
 
+\begin{quote}
 Cool ranch , 4 berry sundae , apple juice \#yessuh \#latenight \#snack http://t.co/ttc3vujp 
@@
 I hate Siri.. -\_\_\_- 
+\end{quote}
 
@@
 Searching for emoticons in this tweet will extract :/ as an emoticon, effectively breaking up the URL.
-
+\begin{quote}
 Now on my iphone ?? http://t.co/Rqr1RL2R 
+\end{quote}
 
@@
 
+\begin{quote}
 I listen to my iPod every day and it's just broke omg:(!!
+\end{quote}
 
@@
 In the following tweet, "loooool" is normalized to "loool".
-
+\begin{quote}
 \#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now loooool \#OoRITE2OutNow https://t.co/r4n4cn6C 
+\end{quote}
 

### 2012-12-02 classify/src/main/java/pipe/Apple.java

@@ -1,0 +1,23 @@
+package pipe;
+
+import java.util.Random;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+public class Apple extends Pipe {
+	
+	
+	@Override
+	public Instance pipe(Instance carrier) {
+		Random gen = new Random(System.currentTimeMillis());
+		
+		StringBuilder apple = new StringBuilder();
+		for (int i = 0; i < gen.nextInt(42); ++i) {
+			apple.append("Apple ");
+		}
+		
+		carrier.setData(apple.toString());
+		return carrier;
+	}
+}

### 2012-12-02 classify/src/main/java/pipe/CopyData2Source.java

@@ -1,0 +1,18 @@
+package pipe;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+/**
+ * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/CopyData2Source.java?r=10
+ *
+ */
+public class CopyData2Source extends Pipe {
+    private static final long serialVersionUID = 1;
+
+    public Instance pipe (Instance carrier) {
+        carrier.setSource(carrier.getData());
+        return carrier;
+    }
+
+}

### 2012-12-02 classify/src/main/java/pipe/Emotes.java

@@ -1,0 +1,55 @@
+package pipe;
+
+import java.util.regex.Pattern;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+/**
+ * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
+ *
+ */
+public class Emotes extends Pipe {
+
+    private static final long serialVersionUID = -22701908667551888L;
+    
+    private Pattern smile = Pattern.compile("#(^|\\W)(\\>\\:\\]|\\:-\\)|\\:\\)|\\:o\\)|\\:\\]|\\:3|\\:c\\)|\\:\\>|\\=\\]|8\\)|\\=\\)|\\:\\}|\\:\\^\\))($|\\W)#");
+    private Pattern laugh = Pattern.compile("#(^|\\W)(\\>\\:D|\\:-D|\\:D|8-D|x-D|X-D|\\=-D|\\=D|\\=-3|8-\\)|xD|XD|8D|\\=3)($|\\W)#");
+    private Pattern sad = Pattern.compile("#(^|\\W)(\\>\\:\\[|\\:-\\(|\\:\\(|\\:-c|\\:c|\\:-\\<|\\:-\\[|\\:\\[|\\:\\{|\\>\\.\\>|\\<\\.\\<|\\>\\.\\<)($|\\W)#");
+    private Pattern wink = Pattern.compile("#(^|\\W)(\\>;\\]|;-\\)|;\\)|\\*-\\)|\\*\\)|;-\\]|;\\]|;D|;\\^\\))($|\\W)#");
+    private Pattern tongue = Pattern.compile("#(^|\\W)(\\>\\:P|\\:-P|\\:P|X-P|x-p|\\:-p|\\:p|\\=p|\\:-Þ|\\:Þ|\\:-b|\\:b|\\=p|\\=P|xp|XP|xP|Xp)($|\\W)#");
+    private Pattern surprise = Pattern.compile("#(^|\\W)(\\>\\:o|\\>\\:O|\\:-O|\\:O|°o°|°O°|\\:O|o_O|o\\.O|8-0)($|\\W)#");
+    private Pattern annoyed = Pattern.compile("#(^|\\W)(\\>\\:\\\\|\\>\\:/|\\:-/|\\:-\\.|\\:\\\\|\\=/|\\=\\\\|\\:S|\\:\\/)($|\\W)#");
[…]

### 2012-12-02 classify/src/main/java/pipe/FixEmoticons.java

@@ -1,0 +1,38 @@
+package pipe;
+
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+/**
+ * Source : http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/FixEmoticons.java?r=10
+ *
+ */
+public class FixEmoticons extends Pipe {
+    
+    private Pattern regex;
+    
+    public FixEmoticons(Pattern regex) {
+        this.regex = regex;
+    }
+
+    public Instance pipe (Instance carrier) {
+        String text = (String) carrier.getData();
+        Matcher m = regex.matcher(text);
+
+        StringBuilder sb = new StringBuilder();
+        int last = 0;
+        while (m.find()) {
+            sb.append(text.substring(last, m.start()));
+            sb.append(m.group(0).toUpperCase());
+            last = m.end();
+        }
+        sb.append(text.substring(last));
+
+        carrier.setData(sb.toString());
+        return carrier;
+    }
+
+}

### 2012-12-02 classify/src/main/java/pipe/Labelize.java

@@ -1,0 +1,40 @@
+package pipe;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Alphabet;
+import cc.mallet.types.Instance;
+import cc.mallet.types.Label;
+import cc.mallet.types.LabelAlphabet;
+
+/**
+ * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/Labelize.java?r=10
+ *
+ */
+public class Labelize extends Pipe {
+    private final static long serialVersionUID = -461155063551297878L; //-8390758647439705273L; 
+
+    public Labelize (Alphabet dataAlphabet, LabelAlphabet labelAlphabet) {
+        super(dataAlphabet, labelAlphabet);
+    }
+
+    public Labelize ()
+    {
+        this(null, new LabelAlphabet());
+    }
+
+    public Labelize (LabelAlphabet labelAlphabet)
+    {
+        this(null, labelAlphabet);
+    }
+
+    public Instance pipe (Instance carrier)
+    {
+        if (carrier.getTarget() != null) {
+            if (carrier.getTarget() instanceof Label)
+                return carrier;
+            LabelAlphabet ldict = (LabelAlphabet) getTargetAlphabet();
+            carrier.setTarget(ldict.lookupLabel (carrier.getTarget()));
+        }
+        return carrier;
+    }
+}

### 2012-12-02 classify/src/main/java/pipe/Link2Title.java

@@ -1,0 +1,79 @@
+package pipe;
+
+import java.io.IOException;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+import org.jsoup.Jsoup;
+import org.jsoup.nodes.Document;
+
+import common.Constants;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+public class Link2Title extends Pipe {
+	
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 6856138170442079105L;
+
+	/**
+	 * This assumes that the carrier still has the Tweet Text STRING in the data field
+	 */
+	@Override
+	public Instance pipe(Instance carrier) {
+		Pattern httpPattern = Pattern.compile(Constants.HTTP_REGEX);
+		
+		String text = (String) carrier.getData();
+				
+		if (text == null) {
+			return carrier;
+		}
+		
+		Matcher m = httpPattern.matcher(text);
+		
+		StringBuilder sb = new StringBuilder();
+		
+		/*
+		 * We assume that the tweet uses at least somewhat proper English and
+		 * has spaces between each word. That way we can just look at each word, see if it's a link,
+		 * look it up if it is, otherwise just append the string, and move on.
+		 */
+		
+		for (String s: text.split("\\s+")) {
+			//We found a link so look it up
+			if (s.matches(Constants.HTTP_REGEX) && m.find()) {
+				String url = m.group();
+				Document doc = null;
+				try {
+					doc = Jsoup.connect(url).get();
+					if (doc.title() != null && !doc.title().equals("")) {
+						//Flawless victory!
+						sb.append(doc.title());
+						System.out.println("replaced " + url + " with " + doc.title());
+					}
+					else {
+						//try to resolve the url
+						sb.append(doc.baseUri());
+						System.out.println("replaced " + url + " with " + doc.baseUri());
+					}
+				} catch (IOException e) {
+					//Ignore it and put the url back into the string
+					sb.append(url);
+					System.out.println("did not replace url " + url);
+				}
+			}
+			//Regular word so just throw it into the result
+			else {
+				sb.append(s);
+			}
+			sb.append(" ");
+		}
+		
+		System.out.println("After replacing: " + sb.toString());
+		carrier.setData(sb.toString());
+		return carrier;
+	}
+}

### 2012-12-02 classify/src/main/java/pipe/SpellCheck.java

@@ -1,0 +1,86 @@
+package pipe;
+
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.util.List;
+import java.util.StringTokenizer;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+import com.swabunga.spell.engine.SpellDictionaryHashMap;
+import com.swabunga.spell.engine.Word;
+import com.swabunga.spell.event.SpellChecker;
+
+public class SpellCheck extends Pipe {
+
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 5452951467629627217L;
+	
+	private SpellDictionaryHashMap dictionary;
+	private SpellChecker spellchecker;
+	
+	private String dictionaryLoc = "../classify/eng_com.dic";
+	private int threshold = 100;
+	
+	//Look at this block!
+	{
+		try {
+			dictionary = new SpellDictionaryHashMap(new File(dictionaryLoc));
+			spellchecker = new SpellChecker(dictionary);
+		} catch (FileNotFoundException e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		} catch (IOException e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+	}
+	
+	
+	/**
+	 * Takes the given instance and does a spell check on the tweet text, replacing misspelled words with the
+	 * best correction. The spell check is taken from the Google SpellChecker api
+	 */
+	@Override
+	public Instance pipe(Instance carrier) {
+		String text = (String) carrier.getData();
+		
+		if (text == null) {
+			return carrier;
+		}
+		
+		StringTokenizer st = new StringTokenizer(text);
+		StringBuilder result = new StringBuilder();
+		while (st.hasMoreTokens()) {
+			String token = st.nextToken();
+			//One letter words don't play well  with others
+			if (token.length() != 1) {
+				List<Word> words = (List<Word>) spellchecker.getSuggestions(token, threshold);
+				Word best = findBest(words);
+				token = (best != null && best.getCost() < threshold) ? best.getWord() : token;
+			}
+			result.append(token).append(" ");
+		}
+		carrier.setData(result.toString());
+		return carrier;
+	}
+	
+	private Word findBest(List<Word> words) {
+		if (words.size() == 0) {
+			return null;
+		}
+		Word best = words.get(0);
+		for (Word w: words) {
[…]

### 2012-12-02 classify/src/main/java/pipe/Stemmer.java

@@ -1,0 +1,49 @@
+package pipe;
+
+import java.io.IOException;
+import java.io.ObjectInputStream;
+
+import org.tartarus.snowball.ext.PorterStemmer;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+import cc.mallet.types.Token;
+import cc.mallet.types.TokenSequence;
+/**
+ * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
+ *
+ */
+public class Stemmer extends Pipe {
+
+	private transient PorterStemmer stemmer;
+
+    private static final long serialVersionUID = -2270190864067551888L;
+
+    public Stemmer() {
+            stemmer = new PorterStemmer();
+    }
+
+    private void readObject(ObjectInputStream aInputStream)
+                    throws ClassNotFoundException, IOException {
+            aInputStream.defaultReadObject();
+            stemmer = new PorterStemmer();
+    }
+
+    public Instance pipe(Instance carrier) {
+            TokenSequence tokenSequence = (TokenSequence) carrier.getData();
+            TokenSequence stemmedTokenSequence = new TokenSequence();
+
+            for (int i = 0; i < tokenSequence.size(); i++) {
+                    Token token = tokenSequence.get(i);
+                    stemmer.setCurrent(token.getText());
+                    stemmer.stem();
+                    String s = stemmer.getCurrent();
+                    stemmedTokenSequence.add(new Token(s));
+//                    if (!token.getText().equals(s)) {
+//                    System.out.println(token.getText() + "   :   " + s);
+//                    }
+            }
+            carrier.setData(stemmedTokenSequence);
+            return carrier;
+    }
+}

### 2012-12-02 classify/src/main/java/pipe/TokenSequenceBiGrammer.java

@@ -1,0 +1,23 @@
+package pipe;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+import cc.mallet.types.TokenSequence;
+
+/**
+ * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/TokenSequenceBiGrammer.java?r=10
+ *
+ */
+public class TokenSequenceBiGrammer extends Pipe {
+
+    public Instance pipe (Instance carrier) {
+        TokenSequence ts = (TokenSequence) carrier.getData();
+        int size = ts.size();
+        for (int i = 1; i < size; i++) {
+            ts.add (ts.get(i-1).getText() + "_" + ts.get(i).getText());
+        }
+        carrier.setData(ts);
+        return carrier;
+    }
+
+}

### 2012-12-02 classify/src/main/java/pipe/Tokenizer.java

@@ -1,0 +1,120 @@
+package pipe;
+
+import java.util.ArrayList;
+import java.util.List;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+import cc.mallet.types.TokenSequence;
+
+/**
+ * Custom tokenizer.
+ */
+public class Tokenizer extends Pipe {
+
+	private static final long serialVersionUID = 1013696874537828543L;
+	// "-_+-
+	private static final String emoticons = "([<>]?[:;=8][\\-o\\*\\']?[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\\\]|[\\)\\]\\(\\[dDP/\\:\\}\\{@\\|\\\\][\\-o\\*\\']?[:;=8][<>]?)";
+	private static final String usernames = "@[\\w_]+";
+	private static final String hashtags = "\\#[\\w_]+[\\w\\'_\\-]*[\\w_]+";
+	private static final String links = "\\b(((ht|f)tp(s?)\\:\\/\\/|~\\/|\\/)|www.)(\\w+:\\w+@)?(([-\\w]+\\.)+(com|org|net|gov|mil|biz|info|mobi|name|aero|jobs|museum|travel|[a-z]{2}))(:[\\d]{1,5})?(((\\/([-\\w~!$+|.,=]|%[a-f\\d]{2})+)+|\\/)+|\\?|#)?((\\?([-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)(&(?:[-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)*)*(#([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)?\\b"; // "http\\:\\/\\/.*?\\s";
+
+	private static final String specialcases = "(\\.\\.\\.)|([\\.0oO\\*-\\^]_+[\\.0oO\\*-\\^])";// \\.0oO\\*@-\\^
+
+	// 1. finds emoticons
+	// 2. finds usernames -> adds them lowercased
+	// 3. finds hashtags -> adds them lowercased
+	// 4. normalize repetitions of all characters
+	// 5. maintain capitalization of "apple"
+	// 6. remove commas, colons, semicolons, hyphens?
+	// possible remove RT and -
+
[…]

### 2012-12-02 classify/src/main/java/pipe/TokenizerToTwoToo.java

@@ -1,0 +1,142 @@
+package pipe;
+
+import java.util.HashMap;
+import java.util.Map;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+import cc.mallet.types.TokenSequence;
+
+/**
+ * Custom tokenizer.
+ */
+public class TokenizerToTwoToo extends Pipe {
+
+	private static final long serialVersionUID = 1013696874537828543L;
+	private static final String emoticons = "([<>]?[:;=8][\\-o\\*\\']?[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\\\]|[\\)\\]\\(\\[dDP/\\:\\}\\{@\\|\\\\][\\-o\\*\\']?[:;=8][<>]?)";
+	private static final String usernames = "@[\\w_]+";
+	private static final String hashtags = "\\#[\\w_]+[\\w\\'_\\-]*[\\w_]+";
+
+	// 1. finds emoticons
+	// 2. finds usernames -> adds them lowercased
+	// 3. finds hashtags -> adds them lowercased
+	// 4. split apart repeated ? and !
+	// 5. normalize repetitions of alpha chars and periods
+	//
+
+	public Instance pipe(Instance carrier) {
+		TokenSequence ts = new TokenSequence();
+
+		String str = (String) carrier.getData();
+		// tokenize(str, ts);
+		System.out.println("Original tweet: " + str);
+		Map<Integer, String> matches = new HashMap<Integer, String>();
+		Map<String, Integer> unmatchedAfterEmoticons = new HashMap<String, Integer>();// offset,
+
+		Pattern p = Pattern.compile(emoticons);
+		Matcher m = p.matcher(str);
+		int earliestUnmatched = 0;
+		int prevEnd = earliestUnmatched;
+		while (m.find()) {
+			matches.put(m.start(), m.group());
+			unmatchedAfterEmoticons.put(str.substring(prevEnd, m.start()),
+					m.start());
+			prevEnd = m.end();
+		}
+		if (prevEnd == 0) {
+			unmatchedAfterEmoticons.put(str, 0);
+		} else {
+			unmatchedAfterEmoticons.put(str.substring(prevEnd), prevEnd);
+		}
+
+		Map<String, Integer> unmatchedAfterUsernames = new HashMap<String, Integer>();// offset,
+		Pattern userPattern = Pattern.compile(usernames);
[…]

### 2012-12-02 classify/src/main/java/pipe/TwitterFeatures.java

@@ -1,0 +1,46 @@
+package pipe;
+
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+/**
+ * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
+ * 
+ */
+public class TwitterFeatures extends Pipe {
+
+	private static final long serialVersionUID = 864155191114123362L;
+
+	public Instance pipe(Instance carrier) {
+		// pipe.add(new
+		// CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b",
+		// Pattern.CASE_INSENSITIVE), "HTTPLINK"));
+		// pipe.add( new
+		// CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+",
+		// Pattern.CASE_INSENSITIVE), "@USERLINK"));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\'"), ""));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"));
+		// pipe.add(new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"));
+		String car = (String) carrier.getData();
+		Pattern apple = Pattern.compile("@apple", Pattern.CASE_INSENSITIVE);
+		Matcher m = apple.matcher(car);
+		car = m.replaceAll("NEWSTRINGPATTERN");
+		Pattern at = Pattern.compile("\\@[\\p{L}\\p{Mn}]+",
+				Pattern.CASE_INSENSITIVE);
+		car = at.matcher(car).replaceAll("ATREFERENCE");
+		car = car.replaceAll("NEWSTRINGPATTERN", "@apple");
+
+		Pattern apple2 = Pattern.compile("#apple", Pattern.CASE_INSENSITIVE);
+		Matcher m2 = apple2.matcher(car);
+		car = m2.replaceAll("NEWSTRINGPATTERN");
+		Pattern at2 = Pattern.compile("\\#[\\p{L}\\p{Mn}]+",
+				Pattern.CASE_INSENSITIVE);
+		car = at2.matcher(car).replaceAll("ATREFERENCE");
+		car = car.replaceAll("NEWSTRINGPATTERN", "#apple");
+
+		return carrier;
+	}
+}

### 2012-12-02 classify/src/main/java/pipe/TwitterPipe.java

@@ -1,0 +1,69 @@
+package pipe;
+
+import java.util.regex.Pattern;
+
+
+import cc.mallet.pipe.CharSequence2TokenSequence;
+import cc.mallet.pipe.CharSequenceLowercase;
+import cc.mallet.pipe.CharSequenceReplace;
+import cc.mallet.pipe.FeatureSequence2AugmentableFeatureVector;
+import cc.mallet.pipe.Noop;
+import cc.mallet.pipe.Pipe;
+import cc.mallet.pipe.SerialPipes;
+import cc.mallet.pipe.TokenSequence2FeatureSequence;
+import cc.mallet.pipe.TokenSequenceRemoveStopwords;
+import cc.mallet.types.Instance;
+
+/**
+ * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/TwitterPipe.java?r=10
+ *
+ */
+public class TwitterPipe extends Pipe {
+
+    private boolean anonmymize = true;
+    private boolean emoticons = true;
+    
+    private String corePattern = "([\\@\\#]?[\\p{L}\\p{Mn}][\\p{L}\\p{Mn}'_]+)|([!?]+)";
+    private String emoticonPattern = "([:;=x][-o^]?[)(/\\\\dp])|([/\\\\)(dp][-o^]?[:;=x])";
+
+    private Pipe myPipe = new SerialPipes(new Pipe[] {
+            new CopyData2Source(),
+//            new CharSequenceLowercase(),
+            anonmymize 
+            ? new CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b", Pattern.CASE_INSENSITIVE), "HTTPLINK") 
+            : new Noop(),
+            anonmymize 
+            ? new CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+", Pattern.CASE_INSENSITIVE), "@USERLINK") 
+            : new Noop(),
+            new CharSequenceReplace(Pattern.compile("\\'"), ""),
+            new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"),
+            new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"),
+//            new CharSequenceReplace(Pattern.compile("\\bno\\s+"), "no_"),
+//            new CharSequenceReplace(Pattern.compile("\\bnot\\s+"), "not_"),
+//            new CharSequenceReplace(Pattern.compile("\\bdoesnt\\s+"), "doesnt_"),
[…]

### 2012-12-02 classify/src/main/java/pipe/UnescapeHTML.java

@@ -1,0 +1,50 @@
+package pipe;
+
+import org.apache.commons.lang.StringEscapeUtils;
+
+import cc.mallet.pipe.Pipe;
+import cc.mallet.types.Instance;
+
+/**
+ * Replaces tokens like &gt; with >, etc.
+ */
+public class UnescapeHTML extends Pipe {
+
+	private static final long serialVersionUID = 1013696874537828543L;
+	private static final String emoticons = "(?:" + "[<>]?" + "[:;=8]"
+			+ "[\\-o\\*\\']?" + "[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\]" + "|"
+			+ "[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\]" + "[\\-o\\*\\']?" + "[:;=8]"
+			+ "[<>]?" + ")";
+
+	public Instance pipe(Instance carrier) {
+		String str = (String) carrier.getData();
+		// System.out.println("----------------------------------------------");
+		// System.out.println("Before UnescapeHTML: " + str);
+		String str2 = StringEscapeUtils.unescapeHtml(str);
+		if (!str2.equals(str)) {
+			// System.out.println(str);
+			// System.out.println(str2);
+			// System.out.println("----------------");
+			carrier.setData(str2);
+		}
+		// str2 = str2.replaceAll("([A-Za-z])\\1{3,}", "$1$1$1").replaceAll(
+		// "\\.{2,}", " ... ");
+		//
+		// String split[] = str2.split("\\s+");
+		// StringBuilder sb = new StringBuilder();
+		// for (int i = 0; i < split.length; i++) {
+		// if (split[i].equals(split[i].toUpperCase())) {
+		// sb.append(split[i]);
+		// } else if (!split[i].contains("http://") &&
+		// !split[i].equalsIgnoreCase("apple")) {
+		// sb.append(split[i].toLowerCase());
+		// } else {
+		// sb.append(split[i]);
+		// }
+		// sb.append(" ");
+		// }
+		// carrier.setData(sb.toString());
+		// System.out.println("After UnescapeHTML: " + sb);
+		return carrier;
+	}
+}

### 2012-12-02 classify/src/main/java/classification/Apple.java
removed old pipes

@@ -1,23 +1,0 @@
-package classification;
-
-import java.util.Random;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-
-public class Apple extends Pipe {
-	
-	
-	@Override
-	public Instance pipe(Instance carrier) {
-		Random gen = new Random(System.currentTimeMillis());
-		
-		StringBuilder apple = new StringBuilder();
-		for (int i = 0; i < gen.nextInt(42); ++i) {
-			apple.append("Apple ");
-		}
-		
-		carrier.setData(apple.toString());
-		return carrier;
-	}
-}

### 2012-12-02 classify/src/main/java/classification/CopyData2Source.java

@@ -1,18 +1,0 @@
-package classification;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-
-/**
- * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/CopyData2Source.java?r=10
- *
- */
-public class CopyData2Source extends Pipe {
-    private static final long serialVersionUID = 1;
-
-    public Instance pipe (Instance carrier) {
-        carrier.setSource(carrier.getData());
-        return carrier;
-    }
-
-}

### 2012-12-02 classify/src/main/java/classification/Emotes.java

@@ -1,55 +1,0 @@
-package classification;
-
-import java.util.regex.Pattern;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-/**
- * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
- *
- */
-public class Emotes extends Pipe {
-
-    private static final long serialVersionUID = -22701908667551888L;
-    
-    private Pattern smile = Pattern.compile("#(^|\\W)(\\>\\:\\]|\\:-\\)|\\:\\)|\\:o\\)|\\:\\]|\\:3|\\:c\\)|\\:\\>|\\=\\]|8\\)|\\=\\)|\\:\\}|\\:\\^\\))($|\\W)#");
-    private Pattern laugh = Pattern.compile("#(^|\\W)(\\>\\:D|\\:-D|\\:D|8-D|x-D|X-D|\\=-D|\\=D|\\=-3|8-\\)|xD|XD|8D|\\=3)($|\\W)#");
-    private Pattern sad = Pattern.compile("#(^|\\W)(\\>\\:\\[|\\:-\\(|\\:\\(|\\:-c|\\:c|\\:-\\<|\\:-\\[|\\:\\[|\\:\\{|\\>\\.\\>|\\<\\.\\<|\\>\\.\\<)($|\\W)#");
-    private Pattern wink = Pattern.compile("#(^|\\W)(\\>;\\]|;-\\)|;\\)|\\*-\\)|\\*\\)|;-\\]|;\\]|;D|;\\^\\))($|\\W)#");
-    private Pattern tongue = Pattern.compile("#(^|\\W)(\\>\\:P|\\:-P|\\:P|X-P|x-p|\\:-p|\\:p|\\=p|\\:-Þ|\\:Þ|\\:-b|\\:b|\\=p|\\=P|xp|XP|xP|Xp)($|\\W)#");
-    private Pattern surprise = Pattern.compile("#(^|\\W)(\\>\\:o|\\>\\:O|\\:-O|\\:O|°o°|°O°|\\:O|o_O|o\\.O|8-0)($|\\W)#");
-    private Pattern annoyed = Pattern.compile("#(^|\\W)(\\>\\:\\\\|\\>\\:/|\\:-/|\\:-\\.|\\:\\\\|\\=/|\\=\\\\|\\:S|\\:\\/)($|\\W)#");
[…]

### 2012-12-02 classify/src/main/java/classification/FixEmoticons.java

@@ -1,38 +1,0 @@
-package classification;
-
-import java.util.regex.Matcher;
-import java.util.regex.Pattern;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-
-/**
- * Source : http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/FixEmoticons.java?r=10
- *
- */
-public class FixEmoticons extends Pipe {
-    
-    private Pattern regex;
-    
-    public FixEmoticons(Pattern regex) {
-        this.regex = regex;
-    }
-
-    public Instance pipe (Instance carrier) {
-        String text = (String) carrier.getData();
-        Matcher m = regex.matcher(text);
-
-        StringBuilder sb = new StringBuilder();
-        int last = 0;
-        while (m.find()) {
-            sb.append(text.substring(last, m.start()));
-            sb.append(m.group(0).toUpperCase());
-            last = m.end();
-        }
-        sb.append(text.substring(last));
-
-        carrier.setData(sb.toString());
-        return carrier;
-    }
-
-}

### 2012-12-02 classify/src/main/java/classification/Labelize.java

@@ -1,40 +1,0 @@
-package classification;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Alphabet;
-import cc.mallet.types.Instance;
-import cc.mallet.types.Label;
-import cc.mallet.types.LabelAlphabet;
-
-/**
- * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/Labelize.java?r=10
- *
- */
-public class Labelize extends Pipe {
-    private final static long serialVersionUID = -461155063551297878L; //-8390758647439705273L; 
-
-    public Labelize (Alphabet dataAlphabet, LabelAlphabet labelAlphabet) {
-        super(dataAlphabet, labelAlphabet);
-    }
-
-    public Labelize ()
-    {
-        this(null, new LabelAlphabet());
-    }
-
-    public Labelize (LabelAlphabet labelAlphabet)
-    {
-        this(null, labelAlphabet);
-    }
-
-    public Instance pipe (Instance carrier)
-    {
-        if (carrier.getTarget() != null) {
-            if (carrier.getTarget() instanceof Label)
-                return carrier;
-            LabelAlphabet ldict = (LabelAlphabet) getTargetAlphabet();
-            carrier.setTarget(ldict.lookupLabel (carrier.getTarget()));
-        }
-        return carrier;
-    }
-}

### 2012-12-02 classify/src/main/java/classification/Link2Title.java

@@ -1,79 +1,0 @@
-package classification;
-
-import java.io.IOException;
-import java.util.regex.Matcher;
-import java.util.regex.Pattern;
-
-import org.jsoup.Jsoup;
-import org.jsoup.nodes.Document;
-
-import common.Constants;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-
-public class Link2Title extends Pipe {
-	
-	/**
-	 * 
-	 */
-	private static final long serialVersionUID = 6856138170442079105L;
-
-	/**
-	 * This assumes that the carrier still has the Tweet Text STRING in the data field
-	 */
-	@Override
-	public Instance pipe(Instance carrier) {
-		Pattern httpPattern = Pattern.compile(Constants.HTTP_REGEX);
-		
-		String text = (String) carrier.getData();
-				
-		if (text == null) {
-			return carrier;
-		}
-		
-		Matcher m = httpPattern.matcher(text);
-		
-		StringBuilder sb = new StringBuilder();
-		
-		/*
-		 * We assume that the tweet uses at least somewhat proper English and
-		 * has spaces between each word. That way we can just look at each word, see if it's a link,
-		 * look it up if it is, otherwise just append the string, and move on.
-		 */
-		
-		for (String s: text.split("\\s+")) {
-			//We found a link so look it up
-			if (s.matches(Constants.HTTP_REGEX) && m.find()) {
-				String url = m.group();
-				Document doc = null;
-				try {
-					doc = Jsoup.connect(url).get();
-					if (doc.title() != null && !doc.title().equals("")) {
-						//Flawless victory!
-						sb.append(doc.title());
-						System.out.println("replaced " + url + " with " + doc.title());
-					}
-					else {
-						//try to resolve the url
-						sb.append(doc.baseUri());
-						System.out.println("replaced " + url + " with " + doc.baseUri());
-					}
-				} catch (IOException e) {
-					//Ignore it and put the url back into the string
-					sb.append(url);
-					System.out.println("did not replace url " + url);
-				}
-			}
-			//Regular word so just throw it into the result
-			else {
-				sb.append(s);
-			}
-			sb.append(" ");
-		}
-		
-		System.out.println("After replacing: " + sb.toString());
-		carrier.setData(sb.toString());
-		return carrier;
-	}
-}

### 2012-12-02 classify/src/main/java/classification/SpellCheck.java

@@ -1,86 +1,0 @@
-package classification;
-
-import java.io.File;
-import java.io.FileNotFoundException;
-import java.io.IOException;
-import java.util.List;
-import java.util.StringTokenizer;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-
-import com.swabunga.spell.engine.SpellDictionaryHashMap;
-import com.swabunga.spell.engine.Word;
-import com.swabunga.spell.event.SpellChecker;
-
-public class SpellCheck extends Pipe {
-
-	/**
-	 * 
-	 */
-	private static final long serialVersionUID = 5452951467629627217L;
-	
-	private SpellDictionaryHashMap dictionary;
-	private SpellChecker spellchecker;
-	
-	private String dictionaryLoc = "../classify/eng_com.dic";
-	private int threshold = 100;
-	
-	//Look at this block!
-	{
-		try {
-			dictionary = new SpellDictionaryHashMap(new File(dictionaryLoc));
-			spellchecker = new SpellChecker(dictionary);
-		} catch (FileNotFoundException e) {
-			// TODO Auto-generated catch block
-			e.printStackTrace();
-		} catch (IOException e) {
-			// TODO Auto-generated catch block
-			e.printStackTrace();
-		}
-	}
-	
-	
-	/**
-	 * Takes the given instance and does a spell check on the tweet text, replacing misspelled words with the
-	 * best correction. The spell check is taken from the Google SpellChecker api
-	 */
-	@Override
-	public Instance pipe(Instance carrier) {
-		String text = (String) carrier.getData();
-		
-		if (text == null) {
-			return carrier;
-		}
-		
-		StringTokenizer st = new StringTokenizer(text);
-		StringBuilder result = new StringBuilder();
-		while (st.hasMoreTokens()) {
-			String token = st.nextToken();
-			//One letter words don't play well  with others
-			if (token.length() != 1) {
-				List<Word> words = (List<Word>) spellchecker.getSuggestions(token, threshold);
-				Word best = findBest(words);
-				token = (best != null && best.getCost() < threshold) ? best.getWord() : token;
-			}
-			result.append(token).append(" ");
-		}
-		carrier.setData(result.toString());
-		return carrier;
-	}
-	
-	private Word findBest(List<Word> words) {
-		if (words.size() == 0) {
-			return null;
-		}
-		Word best = words.get(0);
-		for (Word w: words) {
[…]

### 2012-12-02 classify/src/main/java/classification/Stemmer.java

@@ -1,49 +1,0 @@
-package classification;
-
-import java.io.IOException;
-import java.io.ObjectInputStream;
-
-import org.tartarus.snowball.ext.PorterStemmer;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-import cc.mallet.types.Token;
-import cc.mallet.types.TokenSequence;
-/**
- * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
- *
- */
-public class Stemmer extends Pipe {
-
-	private transient PorterStemmer stemmer;
-
-    private static final long serialVersionUID = -2270190864067551888L;
-
-    public Stemmer() {
-            stemmer = new PorterStemmer();
-    }
-
-    private void readObject(ObjectInputStream aInputStream)
-                    throws ClassNotFoundException, IOException {
-            aInputStream.defaultReadObject();
-            stemmer = new PorterStemmer();
-    }
-
-    public Instance pipe(Instance carrier) {
-            TokenSequence tokenSequence = (TokenSequence) carrier.getData();
-            TokenSequence stemmedTokenSequence = new TokenSequence();
-
-            for (int i = 0; i < tokenSequence.size(); i++) {
-                    Token token = tokenSequence.get(i);
-                    stemmer.setCurrent(token.getText());
-                    stemmer.stem();
-                    String s = stemmer.getCurrent();
-                    stemmedTokenSequence.add(new Token(s));
-//                    if (!token.getText().equals(s)) {
-//                    System.out.println(token.getText() + "   :   " + s);
-//                    }
-            }
-            carrier.setData(stemmedTokenSequence);
-            return carrier;
-    }
-}

### 2012-12-02 classify/src/main/java/classification/TokenSequenceBiGrammer.java

@@ -1,23 +1,0 @@
-package classification;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-import cc.mallet.types.TokenSequence;
-
-/**
- * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/TokenSequenceBiGrammer.java?r=10
- *
- */
-public class TokenSequenceBiGrammer extends Pipe {
-
-    public Instance pipe (Instance carrier) {
-        TokenSequence ts = (TokenSequence) carrier.getData();
-        int size = ts.size();
-        for (int i = 1; i < size; i++) {
-            ts.add (ts.get(i-1).getText() + "_" + ts.get(i).getText());
-        }
-        carrier.setData(ts);
-        return carrier;
-    }
-
-}

### 2012-12-02 classify/src/main/java/classification/Tokenizer.java

@@ -1,120 +1,0 @@
-package classification;
-
-import java.util.ArrayList;
-import java.util.List;
-import java.util.regex.Matcher;
-import java.util.regex.Pattern;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-import cc.mallet.types.TokenSequence;
-
-/**
- * Custom tokenizer.
- */
-public class Tokenizer extends Pipe {
-
-	private static final long serialVersionUID = 1013696874537828543L;
-	// "-_+-
-	private static final String emoticons = "([<>]?[:;=8][\\-o\\*\\']?[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\\\]|[\\)\\]\\(\\[dDP/\\:\\}\\{@\\|\\\\][\\-o\\*\\']?[:;=8][<>]?)";
-	private static final String usernames = "@[\\w_]+";
-	private static final String hashtags = "\\#[\\w_]+[\\w\\'_\\-]*[\\w_]+";
-	private static final String links = "\\b(((ht|f)tp(s?)\\:\\/\\/|~\\/|\\/)|www.)(\\w+:\\w+@)?(([-\\w]+\\.)+(com|org|net|gov|mil|biz|info|mobi|name|aero|jobs|museum|travel|[a-z]{2}))(:[\\d]{1,5})?(((\\/([-\\w~!$+|.,=]|%[a-f\\d]{2})+)+|\\/)+|\\?|#)?((\\?([-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)(&(?:[-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)*)*(#([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)?\\b"; // "http\\:\\/\\/.*?\\s";
-
-	private static final String specialcases = "(\\.\\.\\.)|([\\.0oO\\*-\\^]_+[\\.0oO\\*-\\^])";// \\.0oO\\*@-\\^
-
-	// 1. finds emoticons
-	// 2. finds usernames -> adds them lowercased
-	// 3. finds hashtags -> adds them lowercased
-	// 4. normalize repetitions of all characters
-	// 5. maintain capitalization of "apple"
-	// 6. remove commas, colons, semicolons, hyphens?
-	// possible remove RT and -
-
[…]

### 2012-12-02 classify/src/main/java/classification/TokenizerToTwoToo.java

@@ -1,142 +1,0 @@
-package classification;
-
-import java.util.HashMap;
-import java.util.Map;
-import java.util.regex.Matcher;
-import java.util.regex.Pattern;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-import cc.mallet.types.TokenSequence;
-
-/**
- * Custom tokenizer.
- */
-public class TokenizerToTwoToo extends Pipe {
-
-	private static final long serialVersionUID = 1013696874537828543L;
-	private static final String emoticons = "([<>]?[:;=8][\\-o\\*\\']?[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\\\]|[\\)\\]\\(\\[dDP/\\:\\}\\{@\\|\\\\][\\-o\\*\\']?[:;=8][<>]?)";
-	private static final String usernames = "@[\\w_]+";
-	private static final String hashtags = "\\#[\\w_]+[\\w\\'_\\-]*[\\w_]+";
-
-	// 1. finds emoticons
-	// 2. finds usernames -> adds them lowercased
-	// 3. finds hashtags -> adds them lowercased
-	// 4. split apart repeated ? and !
-	// 5. normalize repetitions of alpha chars and periods
-	//
-
-	public Instance pipe(Instance carrier) {
-		TokenSequence ts = new TokenSequence();
-
-		String str = (String) carrier.getData();
-		// tokenize(str, ts);
-		System.out.println("Original tweet: " + str);
-		Map<Integer, String> matches = new HashMap<Integer, String>();
-		Map<String, Integer> unmatchedAfterEmoticons = new HashMap<String, Integer>();// offset,
-
-		Pattern p = Pattern.compile(emoticons);
-		Matcher m = p.matcher(str);
-		int earliestUnmatched = 0;
-		int prevEnd = earliestUnmatched;
-		while (m.find()) {
-			matches.put(m.start(), m.group());
-			unmatchedAfterEmoticons.put(str.substring(prevEnd, m.start()),
-					m.start());
-			prevEnd = m.end();
-		}
-		if (prevEnd == 0) {
-			unmatchedAfterEmoticons.put(str, 0);
-		} else {
-			unmatchedAfterEmoticons.put(str.substring(prevEnd), prevEnd);
-		}
-
-		Map<String, Integer> unmatchedAfterUsernames = new HashMap<String, Integer>();// offset,
-		Pattern userPattern = Pattern.compile(usernames);
[…]

### 2012-12-02 classify/src/main/java/classification/TwitterFeatures.java

@@ -1,46 +1,0 @@
-package classification;
-
-import java.util.regex.Matcher;
-import java.util.regex.Pattern;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-
-/**
- * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
- * 
- */
-public class TwitterFeatures extends Pipe {
-
-	private static final long serialVersionUID = 864155191114123362L;
-
-	public Instance pipe(Instance carrier) {
-		// pipe.add(new
-		// CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b",
-		// Pattern.CASE_INSENSITIVE), "HTTPLINK"));
-		// pipe.add( new
-		// CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+",
-		// Pattern.CASE_INSENSITIVE), "@USERLINK"));
-		// pipe.add(new CharSequenceReplace(Pattern.compile("\\'"), ""));
-		// pipe.add(new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"));
-		// pipe.add(new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"));
-		String car = (String) carrier.getData();
-		Pattern apple = Pattern.compile("@apple", Pattern.CASE_INSENSITIVE);
-		Matcher m = apple.matcher(car);
-		car = m.replaceAll("NEWSTRINGPATTERN");
-		Pattern at = Pattern.compile("\\@[\\p{L}\\p{Mn}]+",
-				Pattern.CASE_INSENSITIVE);
-		car = at.matcher(car).replaceAll("ATREFERENCE");
-		car = car.replaceAll("NEWSTRINGPATTERN", "@apple");
-
-		Pattern apple2 = Pattern.compile("#apple", Pattern.CASE_INSENSITIVE);
-		Matcher m2 = apple2.matcher(car);
-		car = m2.replaceAll("NEWSTRINGPATTERN");
-		Pattern at2 = Pattern.compile("\\#[\\p{L}\\p{Mn}]+",
-				Pattern.CASE_INSENSITIVE);
-		car = at2.matcher(car).replaceAll("ATREFERENCE");
-		car = car.replaceAll("NEWSTRINGPATTERN", "#apple");
-
-		return carrier;
-	}
-}

### 2012-12-02 classify/src/main/java/classification/TwitterPipe.java

@@ -1,68 +1,0 @@
-package classification;
-
-import java.util.regex.Pattern;
-
-import cc.mallet.pipe.CharSequence2TokenSequence;
-import cc.mallet.pipe.CharSequenceLowercase;
-import cc.mallet.pipe.CharSequenceReplace;
-import cc.mallet.pipe.FeatureSequence2AugmentableFeatureVector;
-import cc.mallet.pipe.Noop;
-import cc.mallet.pipe.Pipe;
-import cc.mallet.pipe.SerialPipes;
-import cc.mallet.pipe.TokenSequence2FeatureSequence;
-import cc.mallet.pipe.TokenSequenceRemoveStopwords;
-import cc.mallet.types.Instance;
-
-/**
- * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/TwitterPipe.java?r=10
- *
- */
-public class TwitterPipe extends Pipe {
-
-    private boolean anonmymize = true;
-    private boolean emoticons = true;
-    
-    private String corePattern = "([\\@\\#]?[\\p{L}\\p{Mn}][\\p{L}\\p{Mn}'_]+)|([!?]+)";
-    private String emoticonPattern = "([:;=x][-o^]?[)(/\\\\dp])|([/\\\\)(dp][-o^]?[:;=x])";
-
-    private Pipe myPipe = new SerialPipes(new Pipe[] {
-            new CopyData2Source(),
-//            new CharSequenceLowercase(),
-            anonmymize 
-            ? new CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b", Pattern.CASE_INSENSITIVE), "HTTPLINK") 
-            : new Noop(),
-            anonmymize 
-            ? new CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+", Pattern.CASE_INSENSITIVE), "@USERLINK") 
-            : new Noop(),
-            new CharSequenceReplace(Pattern.compile("\\'"), ""),
-            new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"),
-            new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"),
-//            new CharSequenceReplace(Pattern.compile("\\bno\\s+"), "no_"),
-//            new CharSequenceReplace(Pattern.compile("\\bnot\\s+"), "not_"),
-//            new CharSequenceReplace(Pattern.compile("\\bdoesnt\\s+"), "doesnt_"),
[…]

### 2012-12-02 classify/src/main/java/classification/UnescapeHTML.java

@@ -1,50 +1,0 @@
-package classification;
-
-import org.apache.commons.lang.StringEscapeUtils;
-
-import cc.mallet.pipe.Pipe;
-import cc.mallet.types.Instance;
-
-/**
- * Replaces tokens like &gt; with >, etc.
- */
-public class UnescapeHTML extends Pipe {
-
-	private static final long serialVersionUID = 1013696874537828543L;
-	private static final String emoticons = "(?:" + "[<>]?" + "[:;=8]"
-			+ "[\\-o\\*\\']?" + "[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\]" + "|"
-			+ "[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\]" + "[\\-o\\*\\']?" + "[:;=8]"
-			+ "[<>]?" + ")";
-
-	public Instance pipe(Instance carrier) {
-		String str = (String) carrier.getData();
-		// System.out.println("----------------------------------------------");
-		// System.out.println("Before UnescapeHTML: " + str);
-		String str2 = StringEscapeUtils.unescapeHtml(str);
-		if (!str2.equals(str)) {
-			// System.out.println(str);
-			// System.out.println(str2);
-			// System.out.println("----------------");
-			carrier.setData(str2);
-		}
-		// str2 = str2.replaceAll("([A-Za-z])\\1{3,}", "$1$1$1").replaceAll(
-		// "\\.{2,}", " ... ");
-		//
-		// String split[] = str2.split("\\s+");
-		// StringBuilder sb = new StringBuilder();
-		// for (int i = 0; i < split.length; i++) {
-		// if (split[i].equals(split[i].toUpperCase())) {
-		// sb.append(split[i]);
-		// } else if (!split[i].contains("http://") &&
-		// !split[i].equalsIgnoreCase("apple")) {
-		// sb.append(split[i].toLowerCase());
-		// } else {
-		// sb.append(split[i]);
-		// }
-		// sb.append(" ");
-		// }
-		// carrier.setData(sb.toString());
-		// System.out.println("After UnescapeHTML: " + sb);
-		return carrier;
-	}
-}

### 2012-12-02 classify/src/main/java/common/PipeFactory.java
added classpath and prefs

@@ -6,6 +6,10 @@ import java.util.Iterator;
 import java.util.List;
 import java.util.regex.Pattern;
 
+import pipe.Stemmer;
+import pipe.Tokenizer;
+import pipe.UnescapeHTML;
+
 import cc.mallet.pipe.CharSequence2TokenSequence;
 import cc.mallet.pipe.CharSequenceLowercase;
 import cc.mallet.pipe.FeatureSequence2FeatureVector;
@@ -16,9 +20,6 @@ import cc.mallet.pipe.Target2Label;
 import cc.mallet.pipe.TokenSequence2FeatureSequence;
 import cc.mallet.pipe.TokenSequenceNGrams;
 import cc.mallet.pipe.TokenSequenceRemoveStopwords;
-import classification.Stemmer;
-import classification.Tokenizer;
-import classification.UnescapeHTML;
 
 import com.google.common.collect.Iterators;
 

### 2012-12-02 classify/src/main/java/common/PipeFactory.java
updated tokenizer configurability

@@ -1,15 +1,14 @@
 package common;
 
 import java.util.ArrayList;
-import java.util.Arrays;
 import java.util.Iterator;
 import java.util.List;
 import java.util.regex.Pattern;
 
 import pipe.Stemmer;
 import pipe.Tokenizer;
+import pipe.Tokenizer.Case;
 import pipe.UnescapeHTML;
-
 import cc.mallet.pipe.CharSequence2TokenSequence;
 import cc.mallet.pipe.CharSequenceLowercase;
 import cc.mallet.pipe.FeatureSequence2FeatureVector;
@@ -21,16 +20,13 @@ import cc.mallet.pipe.TokenSequence2FeatureSequence;
 import cc.mallet.pipe.TokenSequenceNGrams;
 import cc.mallet.pipe.TokenSequenceRemoveStopwords;
 
-import com.google.common.collect.Iterators;
-
 public class PipeFactory {
 
 	public static Iterator<SetItem<SerialPipes>> getPipes() {
 		return new SetCombiner<SerialPipes, Pipe>() {
 
 			@Override
-			public SetItem<SerialPipes> combine(List<Pipe> pipes,
-					List<String> labels) {
+			public SetItem<SerialPipes> combine(List<Pipe> pipes, List<String> labels) {
 
 				return new SetItem<SerialPipes>(new SerialPipes(pipes),
 						labels.toString());
@@ -47,25 +43,28 @@ public class PipeFactory {
 			@Override
 			protected void build() {
 				this.add(
-						new CharSequence2TokenSequence(Pattern
-								.compile("[\\p{L}\\p{N}_]+")), "numdig tokenizer");
-				this.add(
-						new CharSequence2TokenSequence(Pattern
-								.compile("[^\\s]+")), "whitespace tokenizer");
-				this.add(new Tokenizer(), "twitter tokenizer");
+						new CharSequence2TokenSequence(Pattern.compile("[\\p{L}\\p{N}_]+")),
+						"numdig tokenizer");
+				this.add(new CharSequence2TokenSequence(Pattern.compile("[^\\s]+")),
+						"whitespace tokenizer");
+				this.add(new Tokenizer(false, false, false, false, false, false, false, false, false, Case.lower), "simplistic twitter tokenizer");
+				this.add(new Tokenizer(true, true, true, true, true, false, true, true, false, Case.lower), "twitter tokenizer with no RT,appleCase, and noPunct removed");
[…]

### 2012-12-02 classify/src/main/java/pipe/Tokenizer.java

@@ -30,6 +30,47 @@ public class Tokenizer extends Pipe {
 	// 5. maintain capitalization of "apple"
 	// 6. remove commas, colons, semicolons, hyphens?
 	// possible remove RT and -
+	public Tokenizer() {
+		this(true, true, true, true, true, true, true, true, true, Case.apple);
+	}
+
+	public Tokenizer(boolean print) {
+		this(true, true, true, true, true, true, true, true, print, Case.apple);
+
+	}
+
+	public Tokenizer(boolean doEmoticons, boolean doUsernames,
+			boolean doHashtags, boolean doLinks, boolean doSpecialCases,
+			boolean removeRT, boolean normalizeLengths, boolean removePunct,
+			boolean print, Case casing) {
+		this.doEmoticons = doEmoticons;
+		this.doUsernames = doUsernames;
+		this.doHashtags = doHashtags;
+		this.doLinks = doLinks;
+		this.doSpecialCases = doSpecialCases;
+		this.removeRT = removeRT;
+		this.normalizeLengths = normalizeLengths;
+		this.removePunct = removePunct;
+		this.casing = casing;
+		this.print = print;
+
+	}
+
+	private boolean doEmoticons;
+	private boolean doUsernames;
+	private boolean doHashtags;
+	private boolean doLinks;
+	private boolean doSpecialCases;
+	private boolean removeRT;
+	private boolean normalizeLengths;
+	private boolean removePunct;// removes any non-word characters from edges of
+															// space-delimited tokens
+	private boolean print;
+	private Case casing;
+
+	public enum Case {
+		lower, nochange, apple;
+	}
 
 	private List<String> match(String regex, TokenSequence ts, String str,
 			boolean toLowercase, String replacement) {
@@ -42,7 +83,9 @@ public class Tokenizer extends Pipe {
 			if (toLowercase) {
 				s = s.toLowerCase();
 			}
-			System.out.println(s);
+			if (print) {
+				System.out.println(s);
+			}
 			ts.add(replacement == null ? s : replacement);
 			if (m.start() >= prevEnd) {
 				ret.add(str.substring(prevEnd, m.start()));
@@ -64,57 +107,101 @@ public class Tokenizer extends Pipe {
 
 	public Instance pipe(Instance carrier) {
 		TokenSequence ts = new TokenSequence();
-		
+
[…]

### 2012-12-02 classify/src/main/java/classification/ModelTester.java
model tester updates

@@ -14,6 +14,9 @@ import java.util.List;
 import java.util.Random;
 import java.util.Scanner;
 
+import org.apache.commons.math3.stat.descriptive.DescriptiveStatistics;
+
+import cc.mallet.classify.Classification;
 import cc.mallet.classify.Classifier;
 import cc.mallet.classify.ClassifierTrainer;
 import cc.mallet.classify.MaxEntTrainer;
@@ -34,23 +37,23 @@ public class ModelTester {
 
 	private static final int random_seed = 0xDEADBEEF;
 
-	private static final int folds = 6;
-	
+	private static final int folds = 10;
+
 	private static final int test_size = 200;
 
 	public static void main(String[] args) throws IOException {
-		
+
 		int d = 40;
 		int max = 1000;
-		
+
 		ArrayList<String> info = new ArrayList<String>();
-		
-		for(int p=d; p<=max; p+=d) {
+
+		for (int p = d; p <= max; p += d) {
 			List<String> r = run(p);
-			for(String s : r)
-				info.add(String.valueOf(p) + " - " + s);
+			for (String s : r)
+				info.add(String.valueOf(p) + "\t" + s);
 		}
-		
+
 		for (String s : info) {
 			System.out.println(s);
 		}
@@ -69,71 +72,68 @@ public class ModelTester {
 
 			ArrayList<Trial> trials = new ArrayList<Trial>();
 
-			info.add(pipeLabel);
-
 			InstanceList instances = new InstanceList(pipe);
 			File file = new File("../corpus/appleBinaryFiltered.txt");
 			CsvIterator reader = new CsvIterator(new FileReader(file),
 					Constants.CSV_ITERATOR_REGEX, 3, 1, 2);
 			instances.addThruPipe(reader);
-			
-			
-			InstanceList[] testSplit = instances.splitInOrder(new int[] {test_size, instances.size()-test_size});
+
+			InstanceList[] testSplit = instances.splitInOrder(new int[] {
+					test_size, instances.size() - test_size });
 			InstanceList testList = testSplit[0];
 			InstanceList trainList = testSplit[1];
 
 			// Filter instances
-			//double proportion = (double)count / trainList.size();
-			InstanceList[] randomInstanceLists = trainList.splitInOrder(new int[] {count, trainList.size()-count});
-//					.split(new Random(random_seed), new double[] { proportion,
-//							1.0 - proportion });
-
-			CrossValidationIterator cvi = new CrossValidationIterator(
[…]

### 2012-12-02 classify/src/main/java/classification/Main.java
automatic formatting

@@ -1,31 +1,26 @@
 package classification;
 
-import java.io.File;
-import java.io.FileWriter;
 import java.io.IOException;
-import java.util.Scanner;
 
 public class Main {
 	public static void main(String... args) throws IOException {
-			//ModelUpdater m = new ModelUpdater();
-			//Classifier c = m.createNewCompanyWikipediaModel();
+		// ModelUpdater m = new ModelUpdater();
+		// Classifier c = m.createNewCompanyWikipediaModel();
 
-	//	Classifier c = 
-		
-		
-		//			Scanner s = new Scanner(new File("../corpus/companies.txt"));
-//			FileWriter f = new FileWriter(new File("../corpus/companyset.txt"));
-//			while (s.hasNextLine()) {
-//				String l = s.nextLine();
-//				String[] split= l.split("\",\"");
-//				if (split.length < 10) {
-//					System.out.println(l);
-//				}
-//				String o = split[1] + " train " + split[9] + "\n";
-//				f.append(o);
-//			}
-//			f.flush();
-//			f.close();
+		// Classifier c =
+
+		// Scanner s = new Scanner(new File("../corpus/companies.txt"));
+		// FileWriter f = new FileWriter(new File("../corpus/companyset.txt"));
+		// while (s.hasNextLine()) {
+		// String l = s.nextLine();
+		// String[] split= l.split("\",\"");
+		// if (split.length < 10) {
+		// System.out.println(l);
+		// }
+		// String o = split[1] + " train " + split[9] + "\n";
+		// f.append(o);
+		// }
+		// f.flush();
+		// f.close();
 	}
-}
-;
+};

### 2012-12-02 classify/src/main/java/classification/ModelTester.java

@@ -9,7 +9,6 @@ import java.io.IOException;
 import java.io.ObjectInputStream;
 import java.util.ArrayList;
 import java.util.Iterator;
-import java.util.LinkedList;
 import java.util.List;
 import java.util.Random;
 import java.util.Scanner;
@@ -20,10 +19,8 @@ import cc.mallet.classify.Classification;
 import cc.mallet.classify.Classifier;
 import cc.mallet.classify.ClassifierTrainer;
 import cc.mallet.classify.MaxEntTrainer;
-import cc.mallet.classify.NaiveBayes;
 import cc.mallet.classify.NaiveBayesTrainer;
 import cc.mallet.classify.Trial;
-import cc.mallet.pipe.Pipe;
 import cc.mallet.pipe.SerialPipes;
 import cc.mallet.pipe.iterator.CsvIterator;
 import cc.mallet.types.CrossValidationIterator;

### 2012-12-02 classify/src/main/java/classification/ModelUpdater.java

@@ -45,8 +45,8 @@ public class ModelUpdater {
 	}
 
 	public Classifier createNewCompanyWikipediaModel() throws IOException {
-		 MaxEntTrainer trainer = new MaxEntTrainer();
-		//NaiveBayesTrainer trainer = new NaiveBayesTrainer();
+		MaxEntTrainer trainer = new MaxEntTrainer();
+		// NaiveBayesTrainer trainer = new NaiveBayesTrainer();
 
 		File file = new File("../corpus/wikorpus.txt");
 

### 2012-12-02 classify/src/main/java/classification/NewPipesTest.java

@@ -18,16 +18,17 @@ import cc.mallet.types.InstanceList;
 import com.google.gson.JsonArray;
 import com.google.gson.JsonElement;
 import com.google.gson.JsonObject;
-
 import common.Constants;
 import common.FileUtil;
 import common.PipeFactory;
 import common.ServerInteractionsUtil;
 
 public class NewPipesTest {
-	
-	public static void main(String[] args) throws HttpException, IOException, URISyntaxException, ClassNotFoundException {
-		StringBuilder json = FileUtil.getTweetsFromLocal("C://Users//Brandon//Documents//School//ComS572//Project//TweetJSON.txt");
+
+	public static void main(String[] args) throws HttpException, IOException,
+			URISyntaxException, ClassNotFoundException {
+		StringBuilder json = FileUtil
+				.getTweetsFromLocal("C://Users//Brandon//Documents//School//ComS572//Project//TweetJSON.txt");
 
 		TweetJsonIterator tji = new TweetJsonIterator(json.toString(),
 				Mode.CLASSIFY, Type.UNCLASSIFIED);

### 2012-12-02 classify/src/main/java/classification/TweetGrabber.java

@@ -48,9 +48,10 @@ public class TweetGrabber {
 		// Classifies the tweets and adds the Labels and values to the
 		// tweetInstance
 		InstanceList il = new InstanceList(PipeFactory.getDefault());
-		Classifier companyClassifier = (new ModelUpdater()).createNewCompanyWikipediaModel();
-//		Classifier companyClassifier = FileUtil
-//				.loadBestClassifier(Constants.COMPANY_MODEL);
+		Classifier companyClassifier = (new ModelUpdater())
+				.createNewCompanyWikipediaModel();
+		// Classifier companyClassifier = FileUtil
+		// .loadBestClassifier(Constants.COMPANY_MODEL);
 		Classifier sentimentClassifier = FileUtil
 				.loadBestClassifier(Constants.SENTIMENT_MODEL);
 		il.addThruPipe(tji);

### 2012-12-02 classify/src/main/java/common/Constants.java

@@ -4,41 +4,44 @@ import java.text.SimpleDateFormat;
 
 public class Constants {
 
-	//String url for getting tweets to classify
+	// String url for getting tweets to classify
 	public static final String NEW_TWEET_GET_URL = "http://danielstiner.com:9001/unclassified/random/100";
-	
-	//String url for posting classified tweets
+
+	// String url for posting classified tweets
 	public static final String CLASSIFIED_TWEET_POST_URL = "http://danielstiner.com:9001/classified/classify";
 
-	//Strings used in the ModelUpdater class. I thought it would be
-	//good to put these here since everything else is here too
+	// Strings used in the ModelUpdater class. I thought it would be
+	// good to put these here since everything else is here too
 	public final static String VERIFIED_URL_PRE = "http://danielstiner.com:9001/verified/company/";
 	public final static String VERIFIED_URL_POST = "/count/";
 	public static final String VERIFIED_COUNTS_URL = "http://danielstiner.com:9001/verified/companies";
-	
-	//Http regex
+
+	// Http regex
 	public static final String HTTP_REGEX = "http\\:\\/\\/([^\\s]+)";
-	
-	//Classifier constant literals
+
+	// Classifier constant literals
 	public static final String COMPANY_MODEL = "companyModel";
 	public static final String SENTIMENT_MODEL = "sentimentModel";
-	
-	//Json tweet properties
+
+	// Json tweet properties
 	public static final String ID_PROPERTY_KEY = "id_str";
 	public static final String COMPANY_PROPERTY_KEY = "company";
 	public static final String SENTIMENT_PROPERTY_KEY = "sentiment";
 	public static final String COMPANY_CONFIDENCE_PROPERTY_KEY = "companyConfidence";
 	public static final String SENTIMENT_CONFIDENCE_PROPERTY_KEY = "sentimentConfidence";
 	public static final String CSTAMP_PROPERTY_KEY = "cstamp";
-	
-	//Date format for saving classifiers
-	public static final SimpleDateFormat PRETTY_SDF = new SimpleDateFormat("yyyy-MM-dd_HH:mm:ss");
-	public static final SimpleDateFormat UGLY_SDF = new SimpleDateFormat("yyyyMMddHHmmss");
[…]

### 2012-12-02 classify/src/main/java/common/FileUtil.java

@@ -85,18 +85,18 @@ public class FileUtil {
 
 	/**
 	 * This method attempts to load the most recently saved classifier from
-	 * 	disk. If the classifier doesn't exist it creates a new one and saves it.
+	 * disk. If the classifier doesn't exist it creates a new one and saves it.
+	 * 
 	 * @param pattern
-	 * 					The type of classifier to create
-	 * @return
-	 * 			The most recently classifier saved or a new one if none have
-	 * 			been saved yet.
+	 *            The type of classifier to create
+	 * @return The most recently classifier saved or a new one if none have been
+	 *         saved yet.
 	 * @throws FileNotFoundException
 	 * @throws ClassNotFoundException
 	 * @throws IOException
 	 */
-	public static Classifier loadBestClassifier(String pattern) throws FileNotFoundException,
-			ClassNotFoundException, IOException {
+	public static Classifier loadBestClassifier(String pattern)
+			throws FileNotFoundException, ClassNotFoundException, IOException {
 		// This can also be replaced by
 		// FileUtil.loadMostRecentClassifierFromDisk
 		File largest = FileUtil.getMostRecentFile(pattern);

### 2012-12-02 classify/src/main/java/common/ModelFactory.java

@@ -16,8 +16,8 @@ public class ModelFactory {
 
 	/**
 	 * A Method to get a newly trained Company Classifier
-	 * @return
-	 * 			The classifier trained on companies
+	 * 
+	 * @return The classifier trained on companies
 	 * @throws FileNotFoundException
 	 */
 	public static Classifier getCompanyClassifier()
@@ -31,17 +31,17 @@ public class ModelFactory {
 		Classifier classifier = trainer.train(instances);
 		return classifier;
 	}
-	
+
 	public static Classifier getBackgroundKnowledgeClassifier() {
 		ClassifierTrainer<NaiveBayes> n = new NaiveBayesWithPriorsTrainer();
-		
+
 		return null;
 	}
-	
+
 	/**
 	 * A Method to get the best available sentiment classifier
-	 * @return
-	 * 			The classifier trained on sentiment
+	 * 
+	 * @return The classifier trained on sentiment
 	 * @throws FileNotFoundException
 	 */
 	public static Classifier getBestSentimentClassifier()
@@ -73,6 +73,5 @@ public class ModelFactory {
 		Classifier classifier = trainer.train(instances);
 		return classifier;
 	}
-	
-	
+
 }

### 2012-12-02 classify/src/main/java/common/PipeFactory.java

@@ -26,7 +26,8 @@ public class PipeFactory {
 		return new SetCombiner<SerialPipes, Pipe>() {
 
 			@Override
-			public SetItem<SerialPipes> combine(List<Pipe> pipes, List<String> labels) {
+			public SetItem<SerialPipes> combine(List<Pipe> pipes,
+					List<String> labels) {
 
 				return new SetItem<SerialPipes>(new SerialPipes(pipes),
 						labels.toString());
@@ -43,12 +44,18 @@ public class PipeFactory {
 			@Override
 			protected void build() {
 				this.add(
-						new CharSequence2TokenSequence(Pattern.compile("[\\p{L}\\p{N}_]+")),
+						new CharSequence2TokenSequence(Pattern
+								.compile("[\\p{L}\\p{N}_]+")),
 						"numdig tokenizer");
-				this.add(new CharSequence2TokenSequence(Pattern.compile("[^\\s]+")),
-						"whitespace tokenizer");
-				this.add(new Tokenizer(false, false, false, false, false, false, false, false, false, Case.lower), "simplistic twitter tokenizer");
-				this.add(new Tokenizer(true, true, true, true, true, false, true, true, false, Case.lower), "twitter tokenizer with no RT,appleCase, and noPunct removed");
+				this.add(
+						new CharSequence2TokenSequence(Pattern
+								.compile("[^\\s]+")), "whitespace tokenizer");
+				this.add(new Tokenizer(false, false, false, false, false,
+						false, false, false, false, Case.lower),
+						"simplistic twitter tokenizer");
+				this.add(new Tokenizer(true, true, true, true, true, false,
+						true, true, false, Case.lower),
+						"twitter tokenizer with no RT,appleCase, and noPunct removed");
 				this.add(new Tokenizer(false), "default twitter tokenizer");
 			}
 

### 2012-12-02 classify/src/main/java/common/ServerInteractionsUtil.java

@@ -41,16 +41,16 @@ public class ServerInteractionsUtil {
 
 	/**
 	 * A method to get tweets from the server
+	 * 
 	 * @param url
-	 * 				The url to find the tweets at
-	 * @return
-	 * 			The Json version of the tweets in a StringBuilder
+	 *            The url to find the tweets at
+	 * @return The Json version of the tweets in a StringBuilder
 	 * @throws URISyntaxException
 	 * @throws HttpException
 	 * @throws IOException
 	 */
-	public static StringBuilder getTweetsFrom(String url) throws URISyntaxException,
-			HttpException, IOException {
+	public static StringBuilder getTweetsFrom(String url)
+			throws URISyntaxException, HttpException, IOException {
 		HttpGet getUrl = new HttpGet(url);
 
 		HttpClient client = new DefaultHttpClient();

### 2012-12-02 classify/src/main/java/common/SetFactory.java

@@ -6,7 +6,7 @@ import java.util.List;
 public abstract class SetFactory<T> {
 
 	private boolean single;
-	
+
 	public SetFactory() {
 		this(false);
 	}

### 2012-12-02 classify/src/main/java/dualist/classify/NaiveBayesWithPriorsTrainer.java

@@ -5,9 +5,6 @@ import java.io.ObjectInputStream;
 import java.io.ObjectOutputStream;
 import java.io.Serializable;
 
-import com.google.common.collect.HashMultimap;
-import com.google.common.collect.Multimap;
-
 import cc.mallet.classify.Boostable;
 import cc.mallet.classify.Classifier;
 import cc.mallet.classify.ClassifierTrainer;
@@ -22,6 +19,9 @@ import cc.mallet.types.Instance;
 import cc.mallet.types.InstanceList;
 import cc.mallet.types.Labeling;
 import cc.mallet.types.Multinomial;
+
+import com.google.common.collect.HashMultimap;
+import com.google.common.collect.Multimap;
 
 /**
  * Class used to generate a NaiveBayes classifier from a training data AND
@@ -380,10 +380,10 @@ public class NaiveBayesWithPriorsTrainer extends ClassifierTrainer<NaiveBayes>
 	}
 
 	/**
-		 * Create a NaiveBayes classifier from a set of training data and the
-		 * previous state of the trainer. Subsequent calls to incrementalTrain() add
-		 * to the state of the trainer. An incremental training session should
-		 * consist only of calls to incrementalTrain() and have no calls to train();
+	 * Create a NaiveBayes classifier from a set of training data and the
+	 * previous state of the trainer. Subsequent calls to incrementalTrain() add
+	 * to the state of the trainer. An incremental training session should
+	 * consist only of calls to incrementalTrain() and have no calls to train();
 	 * *
 	 * 
 	 * @param trainingList

### 2012-12-02 classify/src/main/java/model/TweetJsonIterator.java

@@ -77,8 +77,8 @@ public class TweetJsonIterator implements Iterator<Instance> {
 				throw new IllegalArgumentException("No target present.");
 			}
 		}
-		 System.out.println("creating new instance: [target]=" + target
-		 + " [data]=" + data);
+		System.out.println("creating new instance: [target]=" + target
+				+ " [data]=" + data);
 		Instance carrier = new Instance(data, target, name, o);
 		return carrier;
 	}

### 2012-12-02 classify/src/main/java/pipe/Apple.java

@@ -6,17 +6,16 @@ import cc.mallet.pipe.Pipe;
 import cc.mallet.types.Instance;
 
 public class Apple extends Pipe {
-	
-	
+
 	@Override
 	public Instance pipe(Instance carrier) {
 		Random gen = new Random(System.currentTimeMillis());
-		
+
 		StringBuilder apple = new StringBuilder();
 		for (int i = 0; i < gen.nextInt(42); ++i) {
 			apple.append("Apple ");
 		}
-		
+
 		carrier.setData(apple.toString());
 		return carrier;
 	}

### 2012-12-02 classify/src/main/java/pipe/CopyData2Source.java

@@ -4,15 +4,17 @@ import cc.mallet.pipe.Pipe;
 import cc.mallet.types.Instance;
 
 /**
- * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/CopyData2Source.java?r=10
- *
+ * Source:
+ * http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/
+ * pipes/CopyData2Source.java?r=10
+ * 
  */
 public class CopyData2Source extends Pipe {
-    private static final long serialVersionUID = 1;
+	private static final long serialVersionUID = 1;
 
-    public Instance pipe (Instance carrier) {
-        carrier.setSource(carrier.getData());
-        return carrier;
-    }
+	public Instance pipe(Instance carrier) {
+		carrier.setSource(carrier.getData());
+		return carrier;
+	}
 
 }

### 2012-12-02 classify/src/main/java/pipe/Emotes.java

@@ -4,52 +4,60 @@ import java.util.regex.Pattern;
 
 import cc.mallet.pipe.Pipe;
 import cc.mallet.types.Instance;
+
 /**
  * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
- *
+ * 
  */
 public class Emotes extends Pipe {
 
-    private static final long serialVersionUID = -22701908667551888L;
-    
-    private Pattern smile = Pattern.compile("#(^|\\W)(\\>\\:\\]|\\:-\\)|\\:\\)|\\:o\\)|\\:\\]|\\:3|\\:c\\)|\\:\\>|\\=\\]|8\\)|\\=\\)|\\:\\}|\\:\\^\\))($|\\W)#");
-    private Pattern laugh = Pattern.compile("#(^|\\W)(\\>\\:D|\\:-D|\\:D|8-D|x-D|X-D|\\=-D|\\=D|\\=-3|8-\\)|xD|XD|8D|\\=3)($|\\W)#");
-    private Pattern sad = Pattern.compile("#(^|\\W)(\\>\\:\\[|\\:-\\(|\\:\\(|\\:-c|\\:c|\\:-\\<|\\:-\\[|\\:\\[|\\:\\{|\\>\\.\\>|\\<\\.\\<|\\>\\.\\<)($|\\W)#");
-    private Pattern wink = Pattern.compile("#(^|\\W)(\\>;\\]|;-\\)|;\\)|\\*-\\)|\\*\\)|;-\\]|;\\]|;D|;\\^\\))($|\\W)#");
-    private Pattern tongue = Pattern.compile("#(^|\\W)(\\>\\:P|\\:-P|\\:P|X-P|x-p|\\:-p|\\:p|\\=p|\\:-Þ|\\:Þ|\\:-b|\\:b|\\=p|\\=P|xp|XP|xP|Xp)($|\\W)#");
-    private Pattern surprise = Pattern.compile("#(^|\\W)(\\>\\:o|\\>\\:O|\\:-O|\\:O|°o°|°O°|\\:O|o_O|o\\.O|8-0)($|\\W)#");
-    private Pattern annoyed = Pattern.compile("#(^|\\W)(\\>\\:\\\\|\\>\\:/|\\:-/|\\:-\\.|\\:\\\\|\\=/|\\=\\\\|\\:S|\\:\\/)($|\\W)#");
-    private Pattern cry = Pattern.compile("#(^|\\W)(\\:'\\(|;'\\()($|\\W)#");
[…]

### 2012-12-02 classify/src/main/java/pipe/FixEmoticons.java

@@ -7,32 +7,34 @@ import cc.mallet.pipe.Pipe;
 import cc.mallet.types.Instance;
 
 /**
- * Source : http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/FixEmoticons.java?r=10
- *
+ * Source :
+ * http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist
+ * /pipes/FixEmoticons.java?r=10
+ * 
  */
 public class FixEmoticons extends Pipe {
-    
-    private Pattern regex;
-    
-    public FixEmoticons(Pattern regex) {
-        this.regex = regex;
-    }
 
-    public Instance pipe (Instance carrier) {
-        String text = (String) carrier.getData();
-        Matcher m = regex.matcher(text);
+	private Pattern regex;
 
-        StringBuilder sb = new StringBuilder();
-        int last = 0;
-        while (m.find()) {
-            sb.append(text.substring(last, m.start()));
-            sb.append(m.group(0).toUpperCase());
-            last = m.end();
-        }
-        sb.append(text.substring(last));
+	public FixEmoticons(Pattern regex) {
+		this.regex = regex;
+	}
 
-        carrier.setData(sb.toString());
-        return carrier;
-    }
+	public Instance pipe(Instance carrier) {
+		String text = (String) carrier.getData();
+		Matcher m = regex.matcher(text);
+
+		StringBuilder sb = new StringBuilder();
+		int last = 0;
+		while (m.find()) {
+			sb.append(text.substring(last, m.start()));
+			sb.append(m.group(0).toUpperCase());
+			last = m.end();
+		}
+		sb.append(text.substring(last));
+
+		carrier.setData(sb.toString());
+		return carrier;
+	}
 
 }

### 2012-12-02 classify/src/main/java/pipe/Labelize.java

@@ -7,34 +7,33 @@ import cc.mallet.types.Label;
 import cc.mallet.types.LabelAlphabet;
 
 /**
- * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/Labelize.java?r=10
- *
+ * Source:
+ * http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/
+ * pipes/Labelize.java?r=10
+ * 
  */
 public class Labelize extends Pipe {
-    private final static long serialVersionUID = -461155063551297878L; //-8390758647439705273L; 
+	private final static long serialVersionUID = -461155063551297878L; // -8390758647439705273L;
 
-    public Labelize (Alphabet dataAlphabet, LabelAlphabet labelAlphabet) {
-        super(dataAlphabet, labelAlphabet);
-    }
+	public Labelize(Alphabet dataAlphabet, LabelAlphabet labelAlphabet) {
+		super(dataAlphabet, labelAlphabet);
+	}
 
-    public Labelize ()
-    {
-        this(null, new LabelAlphabet());
-    }
+	public Labelize() {
+		this(null, new LabelAlphabet());
+	}
 
-    public Labelize (LabelAlphabet labelAlphabet)
-    {
-        this(null, labelAlphabet);
-    }
+	public Labelize(LabelAlphabet labelAlphabet) {
+		this(null, labelAlphabet);
+	}
 
-    public Instance pipe (Instance carrier)
-    {
-        if (carrier.getTarget() != null) {
-            if (carrier.getTarget() instanceof Label)
-                return carrier;
-            LabelAlphabet ldict = (LabelAlphabet) getTargetAlphabet();
-            carrier.setTarget(ldict.lookupLabel (carrier.getTarget()));
-        }
-        return carrier;
-    }
+	public Instance pipe(Instance carrier) {
+		if (carrier.getTarget() != null) {
+			if (carrier.getTarget() instanceof Label)
+				return carrier;
+			LabelAlphabet ldict = (LabelAlphabet) getTargetAlphabet();
+			carrier.setTarget(ldict.lookupLabel(carrier.getTarget()));
+		}
+		return carrier;
+	}
 }

### 2012-12-02 classify/src/main/java/pipe/Link2Title.java

@@ -7,71 +7,74 @@ import java.util.regex.Pattern;
 import org.jsoup.Jsoup;
 import org.jsoup.nodes.Document;
 
-import common.Constants;
-
 import cc.mallet.pipe.Pipe;
 import cc.mallet.types.Instance;
 
+import common.Constants;
+
 public class Link2Title extends Pipe {
-	
+
 	/**
 	 * 
 	 */
 	private static final long serialVersionUID = 6856138170442079105L;
 
 	/**
-	 * This assumes that the carrier still has the Tweet Text STRING in the data field
+	 * This assumes that the carrier still has the Tweet Text STRING in the data
+	 * field
 	 */
 	@Override
 	public Instance pipe(Instance carrier) {
 		Pattern httpPattern = Pattern.compile(Constants.HTTP_REGEX);
-		
+
 		String text = (String) carrier.getData();
-				
+
 		if (text == null) {
 			return carrier;
 		}
-		
+
 		Matcher m = httpPattern.matcher(text);
-		
+
 		StringBuilder sb = new StringBuilder();
-		
+
 		/*
 		 * We assume that the tweet uses at least somewhat proper English and
-		 * has spaces between each word. That way we can just look at each word, see if it's a link,
-		 * look it up if it is, otherwise just append the string, and move on.
+		 * has spaces between each word. That way we can just look at each word,
+		 * see if it's a link, look it up if it is, otherwise just append the
+		 * string, and move on.
 		 */
-		
-		for (String s: text.split("\\s+")) {
-			//We found a link so look it up
+
+		for (String s : text.split("\\s+")) {
+			// We found a link so look it up
 			if (s.matches(Constants.HTTP_REGEX) && m.find()) {
 				String url = m.group();
 				Document doc = null;
 				try {
 					doc = Jsoup.connect(url).get();
 					if (doc.title() != null && !doc.title().equals("")) {
-						//Flawless victory!
+						// Flawless victory!
 						sb.append(doc.title());
-						System.out.println("replaced " + url + " with " + doc.title());
-					}
-					else {
-						//try to resolve the url
+						System.out.println("replaced " + url + " with "
+								+ doc.title());
+					} else {
+						// try to resolve the url
 						sb.append(doc.baseUri());
-						System.out.println("replaced " + url + " with " + doc.baseUri());
+						System.out.println("replaced " + url + " with "
+								+ doc.baseUri());
 					}
 				} catch (IOException e) {
-					//Ignore it and put the url back into the string
[…]

### 2012-12-02 classify/src/main/java/pipe/SpellCheck.java

@@ -19,14 +19,14 @@ public class SpellCheck extends Pipe {
 	 * 
 	 */
 	private static final long serialVersionUID = 5452951467629627217L;
-	
+
 	private SpellDictionaryHashMap dictionary;
 	private SpellChecker spellchecker;
-	
+
 	private String dictionaryLoc = "../classify/eng_com.dic";
 	private int threshold = 100;
-	
-	//Look at this block!
+
+	// Look at this block!
 	{
 		try {
 			dictionary = new SpellDictionaryHashMap(new File(dictionaryLoc));
@@ -39,48 +39,49 @@ public class SpellCheck extends Pipe {
 			e.printStackTrace();
 		}
 	}
-	
-	
+
 	/**
-	 * Takes the given instance and does a spell check on the tweet text, replacing misspelled words with the
-	 * best correction. The spell check is taken from the Google SpellChecker api
+	 * Takes the given instance and does a spell check on the tweet text,
+	 * replacing misspelled words with the best correction. The spell check is
+	 * taken from the Google SpellChecker api
 	 */
 	@Override
 	public Instance pipe(Instance carrier) {
 		String text = (String) carrier.getData();
-		
+
 		if (text == null) {
 			return carrier;
 		}
-		
+
 		StringTokenizer st = new StringTokenizer(text);
 		StringBuilder result = new StringBuilder();
 		while (st.hasMoreTokens()) {
 			String token = st.nextToken();
-			//One letter words don't play well  with others
+			// One letter words don't play well with others
 			if (token.length() != 1) {
-				List<Word> words = (List<Word>) spellchecker.getSuggestions(token, threshold);
+				List<Word> words = (List<Word>) spellchecker.getSuggestions(
+						token, threshold);
 				Word best = findBest(words);
-				token = (best != null && best.getCost() < threshold) ? best.getWord() : token;
+				token = (best != null && best.getCost() < threshold) ? best
+						.getWord() : token;
 			}
 			result.append(token).append(" ");
 		}
 		carrier.setData(result.toString());
 		return carrier;
 	}
-	
+
 	private Word findBest(List<Word> words) {
 		if (words.size() == 0) {
 			return null;
 		}
 		Word best = words.get(0);
-		for (Word w: words) {
+		for (Word w : words) {
 			if (w.getCost() < best.getCost()) {
 				best = w;
 			}
 		}
 		return best;
 	}
-
 
 }

### 2012-12-02 classify/src/main/java/pipe/Stemmer.java

@@ -9,41 +9,42 @@ import cc.mallet.pipe.Pipe;
 import cc.mallet.types.Instance;
 import cc.mallet.types.Token;
 import cc.mallet.types.TokenSequence;
+
 /**
  * Source: http://comments.gmane.org/gmane.comp.ai.mallet.devel/1724
- *
+ * 
  */
 public class Stemmer extends Pipe {
 
 	private transient PorterStemmer stemmer;
 
-    private static final long serialVersionUID = -2270190864067551888L;
+	private static final long serialVersionUID = -2270190864067551888L;
 
-    public Stemmer() {
-            stemmer = new PorterStemmer();
-    }
+	public Stemmer() {
+		stemmer = new PorterStemmer();
+	}
 
-    private void readObject(ObjectInputStream aInputStream)
-                    throws ClassNotFoundException, IOException {
-            aInputStream.defaultReadObject();
-            stemmer = new PorterStemmer();
-    }
+	private void readObject(ObjectInputStream aInputStream)
+			throws ClassNotFoundException, IOException {
+		aInputStream.defaultReadObject();
+		stemmer = new PorterStemmer();
+	}
 
-    public Instance pipe(Instance carrier) {
-            TokenSequence tokenSequence = (TokenSequence) carrier.getData();
-            TokenSequence stemmedTokenSequence = new TokenSequence();
+	public Instance pipe(Instance carrier) {
+		TokenSequence tokenSequence = (TokenSequence) carrier.getData();
+		TokenSequence stemmedTokenSequence = new TokenSequence();
 
-            for (int i = 0; i < tokenSequence.size(); i++) {
-                    Token token = tokenSequence.get(i);
-                    stemmer.setCurrent(token.getText());
-                    stemmer.stem();
-                    String s = stemmer.getCurrent();
-                    stemmedTokenSequence.add(new Token(s));
-//                    if (!token.getText().equals(s)) {
-//                    System.out.println(token.getText() + "   :   " + s);
-//                    }
-            }
-            carrier.setData(stemmedTokenSequence);
-            return carrier;
-    }
+		for (int i = 0; i < tokenSequence.size(); i++) {
+			Token token = tokenSequence.get(i);
+			stemmer.setCurrent(token.getText());
+			stemmer.stem();
+			String s = stemmer.getCurrent();
+			stemmedTokenSequence.add(new Token(s));
+			// if (!token.getText().equals(s)) {
[…]

### 2012-12-02 classify/src/main/java/pipe/TokenSequenceBiGrammer.java

@@ -5,19 +5,21 @@ import cc.mallet.types.Instance;
 import cc.mallet.types.TokenSequence;
 
 /**
- * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/TokenSequenceBiGrammer.java?r=10
- *
+ * Source:
+ * http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/
+ * pipes/TokenSequenceBiGrammer.java?r=10
+ * 
  */
 public class TokenSequenceBiGrammer extends Pipe {
 
-    public Instance pipe (Instance carrier) {
-        TokenSequence ts = (TokenSequence) carrier.getData();
-        int size = ts.size();
-        for (int i = 1; i < size; i++) {
-            ts.add (ts.get(i-1).getText() + "_" + ts.get(i).getText());
-        }
-        carrier.setData(ts);
-        return carrier;
-    }
+	public Instance pipe(Instance carrier) {
+		TokenSequence ts = (TokenSequence) carrier.getData();
+		int size = ts.size();
+		for (int i = 1; i < size; i++) {
+			ts.add(ts.get(i - 1).getText() + "_" + ts.get(i).getText());
+		}
+		carrier.setData(ts);
+		return carrier;
+	}
 
 }

### 2012-12-02 classify/src/main/java/pipe/Tokenizer.java

@@ -64,7 +64,7 @@ public class Tokenizer extends Pipe {
 	private boolean removeRT;
 	private boolean normalizeLengths;
 	private boolean removePunct;// removes any non-word characters from edges of
-															// space-delimited tokens
+								// space-delimited tokens
 	private boolean print;
 	private Case casing;
 
@@ -191,12 +191,14 @@ public class Tokenizer extends Pipe {
 			String replacement) {
 		if (is1) {
 			for (String s : remaining1) {
-				remaining2.addAll(match(regex, ts, s, toLowercase, replacement));
+				remaining2
+						.addAll(match(regex, ts, s, toLowercase, replacement));
 			}
 			remaining1.clear();
 		} else {
 			for (String s : remaining2) {
-				remaining1.addAll(match(regex, ts, s, toLowercase, replacement));
+				remaining1
+						.addAll(match(regex, ts, s, toLowercase, replacement));
 
 			}
 			remaining2.clear();

### 2012-12-02 classify/src/main/java/pipe/TokenizerToTwoToo.java

@@ -105,9 +105,8 @@ public class TokenizerToTwoToo extends Pipe {
 			String split[] = t.split("\\s+");
 			for (int j = 0; j < split.length; j++) {
 				if (split[j].startsWith("http://")) {
-					matches.put(offset+j, split[j]);
-				}
-				else if (split[j].equals(split[j].toUpperCase())) {
+					matches.put(offset + j, split[j]);
+				} else if (split[j].equals(split[j].toUpperCase())) {
 					matches.put(offset + j,
 							split[j].replaceAll("([A-Z])\\1{3,}", "$1$1$1")
 									.replaceAll("\\.{2,}", " ... "));

### 2012-12-02 classify/src/main/java/pipe/TwitterPipe.java

@@ -2,9 +2,6 @@ package pipe;
 
 import java.util.regex.Pattern;
 
-
-import cc.mallet.pipe.CharSequence2TokenSequence;
-import cc.mallet.pipe.CharSequenceLowercase;
 import cc.mallet.pipe.CharSequenceReplace;
 import cc.mallet.pipe.FeatureSequence2AugmentableFeatureVector;
 import cc.mallet.pipe.Noop;
@@ -15,55 +12,69 @@ import cc.mallet.pipe.TokenSequenceRemoveStopwords;
 import cc.mallet.types.Instance;
 
 /**
- * Source: http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/pipes/TwitterPipe.java?r=10
- *
+ * Source:
+ * http://code.google.com/p/dualist/source/browse/trunk/core/src/dualist/
+ * pipes/TwitterPipe.java?r=10
+ * 
  */
 public class TwitterPipe extends Pipe {
 
-    private boolean anonmymize = true;
-    private boolean emoticons = true;
-    
-    private String corePattern = "([\\@\\#]?[\\p{L}\\p{Mn}][\\p{L}\\p{Mn}'_]+)|([!?]+)";
-    private String emoticonPattern = "([:;=x][-o^]?[)(/\\\\dp])|([/\\\\)(dp][-o^]?[:;=x])";
+	private boolean anonmymize = true;
+	private boolean emoticons = true;
 
-    private Pipe myPipe = new SerialPipes(new Pipe[] {
-            new CopyData2Source(),
-//            new CharSequenceLowercase(),
-            anonmymize 
-            ? new CharSequenceReplace(Pattern.compile("http\\:\\/\\/.*\\b", Pattern.CASE_INSENSITIVE), "HTTPLINK") 
-            : new Noop(),
-            anonmymize 
-            ? new CharSequenceReplace(Pattern.compile("\\@[\\p{L}\\p{Mn}]+", Pattern.CASE_INSENSITIVE), "@USERLINK") 
-            : new Noop(),
-            new CharSequenceReplace(Pattern.compile("\\'"), ""),
-            new CharSequenceReplace(Pattern.compile("\\!\\!+"), "!!"),
-            new CharSequenceReplace(Pattern.compile("\\?\\?+"), "??"),
-//            new CharSequenceReplace(Pattern.compile("\\bno\\s+"), "no_"),
-//            new CharSequenceReplace(Pattern.compile("\\bnot\\s+"), "not_"),
[…]

### 2012-12-02 classify/src/main/java/ui/LabelingFrame.java

@@ -1,6 +1,7 @@
 package ui;
 
 import java.awt.BorderLayout;
+import java.awt.Color;
 import java.awt.EventQueue;
 import java.awt.Font;
 import java.awt.GridBagConstraints;
@@ -15,7 +16,6 @@ import java.io.File;
 import java.io.FileReader;
 import java.io.FileWriter;
 import java.io.IOException;
-import java.util.ArrayList;
 import java.util.HashSet;
 import java.util.LinkedList;
 import java.util.List;
@@ -35,9 +35,6 @@ import javax.swing.JTextField;
 import javax.swing.SwingConstants;
 import javax.swing.border.EmptyBorder;
 import javax.swing.filechooser.FileFilter;
-import java.awt.Color;
-import java.awt.event.FocusAdapter;
-import java.awt.event.FocusEvent;
 
 public class LabelingFrame extends JFrame implements ActionListener {
 
@@ -46,10 +43,10 @@ public class LabelingFrame extends JFrame implements ActionListener {
 	 */
 	private static final long serialVersionUID = -2225603632488216748L;
 	private JPanel contentPane;
-	
+
 	List<Tweet> tweets;
-	
-	//Fields holding the two types of labels for labeling
+
+	// Fields holding the two types of labels for labeling
 
 	private JTextField firstLabelField;
 	private JTextField secondLabelField;
@@ -70,9 +67,10 @@ public class LabelingFrame extends JFrame implements ActionListener {
 
 	// Dummy tweet for beginning and ending
 	private Tweet defaultTweet;
-	
-	JButton openFile, prev, next, delete, finish, firstLabel, secondLabel, check;
-	
+
+	JButton openFile, prev, next, delete, finish, firstLabel, secondLabel,
+			check;
+
 	private JFileChooser fc;
 
 	private int curTweet, totalTweets;
@@ -140,10 +138,10 @@ public class LabelingFrame extends JFrame implements ActionListener {
 		finish.setForeground(new Color(148, 0, 211));
 		finish.addActionListener(this);
 		buttonPanel.add(finish);
-		
-//		check = new JButton("Check Finished");
-//		check.addActionListener(this);
-//		buttonPanel.add(check);
+
+		// check = new JButton("Check Finished");
+		// check.addActionListener(this);
+		// buttonPanel.add(check);
 
[…]

### 2012-12-02 classify/src/main/java/classification/ModelTester.java
randomized testing data

@@ -40,8 +40,8 @@ public class ModelTester {
 
 	public static void main(String[] args) throws IOException {
 
-		int d = 5;
-		int max = 100;
+		int d = 100;
+		int max = 1800;
 
 		ArrayList<String> info = new ArrayList<String>();
 
@@ -72,7 +72,7 @@ public class ModelTester {
 			ArrayList<Trial> trials = new ArrayList<Trial>();
 
 			InstanceList instances = new InstanceList(pipe);
-			File file = new File("../corpus/appleBinaryFiltered.txt");
+			File file = new File("../corpus/appleBinaryFilteredRandomized.txt");
 			CsvIterator reader = new CsvIterator(new FileReader(file),
 					Constants.CSV_ITERATOR_REGEX, 3, 1, 2);
 			instances.addThruPipe(reader);

### 2012-12-02 classify/src/main/java/classification/ModelTester.java
Data was already randomized, undoing

@@ -40,8 +40,8 @@ public class ModelTester {
 
 	public static void main(String[] args) throws IOException {
 
-		int d = 100;
-		int max = 1800;
+		int d = 5;
+		int max = 100;
 
 		ArrayList<String> info = new ArrayList<String>();
 
@@ -72,7 +72,7 @@ public class ModelTester {
 			ArrayList<Trial> trials = new ArrayList<Trial>();
 
 			InstanceList instances = new InstanceList(pipe);
-			File file = new File("../corpus/appleBinaryFilteredRandomized.txt");
+			File file = new File("../corpus/appleBinaryFiltered.txt");
 			CsvIterator reader = new CsvIterator(new FileReader(file),
 					Constants.CSV_ITERATOR_REGEX, 3, 1, 2);
 			instances.addThruPipe(reader);

### 2012-12-02 classify/src/main/java/common/PipeFactory.java
added ngramming

@@ -26,8 +26,7 @@ public class PipeFactory {
 		return new SetCombiner<SerialPipes, Pipe>() {
 
 			@Override
-			public SetItem<SerialPipes> combine(List<Pipe> pipes,
-					List<String> labels) {
+			public SetItem<SerialPipes> combine(List<Pipe> pipes, List<String> labels) {
 
 				return new SetItem<SerialPipes>(new SerialPipes(pipes),
 						labels.toString());
@@ -44,18 +43,18 @@ public class PipeFactory {
 			@Override
 			protected void build() {
 				this.add(
-						new CharSequence2TokenSequence(Pattern
-								.compile("[\\p{L}\\p{N}_]+")),
+						new CharSequence2TokenSequence(Pattern.compile("[\\p{L}\\p{N}_]+")),
 						"numdig tokenizer");
-				this.add(
-						new CharSequence2TokenSequence(Pattern
-								.compile("[^\\s]+")), "whitespace tokenizer");
-				this.add(new Tokenizer(false, false, false, false, false,
-						false, false, false, false, Case.lower),
-						"simplistic twitter tokenizer");
-				this.add(new Tokenizer(true, true, true, true, true, false,
-						true, true, false, Case.lower),
-						"twitter tokenizer with no RT,appleCase, and noPunct removed");
+				this.add(new CharSequence2TokenSequence(Pattern.compile("[^\\s]+")),
+						"whitespace tokenizer");
+				this.add(new Tokenizer(false, false, false, false, false, false, false,
+						false, false, false, Case.lower), "simplistic twitter tokenizer");
+				this.add(new Tokenizer(true, true, true, true, true, false, true, true,
+						false, false, Case.lower),
+						"twitter tokenizer with no RT--appleCase--no ngramming--and noPunct removed");
+				this.add(new Tokenizer(true, true, true, true, true, true, true, true,
+						false, false, Case.apple),
+						"twitter tokenizer with everything but ngramming");
 				this.add(new Tokenizer(false), "default twitter tokenizer");
 			}
 
@@ -98,7 +97,7 @@ public class PipeFactory {
 		Pattern tokenPattern = Pattern.compile("[^\\s]+");
 		// pipe.add(new CharSequence2TokenSequence(tokenPattern));
 		pipe.add(new Tokenizer(false, false, false, false, false, false, false,
-				false, false, Case.nochange));
+				false, false, false, Case.nochange));
[…]

### 2012-12-02 classify/src/main/java/pipe/Tokenizer.java

@@ -31,18 +31,19 @@ public class Tokenizer extends Pipe {
 	// 6. remove commas, colons, semicolons, hyphens?
 	// possible remove RT and -
 	public Tokenizer() {
-		this(true, true, true, true, true, true, true, true, true, Case.apple);
+		this(true, true, true, true, true, true, true, true, true, true, Case.apple);
 	}
 
 	public Tokenizer(boolean print) {
-		this(true, true, true, true, true, true, true, true, print, Case.apple);
+		this(true, true, true, true, true, true, true, true, true, print,
+				Case.apple);
 
 	}
 
 	public Tokenizer(boolean doEmoticons, boolean doUsernames,
 			boolean doHashtags, boolean doLinks, boolean doSpecialCases,
 			boolean removeRT, boolean normalizeLengths, boolean removePunct,
-			boolean print, Case casing) {
+			boolean ngram, boolean print, Case casing) {
 		this.doEmoticons = doEmoticons;
 		this.doUsernames = doUsernames;
 		this.doHashtags = doHashtags;
@@ -51,6 +52,7 @@ public class Tokenizer extends Pipe {
 		this.removeRT = removeRT;
 		this.normalizeLengths = normalizeLengths;
 		this.removePunct = removePunct;
+		this.ngram = ngram;
 		this.casing = casing;
 		this.print = print;
 
@@ -64,7 +66,8 @@ public class Tokenizer extends Pipe {
 	private boolean removeRT;
 	private boolean normalizeLengths;
 	private boolean removePunct;// removes any non-word characters from edges of
-								// space-delimited tokens
+	// space-delimited tokens
+	private boolean ngram;
 	private boolean print;
 	private Case casing;
 
@@ -140,6 +143,7 @@ public class Tokenizer extends Pipe {
 		if (doHashtags) {
 			use1 = next(strings1, strings2, use1, hashtags, ts, true, null);
 		}
+		String prev = "";
 
 		for (String s : use1 ? strings1 : strings2) {
 			String spl[] = s.split("\\s+");
@@ -170,6 +174,13 @@ public class Tokenizer extends Pipe {
 
 				if (ss.length() > 0) {
 					ts.add(ss);
+					if (ngram) {
+						if (prev != "") {
+							ts.add(prev + "_" + ss);
+						}
+						prev = ss;
+					}
+
 					if (print) {
 						System.out.println(ss);
 					}
[…]

### 2012-12-02 paper/paper.tex
updated paper

@@
 \section{Introduction}
-Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on sentiment \cite{Ruiz:2012:CFT:2124295.2124358}, ... [ADD MORE]
+Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on sentiment% \cite{Ruiz:2012:CFT:2124295.2124358}, ... [ADD MORE]
 In many cases, the problem of determining which tweets are relevant for a particular application is prerequisite to meaningful results.
@@
 DUALIST is a system that extends Mallet by user-interactive feedback during training[Settles]. Included in their implementation was a TwitterPipe that performed some simple feature extraction. 
-Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing \cite{potts2011}.
+Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing %\cite{potts2011}.
 A good deal of research has been done into sentiment classification of tweets, which requires very similar text processing and tokenization \cite{Pak10}.
@@
 
-We do all machine learning with the Mallet\cite{McCallumMALLET} library developed by the University of Massachusetts.
+We do all machine learning with the Mallet%\cite{McCallumMALLET} library developed by the University of Massachusetts.
 Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format.
@@
 ~\\
-\textit{Stopword removal}: In order to improve accuracy of classification we decided to run each tweet through a pipe that would remove stopwords.
-Stopwords are generally known as adverbs, conjunctions, pronouns, and prepositions commonly found in English sentences, By removing these words, we hoped that the classifiers would be able to focus more on the relevant text and less on meaningless parts of the tweets.
-Since this is a common task for natural language processing we were able to make use of one of Mallet's stopwords pipes, using a default list of stopwords.\\
-\textit{N-grams}:\\
-\textit{Fix emoticons}:\\
-\textit{HTML corrections}:\\ 
-\textit{URL replacement}:\\
-Spell checking: Since Twitter is an informal form of communication, we found that a fair number of tweets were being classified that had misspelled words.
-We decided that performing a spell check on the tweet might help the classifier work, since then it would only have to process proper English.
-In order to perform the spell check, we made use of an api that would return suggestions for misspelled words.
-Along with the suggested correct spellings of words, we were also given a "confidence" level for each suggestion.
-By using this value we were able to choose the best suggestion, and also filter out any suggestions that were too far from the original word.\\
-
+\textit{Stopword removal}: We wrote a Pipe to remove any tokens that appeared in a list of the 50 most common words in the English language.\\
+~\\
+\textit{N-grams}: Using n-grams is a common method of increasing the number of features present in short text [FIND CITATION].
+Often, this is enough to increase accuracy significantly.
+During our testing, this was not the case.
+Rather, including bigrams and trigrams actually reduced accuracy slightly.\\
+~\\
+\textit{HTML corrections}: When accessing tweets through Twitter's public API, the native JSON format includes HTML-encoded entities that can add confusing features to the tweets if not un-escaped.
+For instance, angle brackets are replaced with \&lt; and \&gt; (less-than and greater-than), causing emoticons, for instance, to no longer be parseable.
+The emoticon ">.<", for instance, would be "\&gt;.\&lt;".
+This Pipe un-escapes all such entities, making them easier to parse.\\
+~\\
+\textit{URL replacement}: 
+~\\
+\textit{Spell checking}: Twitter's user-generated content contains a large volume of misspelled words.
+Using a spell-checking library, we wrote a Pipe to replace unrecognized words (misspelled words) with their corrections if the confidence for correction was above a certain threshold.
+\\
+~\\
 \subsubsection{Disambiguation}
 ~\\
-\textit{Lowercasing}:\\
-Stemming: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
-Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not a real word.
-We believed that by reducing each word in the tweet to a its stem, we would be able to improve the classifying algorithm's ability to classify.
-In order to add stemming we made use of an api that used a Porter stemming algorithm to find the stem of each word.\\
+\textit{Stemming}: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
+Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not the true linguistic stem.
+We used the standard Porter stemmer to implement this[CITATION].\\
 
@@
 
-Things that could be done....
+We could test the robustness of this system by applying this process to other companies for a similar-length time slice of training data.
+We could also test this model against tweets from a different time span to determine whether the data is subject to temporal overfitting, and to what degree.
 
 [These guys] demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification.
+
+Inclusion of background knowledge.
+
+Use of Wikipedia for disambiguation.
 
@@
 We have implemented several Pipes that can be reused or easily modified to suit a similar Twitter processing purpose.
-These include FixEmoticons, Link2Title, Stemmer, SpellCheck, and Tokenize, which serves as a more extensible tokenizer than Mallet's default.
+These include Link2Title, Stemmer, SpellCheck, and Tokenize, the latter of which serves as a more extensible tokenizer than Mallet's default.
 All code is available through our project website.
@@
 \section{References}
-\begin{thebibliography}{99}
-@article{potts2011,
-    author    = "Christopher Potts",
-    title     = "Sentiment Symposium Tutorial: Tokenizing",
-    journal   = "",
-    year      = "2011"
-}
-@inproceedings{Pak10,
-  added-at = {2010-06-01T10:23:44.000+0200},
-  address = {Valletta, Malta},
-  author = {Pak, Alexander and Paroubek, Patrick},
-  biburl = {http://www.bibsonomy.org/bibtex/25656c3bb1adf00c58a85e3204096961c/frederik},
-  booktitle = {Proceedings of the Seventh conference on International Language Resources and Evaluation (LREC'10)},
-  date = {19-21},
-  interhash = {ac930b0459a3c8a2fc2d74c52a475026},
-  intrahash = {5656c3bb1adf00c58a85e3204096961c},
-  isbn = {2-9517408-6-7},
-  keywords = {imported},
-  language = {english},
-  month = may,
-  publisher = {European Language Resources Association (ELRA)},
-  timestamp = {2010-06-01T10:23:44.000+0200},
-  title = {Twitter as a Corpus for Sentiment Analysis and Opinion Mining},
-  url = {http://www.lrec-conf.org/proceedings/lrec2010/pdf/385\_Paper.pdf},
-  year = 2010
-}
-@inproceedings{Ruiz:2012:CFT:2124295.2124358,
- author = {Ruiz, Eduardo J. and Hristidis, Vagelis and Castillo, Carlos and Gionis, Aristides and Jaimes, Alejandro},
- title = {Correlating financial time series with micro-blogging activity},
- booktitle = {Proceedings of the fifth ACM international conference on Web search and data mining},
- series = {WSDM '12},
- year = {2012},
- isbn = {978-1-4503-0747-5},
- location = {Seattle, Washington, USA},
- pages = {513--522},
- numpages = {10},
- url = {http://doi.acm.org/10.1145/2124295.2124358},
- doi = {10.1145/2124295.2124358},
- acmid = {2124358},
- publisher = {ACM},
- address = {New York, NY, USA},
- keywords = {financial time series, micro-blogging, social networks},
-} 
-@unpublished{McCallumMALLET,
-    author = "Andrew Kachites McCallum",
-    title = "MALLET: A Machine Learning for Language Toolkit",
-    note = "http://mallet.cs.umass.edu",
-    year = 2002,
-}
+\bibliographystyle{plain}
+\bibliography{references}
 
-\end{thebibliography}
-
-[1] J. Bollen, H. Mao, and X.-J. Zeng. Twitter mood predicts the
-stock market. Journal of Computational Science,
-abs/1010.3003, 2010\\
+%[1] J. Bollen, H. Mao, and X.-J. Zeng. Twitter mood predicts the stock market. Journal of Computational Science, abs/1010.3003, 2010\\
 

### 2012-12-02 classify/src/main/java/classification/ModelTester.java
updaet model tester

@@ -34,14 +34,14 @@ public class ModelTester {
 
 	private static final int random_seed = 0xDEADBEEF;
 
-	private static final int folds = 10;
+	private static final int folds = 1;
 
-	private static final int test_size = 200;
+	private static final int test_size = 500;
 
 	public static void main(String[] args) throws IOException {
 
-		int d = 5;
-		int max = 100;
+		int d = 100;
+		int max = 1500;
 
 		ArrayList<String> info = new ArrayList<String>();
 

### 2012-12-03 paper/paper.tex
bib for paper and some formatting

@@
 
-This set of keywords clearly allows a large number of false positives:\\
-\begin{quote}
-nice fish and chip.. good pie apple :-) http://t.co/KVDN5r5l \\
-20 chicken nuggets, chips, big mac, and a vanilla milkshake LIFE IS GOOD \\
-1 more day whoop plus safari ride yay \\
-Ashley staples an apple.  "AHHHH!!!!  Apple juice in my eye!" \\
+This set of keywords clearly allows a large number of false positives:
+
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	nice fish and chip.. good pie apple :-) \\ http://t.co/KVDN5r5l \\ \hline
+	20 chicken nuggets, chips, big mac, and a \\ vanilla milkshake LIFE IS GOOD \\ \hline
+	1 more day whoop plus safari ride yay \\ \hline
+	Ashley staples an apple.  "AHHHH!!!! \\ Apple juice in my eye!" \\ \hline
 	I ain't seen uncle Mac in a while \\
-\end{quote}
+	\hline
+\end{tabular}
+\caption{Examples of false positive tweets}
+\label{tab:myfirsttable}
+\end{table}
 
@@
 A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].
+
+A computer-posted spam tweet:
 \begin{quote}
-A computer-posted spam tweet: I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
-A retweet, signified by "RT": RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
+I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
+\end{quote}
+
+A retweet, signified by "RT":
+\begin{quote}
+RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
 \end{quote}
@@
 
-\subsubsection{Feature-space Enrichment}
-~\\
+\subsubsection{Feature-space Enrichment} ~\\
 \textit{Stopword removal}: We wrote a Pipe to remove any tokens that appeared in a list of the 50 most common words in the English language.\\
 ~\\
-\textit{N-grams}: Using n-grams is a common method of increasing the number of features present in short text [FIND CITATION].
+\textit{N-grams}: Using n-grams is a common method of increasing the number of features present in short text [FIND CITATION]\cite{article_label,book_label}.
 Often, this is enough to increase accuracy significantly.
@@
 For instance, angle brackets are replaced with \&lt; and \&gt; (less-than and greater-than), causing emoticons, for instance, to no longer be parseable.
-The emoticon ">.<", for instance, would be "\&gt;.\&lt;".
+The emoticon \">.<", for instance, would be "\&gt;.\&lt;".
 This Pipe un-escapes all such entities, making them easier to parse.\\
@@
 
-\section{References}
 \bibliographystyle{plain}
-\bibliography{references}
+
+\begin{thebibliography}{2}
+\providecommand{\natexlab}[1]{#1}
+\providecommand{\url}[1]{\texttt{#1}}
+\expandafter\ifx\csname urlstyle\endcsname\relax
+\providecommand{\doi}[1]{doi: #1}\else
+\providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi
+
+\bibitem[{Surname}(2007{\natexlab{a}})]{article_label}
+Firstname~I. {Surname}.
+\newblock Title of article.
+\newblock \emph{Journal of Publication}, 1:\penalty0 1--2, May
+2007{\natexlab{a}}.
+
+\bibitem[{Surname2}(2007{\natexlab{b}})]{book_label}
+Firstname~I. {Surname}.
+\newblock \emph{Title of Book}.
+\newblock Publishing House, Address of Publishing House, 1 edition,
+2007{\natexlab{b}}.
+
+\end{thebibliography}
 

### 2012-12-03 paper/paper.tex
Fixed references

@@
 Twitter is a popular source for data mining due to its massive scale and inclusivity of current trends.
-As businesses seek to discover public opinion about their business or products, Twitter is one source for mining this information.
-Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
-Tweet selection by keyword filtering often suffers from an high accuracy and low recall, or low accuracy and high recall.
-Using machine learning for text classification can improve this.
-We aim to survey a variety of text processing steps, focusing on the effects of tokenization, to increase accuracy of classification using a Naive Bayes classifier.
-We use a broad set of keywords with the goal of collecting a superset of the Tweets about a particular company (Apple, in this case) and train a binary classifier to filter out false positives.
+It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products.
+Using machine learning techniques, we analyze the accuracy of classifying whether tweets are part of the public opinion about a particular company or mearly contain keywords related to the company.
+%Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
+%Classification purely by keyword filtering often suffers from a
+%high accuracy and low recall, or low accuracy and high recall. % Q: Daniel - What does recall mean in this context? Also, list low accuracy first I think.
+We aim to survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations.
+Our dataset consists of approximately 2,000 tweets of which 64\% are related to public opinion about the company Apple, Inc. The other 36\% are not, but still contain keywords related to the company.
+Peliminary results have shown significant increases in accuracy % TODO insert actual numbers
+by using domain-specific tokenizers, while suprisingly showing decreases in classification accurracy for other standard preproccessing methods such as n-grams.
 \end{quote}
@@
 \section{Introduction}
-Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on sentiment% \cite{Ruiz:2012:CFT:2124295.2124358}, ... [ADD MORE]
+Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on sentiment \citeauthor{Ruiz}, ... [ADD MORE]
 In many cases, the problem of determining which tweets are relevant for a particular application is prerequisite to meaningful results.
@@
 ~\\
-\textit{N-grams}: Using n-grams is a common method of increasing the number of features present in short text [FIND CITATION]\cite{article_label,book_label}.
+\textit{N-grams}: Using n-grams is a common method of increasing the number of features present in short text [FIND CITATION].
 Often, this is enough to increase accuracy significantly.
@@
 \bibliographystyle{plain}
-
-\begin{thebibliography}{2}
-\providecommand{\natexlab}[1]{#1}
-\providecommand{\url}[1]{\texttt{#1}}
-\expandafter\ifx\csname urlstyle\endcsname\relax
-\providecommand{\doi}[1]{doi: #1}\else
-\providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi
-
-\bibitem[{Surname}(2007{\natexlab{a}})]{article_label}
-Firstname~I. {Surname}.
-\newblock Title of article.
-\newblock \emph{Journal of Publication}, 1:\penalty0 1--2, May
-2007{\natexlab{a}}.
-
-\bibitem[{Surname2}(2007{\natexlab{b}})]{book_label}
-Firstname~I. {Surname}.
-\newblock \emph{Title of Book}.
-\newblock Publishing House, Address of Publishing House, 1 edition,
-2007{\natexlab{b}}.
-
-\end{thebibliography}
+\bibliography{paper}
 

### 2012-12-04 paper/paper.tex
updated chart

@@
 \usepackage{hyperref}
+\usepackage[round]{natbib}
+\usepackage{graphicx}
 
@@
 DUALIST is a system that extends Mallet by user-interactive feedback during training[Settles]. Included in their implementation was a TwitterPipe that performed some simple feature extraction. 
-Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing %\cite{potts2011}.
+Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing \cite{potts2011}.
 A good deal of research has been done into sentiment classification of tweets, which requires very similar text processing and tokenization \cite{Pak10}.
@@
 \subsection{Corpus creation}
-By accessing the Twitter "Firehose" stream through their public API, we harvested 115,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
+By accessing the Twitter \"Firehose\" stream through their public API, we harvested 115,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
 This provides us a smaller set of features in the overall corpus.
@@
 A computer-posted spam tweet:
-\begin{quote}
-I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
-\end{quote}
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	I've collected 10,650 gold coins! \\ http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
+	\hline
+\end{tabular}
+\end{table}
 
 A retweet, signified by "RT":
-\begin{quote}
-RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
-\end{quote}
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	RT @PHILerNotebook: Trying to fix my Mac. \\ This gray loading bar takes 10 minutes to start up. \\ Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
+	\hline
+\end{tabular}
+\end{table}
 
 We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. \\
-Data sets and scripts used for processing text data are available on the project website.\\
+Data sets and scripts used for processing text data are available on the project website. (http://tweets.curtisullerich.com/)\\
 
@@
 
-We do all machine learning with the Mallet%\cite{McCallumMALLET} library developed by the University of Massachusetts.
+We do all machine learning with the Mallet library developed by the University of Massachusetts \cite{McCallumMALLET}.
 Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format.
@@
 
+\begin{figure*}[t!]
+\centering
+\includegraphics[height=7cm]{chart}
+\caption{Accuracy Chart}
+\label{fig:chart}
+\end{figure*}
+
 \subsubsection{Tokenization}
@@
 
-\begin{quote}
-Cool ranch , 4 berry sundae , apple juice \#yessuh \#latenight \#snack http://t.co/ttc3vujp 
-I just poured apple juice on my cereal.. Gah. \#SoTired 
-I hate Siri.. -\_\_\_- 
-\end{quote}
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	Cool ranch , 4 berry sundae , apple juice \#yessuh \\ \#latenight \#snack http://t.co/ttc3vujp \\ \hline
+	I just poured apple juice on my cereal.. Gah. \#SoTired \\ \hline
+	I hate Siri.. -\_\_\_- \\
+	\hline
+\end{tabular}
+\caption{Examples of difficult tokenizations}
+\label{tab:tokenization_examples}
+\end{table}
 
@@
 \begin{quote}
-Now on my iphone ?? http://t.co/Rqr1RL2R 
+\textit{Now on my iphone ?? http://t.co/Rqr1RL2R}
 \end{quote}
@@
 \begin{quote}
-I listen to my iPod every day and it's just broke omg:(!!
+\textit{I listen to my iPod every day and it's just broke omg:(!!}
 \end{quote}
@@
 After tokenizing these special features in order (URLs, emoticons, usernames, and hashtags) we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings.
-As done by Potts (2011) we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
+As done by \citet{potts2011} we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
 In the following tweet, "loooool" is normalized to "loool".
@@
 
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Maecenas vulputate ultricies lorem, quis consectetur erat tristique id.
+Nulla eget nunc in urna vestibulum ornare ac sed purus.
+Curabitur consequat gravida turpis in rutrum.
+Nulla vehicula condimentum luctus.
+Nam venenatis facilisis orci sed ullamcorper.
+In felis leo, rutrum nec vestibulum vitae, lacinia at ipsum.
+Praesent orci nibh, pellentesque vitae placerat eget, tempus eget libero.
+Duis eleifend, orci nec pretium condimentum, quam erat euismod quam, sed accumsan erat lacus in felis.
+Aliquam vitae leo sem.
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+Etiam consequat ante eu turpis molestie vel gravida felis varius.
+Vestibulum tincidunt, velit quis convallis imperdiet, est nisi aliquet mauris, eget tempus metus eros eget erat.
+Aenean sit amet dui vel urna pretium dictum nec sed elit.
+Vivamus feugiat dictum neque imperdiet ultrices.
+Nullam commodo rhoncus elit id adipiscing.
+Nam nec turpis ut nisi pulvinar blandit at tincidunt dolor.
+
+Integer dictum tristique felis vitae lobortis.
+Quisque hendrerit, mi vel vestibulum sagittis, nulla leo rhoncus nisl, ac lobortis nisi lorem quis nisl.
+Nullam vehicula magna convallis odio semper vestibulum.
+Ut lobortis, purus eu sodales congue, sapien dolor consectetur turpis, vitae luctus nibh elit et eros.
+Nam tempor felis eget dui laoreet vehicula.
+Praesent imperdiet hendrerit elit sed tempus.
+Phasellus feugiat pretium metus id scelerisque.
+Morbi ligula lectus, blandit in vestibulum id, fermentum sit amet augue.
+Donec pharetra molestie euismod.
+Nulla porttitor feugiat purus, in egestas lorem venenatis sed.
+Phasellus quis interdum diam.
+Ut congue, magna at malesuada luctus, augue urna dignissim nulla, congue lacinia metus felis eget odio.
+Vestibulum et nisl sodales quam commodo laoreet.
+Ut a tortor tortor.
+
 \section{Results}
+
 ...baseline using priors
@@
   most useful features for classification
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Maecenas vulputate ultricies lorem, quis consectetur erat tristique id.
+Nulla eget nunc in urna vestibulum ornare ac sed purus.
+Curabitur consequat gravida turpis in rutrum.
+Nulla vehicula condimentum luctus.
+Nam venenatis facilisis orci sed ullamcorper.
+In felis leo, rutrum nec vestibulum vitae, lacinia at ipsum.
+Praesent orci nibh, pellentesque vitae placerat eget, tempus eget libero.
+Duis eleifend, orci nec pretium condimentum, quam erat euismod quam, sed accumsan erat lacus in felis.
+Aliquam vitae leo sem.
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+Etiam consequat ante eu turpis molestie vel gravida felis varius.
+Vestibulum tincidunt, velit quis convallis imperdiet, est nisi aliquet mauris, eget tempus metus eros eget erat.
+Aenean sit amet dui vel urna pretium dictum nec sed elit.
+Vivamus feugiat dictum neque imperdiet ultrices.
+Nullam commodo rhoncus elit id adipiscing.
+Nam nec turpis ut nisi pulvinar blandit at tincidunt dolor.
+
+Integer dictum tristique felis vitae lobortis.
+Quisque hendrerit, mi vel vestibulum sagittis, nulla leo rhoncus nisl, ac lobortis nisi lorem quis nisl.
+Nullam vehicula magna convallis odio semper vestibulum.
+Ut lobortis, purus eu sodales congue, sapien dolor consectetur turpis, vitae luctus nibh elit et eros.
+Nam tempor felis eget dui laoreet vehicula.
+Praesent imperdiet hendrerit elit sed tempus.
+Phasellus feugiat pretium metus id scelerisque.
+Morbi ligula lectus, blandit in vestibulum id, fermentum sit amet augue.
+Donec pharetra molestie euismod.
+Nulla porttitor feugiat purus, in egestas lorem venenatis sed.
+Phasellus quis interdum diam.
+Ut congue, magna at malesuada luctus, augue urna dignissim nulla, congue lacinia metus felis eget odio.
+Vestibulum et nisl sodales quam commodo laoreet.
+Ut a tortor tortor.
+
+Phasellus et mi eu est fermentum cursus id sodales nisi.
+Maecenas sodales ornare mauris, nec cursus mi commodo non.
+In pulvinar odio id est pharetra cursus.
+Fusce blandit scelerisque bibendum.
+Aliquam erat volutpat.
+Aliquam tellus lorem, pharetra a vehicula nec, tincidunt sit amet felis.
+Nullam nec sapien quis leo facilisis commodo at vel enim.
+Suspendisse ultricies massa at nisl iaculis scelerisque.
+Phasellus sed sodales augue.
+Pellentesque a nisl enim.
+
+Mauris at eros velit, non venenatis augue.
+Fusce vel ornare purus.
+Praesent condimentum lectus sit amet sem ullamcorper eget euismod tellus dapibus.
+Aenean fringilla urna vel nisl accumsan imperdiet.
+Duis cursus mattis molestie.
+Phasellus est lorem, condimentum quis congue eget, condimentum scelerisque arcu.
+Phasellus odio lacus, imperdiet at convallis et, vehicula a nisi.
+Mauris consequat urna vitae ipsum vulputate ullamcorper.
+Fusce ullamcorper mauris dolor.
+Quisque gravida hendrerit tristique.
+Fusce magna urna, vestibulum eget condimentum eu, semper sit amet felis.
+Ut placerat hendrerit neque id vestibulum.
+Phasellus convallis, nulla at fermentum bibendum, massa risus tempus eros, et malesuada diam enim sed purus.
+Praesent tincidunt dapibus lobortis.
+Curabitur sodales dignissim est quis tempus.
+
+Aenean vel enim eu mauris scelerisque pulvinar in quis odio.
+Suspendisse eu sapien vitae eros ultrices congue volutpat quis elit.
+Aliquam nisl nibh, hendrerit ut feugiat eget, gravida eget urna.
+In nisl felis, elementum ut sollicitudin non, fringilla in neque.
+Aliquam quis luctus lacus.
+Cras et mauris sem, vel imperdiet sapien.
+Suspendisse in ligula id turpis adipiscing sodales vitae ut lectus.
+Vestibulum neque nulla, commodo vitae venenatis id, accumsan vitae odio.
+Quisque velit purus, tempor non porta laoreet, elementum vel sem.
+Nullam mollis euismod dolor, eget pulvinar elit cursus eget.
+Nunc quis pharetra odio.
+Donec lacus leo, pulvinar quis vestibulum eget, porta id nibh.
 
@@
 
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Maecenas vulputate ultricies lorem, quis consectetur erat tristique id.
+Nulla eget nunc in urna vestibulum ornare ac sed purus.
+Curabitur consequat gravida turpis in rutrum.
+Nulla vehicula condimentum luctus.
+Nam venenatis facilisis orci sed ullamcorper.
+In felis leo, rutrum nec vestibulum vitae, lacinia at ipsum.
+Praesent orci nibh, pellentesque vitae placerat eget, tempus eget libero.
+Duis eleifend, orci nec pretium condimentum, quam erat euismod quam, sed accumsan erat lacus in felis.
+Aliquam vitae leo sem.
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+Etiam consequat ante eu turpis molestie vel gravida felis varius.
+Vestibulum tincidunt, velit quis convallis imperdiet, est nisi aliquet mauris, eget tempus metus eros eget erat.
+Aenean sit amet dui vel urna pretium dictum nec sed elit.
+Vivamus feugiat dictum neque imperdiet ultrices.
+Nullam commodo rhoncus elit id adipiscing.
+Nam nec turpis ut nisi pulvinar blandit at tincidunt dolor.
+
+Integer dictum tristique felis vitae lobortis.
+Quisque hendrerit, mi vel vestibulum sagittis, nulla leo rhoncus nisl, ac lobortis nisi lorem quis nisl.
+Nullam vehicula magna convallis odio semper vestibulum.
+Ut lobortis, purus eu sodales congue, sapien dolor consectetur turpis, vitae luctus nibh elit et eros.
+Nam tempor felis eget dui laoreet vehicula.
+Praesent imperdiet hendrerit elit sed tempus.
+Phasellus feugiat pretium metus id scelerisque.
+Morbi ligula lectus, blandit in vestibulum id, fermentum sit amet augue.
+Donec pharetra molestie euismod.
+Nulla porttitor feugiat purus, in egestas lorem venenatis sed.
+Phasellus quis interdum diam.
+Ut congue, magna at malesuada luctus, augue urna dignissim nulla, congue lacinia metus felis eget odio.
+Vestibulum et nisl sodales quam commodo laoreet.
+Ut a tortor tortor.
+
 \section{Contributions}
@@
 \section{ Acknowledgments}
-Thank you to Dr. Jin Tian and our TA Ru He for their guidance during this research project. We also extend our thanks to our friends for their help in manual labeling of tweets.
+Thank you to Dr.
+Jin Tian and our class teaching assistant, Ru He, for their helpful guidance during this research project.
+We also extend our thanks to our friends for their help in manual labeling of tweets.
 
-\bibliographystyle{plain}
+\bibliographystyle{plainnat}
 \bibliography{paper}

### 2012-12-04 classify/src/main/java/common/PipeFactory.java
updated pipes

@@ -13,6 +13,7 @@ import cc.mallet.pipe.CharSequence2TokenSequence;
 import cc.mallet.pipe.CharSequenceLowercase;
 import cc.mallet.pipe.FeatureSequence2FeatureVector;
 import cc.mallet.pipe.Input2CharSequence;
+import cc.mallet.pipe.Noop;
 import cc.mallet.pipe.Pipe;
 import cc.mallet.pipe.SerialPipes;
 import cc.mallet.pipe.Target2Label;
@@ -32,7 +33,7 @@ public class PipeFactory {
 						labels.toString());
 			}
 
-		}.add(new SetFactory<Pipe>() {
+		}.add(new SetFactory<Pipe>(true) {
 			@Override
 			protected void build() {
 				this.add(new Input2CharSequence("UTF-8"), "Input2CharSequence");
@@ -64,6 +65,13 @@ public class PipeFactory {
 				this.add(new TokenSequenceRemoveStopwords(),
 						"TokenSequenceRemoveStopwords");
 				this.add(new Stemmer(), "Stemmed");
+			}
+
+		}).add(new SetFactory<Pipe>(true) {
+			@Override
+			protected void build() {
+				this.add(new Noop(), "NGRAM1");
+				this.add(new TokenSequenceNGrams(new int[] {1, 2}), "NGRAM2");
 			}
 
 		}).add(new SetFactory<Pipe>(true) {

### 2012-12-04 paper/paper.tex
major updates to paper, added parser to Main

--- 2012-12-03 paper/paper.tex
@@
 It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products.
-Using machine learning techniques, we analyze the accuracy of classifying whether tweets are part of the public opinion about a particular company or mearly contain keywords related to the company.
+Using machine learning techniques, we analyze the accuracy of classifying whether tweets are part of the public opinion about a particular company or merely contain keywords related to the company.
 %Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
@@
 Our dataset consists of approximately 2,000 tweets of which 64\% are related to public opinion about the company Apple, Inc. The other 36\% are not, but still contain keywords related to the company.
-Peliminary results have shown significant increases in accuracy % TODO insert actual numbers
-by using domain-specific tokenizers, while suprisingly showing decreases in classification accurracy for other standard preproccessing methods such as n-grams.
+Preliminary results have shown significant increases in accuracy % TODO insert actual numbers
+by using domain-specific tokenizers, while surprisingly showing decreases in classification accuracy for other standard preprocessing methods such as n-grams.%maybe?
 \end{quote}
@@
 \section{Introduction}
-Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on sentiment \citeauthor{Ruiz}, ... [ADD MORE]
+Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on user sentiment (\citeauthor{Ruiz}) and identifying characteristics of Twitter users (\citeauthor{conf/icwsm/PennacchiottiP11}) to tracking political protests and uncovering scams (\citeauthor{ICWSM101540}).
 In many cases, the problem of determining which tweets are relevant for a particular application is prerequisite to meaningful results.
-In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interest natural language processing problem in many cases.
-We present a system to disambiguate tweets about the company Apple.
+Use of hashtags and username references on Twitter through syntax conventions (prepending with \# and @, respectively) can be used to select a subset of the tweets about a particular topic.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+\textbf{@Apple} please make a squid \textbf{\#emoji} so I can put \\
+one next to \textbf{@squidneyy22}'s name\\ \hline
+Maybe \textbf{\#Apple} will release \textbf{\#iTunes11} \\
+tomorrow. Maybe? \\ \hline
+\end{tabular}
+\caption{Hashtags and username references (note that Apple Inc. does not own the handle @Apple, though it is commonly used this way)}
+\label{tab:myfirsttable}
+\end{table}
+
+In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interest natural language processing problem in many cases, particularly when the topic in question is a commonplace (and thus ambiguous) word, such as "apple," "blackberry," "android," or "adobe" (\citeauthor{journals/ijcsa/YervaMA12}).
+
+Additionally, tweets contain a high rate of errors in grammar, spelling, and punctuation.
+These features are present alongside myriad augmentations of the English language due to internet trends and culture, as well as the desire of packing more information into Twitter's 140-character message limit (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
+Preprocessing is necessary to avoid discarding or misinterpreting these features as noise or part of other tokens during tokenization.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+\textbf{Nvm} i'll buy you an ipad \textbf{\^-\^} \\ \hline
+\#Apple fires "maps" project manager \textbf{loooool} big \\
+ news story here in San Francisco! Go figure. \textbf{:-)} \\ \hline
+Think I might have a \textbf{gf}! \textbf{O\_o} oh \\
+lord\textbf{..} Lets see how this goes. \\ \hline
+\end{tabular}
+\caption{Examples of emoticons and common abbreviations found on Twitter}
+\label{tab:myfirsttable}
+\end{table}
+
+We present a system to disambiguate tweets about the company Apple using a Naive Bayes model, increasing its baseline accuracy by 8\% through use of specialized, Twitter-aware tokenization.
 
 \section{Related Work}
-DUALIST is a system that extends Mallet by user-interactive feedback during training[Settles]. Included in their implementation was a TwitterPipe that performed some simple feature extraction. 
-Part of the Sentiment Analysis Symposium focuses on tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace-based tokenizing %\cite{potts2011}.
+DUALIST is a system that extends Mallet, our machine learning API of choice, by user-interactive feedback during training (\citeauthor{Settles:2011:CLF:2145432.2145588}).
+Included in his implementation was a preprocessing step that performed some simple Twitter-specific feature extraction and tokenization.
+Part of the Sentiment Analysis Symposium focuses on Twitter-aware tokenization of tweets for sentiment analysis, demonstrating that it provides consistent improvement over whitespace- and Treebank-based tokenization \cite{potts2011}.
 A good deal of research has been done into sentiment classification of tweets, which requires very similar text processing and tokenization \cite{Pak10}.
+Laboreiro et al focus on the problem of tokenizing, using support vector machines (SVM) to improve upon the accuracy of rule-based tokenization, succeeded in improving from 85\% to 96\% token accuracy (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
+Yerva et al construct classifiers to disambiguate tweets containing company-related keywords, primarily using profiles containing company background knowledge (\citeauthor{journals/ijcsa/YervaMA12}).
 
@@
 \subsection{Corpus creation}
-By accessing the Twitter "Firehose" stream through their public API, we harvested 115,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
-This provides us a smaller set of features in the overall corpus.
+By accessing the Twitter "Firehose" stream through their public API, we harvested 100,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
+This provides us a smaller set of features in the overall corpus, with a much higher prior confidence that each individual tweet is of interest.
 The keywords used for the company of choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
-...\\
+
+[INSERT LIST OF KEYWORDS]...\\
 
@@
 We make the assumption that spam will be filtered from the testing set.
-This could be done via an existing Naive Bayes classifier, but we simply did not include instances of spam in our corpus during the manual labeling process.
+This could be done via an existing Naive Bayes classifier %[INSERT REFERENCE FOR TWEET SPAM FILTERING]
+, but we simply did not include instances of spam in our corpus during the manual labeling process.
 We collected our tweets over the course of twelve hours.
@@
 We filtered these duplicates out of the dataset as well to prevent over-fitting in our model.
-After filtering, our original set of 115,000 tweets was reduced to 65,000.
-A representative sample of non-spam, non-duplicate tweets has composition of 60\% topical instances and 40\% false positives [need to analyze this for sure].
+After filtering, our original set of 100,000 tweets was reduced to 50,000.
+A representative sample of non-spam, non-duplicate tweets has a composition of 64\% topical instances and 36\% false positives.
 
-A computer-posted spam tweet:
-\begin{quote}
-I've collected 10,650 gold coins! http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
-\end{quote}
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	I've collected 10,650 gold coins! \\ http://t.co/H0V0O6yP \#ipad, \#ipadgames, \#gameinsight\\
+	\hline
+\end{tabular}
+\caption{A computer-posted spam tweet}
+\end{table}
 
-A retweet, signified by "RT":
-\begin{quote}
-RT @PHILerNotebook: Trying to fix my Mac. This gray loading bar takes 10 minutes to start up. Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
-\end{quote}
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	RT @PHILerNotebook: Trying to fix my Mac. \\ This gray loading bar takes 10 minutes to start up. \\ Grr. Shall take it to an \_Apple\_ \_store\_ soon! \\
+	\hline
+\end{tabular}
+\caption{A retweet, signified by "RT"}
+\end{table}
 
 We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. \\
-Data sets and scripts used for processing text data are available on the project website.\\
+Data sets and scripts used for processing text data are available on the project website. (http://tweets.curtisullerich.com/)\\
 
@@
 
-We do all machine learning with the Mallet%\cite{McCallumMALLET} library developed by the University of Massachusetts.
-Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweets text and ending in Mallet's internal FeatureVector format.
-We built several Pipes to analyze the effect of different filters and processes on the accuracy of classification.
-Not every Pipe proved to increase accuracy--some decreased it.
+We do all machine learning with the Mallet library developed by the University of Massachusetts \cite{McCallumMALLET}.
+Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweet text and ending in Mallet's internal FeatureVector format.
+We built and tested several Pipes to analyze the effect of different filters and processes on the accuracy of classification.
+Not every Pipe proved to increase accuracy--some decreased it, as presented in the results.
 We present the descriptions of and motivations for these Pipes here.
@@
 \subsubsection{Feature-space Enrichment} ~\\
-\textit{Stopword removal}: We wrote a Pipe to remove any tokens that appeared in a list of the 50 most common words in the English language.\\
+\textit{Stopword removal}: We used Mallet's TokenSequenceRemoveStopwords Pipe to remove 500 of the most common words in the English language from each tweet.
+We remove these words because of the high likelihood of many tweets containing these words, without contributing significant discriminatory features to the tweets.
+%TODO [REFERENCE NLP PAPER ABOUT STOPWORD REMOVAL]
+\\
 ~\\
-\textit{N-grams}: Using n-grams is a common method of increasing the number of features present in short text [FIND CITATION].
-Often, this is enough to increase accuracy significantly.
-During our testing, this was not the case.
-Rather, including bigrams and trigrams actually reduced accuracy slightly.\\
+\textit{Bigrams}: Using n-grams is a common method of increasing the number of features present in short text %[FIND CITATION]
+. Often, this is enough to increase accuracy significantly%CITATION
+. As discussed in the tokenization section below, we used selective bigramming, which yielded increases in accuracy in almost all test cases.\\
 ~\\
@@
 For instance, angle brackets are replaced with \&lt; and \&gt; (less-than and greater-than), causing emoticons, for instance, to no longer be parseable.
-The emoticon \">.<", for instance, would be "\&gt;.\&lt;".
-This Pipe un-escapes all such entities, making them easier to parse.\\
+The emoticon ">.<", for instance, would be "\&gt;.\&lt;".
+Necessarily, this Pipe un-escapes all such entities, making them easier to parse.\\
 ~\\
-\textit{URL replacement}: 
-~\\
-\textit{Spell checking}: Twitter's user-generated content contains a large volume of misspelled words.
+\textit{URL replacement}: In our dataset, 60\% of the 100,000 tweets we collected contained a link.
+As the vast majority of these are unique, and shortened using a URL shortener, often Twitter's own t.co.
+Links, then, lose any features that may have been parsed from the URL, which often contains a domain name or title that may be useful in discriminating especially ambiguous links.
+Consider, for instance, the tweet "hmmm http://t.co/39D8I3qM" which leaves a parser completely unaware of the true content of the tweet.
+Following this URL leads to 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade/', which is clearly related to Apple.
+This pipe replaces the link itself in the tweet with the title of the destination web page: "iPhone 5 vs iPhone 4S: Should You Upgrade?
+| Redmond Pie." In cases where the title is empty, we instead replace the shortened link with the resolved URL, which is 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade' in this case.
+In many cases like this, there is not other way to distinguish the content of a tweet.
+From our dataset of 100,000 tweets, 102 tweets contained \textit{only} a link, while 608 tweets contained only a link and fewer than 20 other characters.
+While this is a fairly small portion of the overall dataset for training purposes, it can be crucial in making decision on novel test instances.
+\textit{Spell checking}: Twitter's user-generated content contains a large volume of misspelled words (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
 Using a spell-checking library, we wrote a Pipe to replace unrecognized words (misspelled words) with their corrections if the confidence for correction was above a certain threshold.
+Our intention was to reduce the noise in the feature set by eliminating common misspellings.
+This did not provide any statistically significant change in our results.
 \\
@@
 ~\\
-\textit{Stemming}: Stemming is the process of reducing words to their "stem." While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
-Therefore the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not the true linguistic stem.
-We used the standard Porter stemmer to implement this[CITATION].\\
+\textit{Stemming}: Stemming is the process of reducing words to their "stem," in order to group different forms of the same word into a single feature.
+While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
+For instance, the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not the true linguistic stem, or a real word.
+We used the standard Porter stemmer to implement this%[CITATION].
+In some cases, stemming proved to increase our accuracy.
+\\
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[height=7cm]{chart}
+\caption{Accuracy Chart}
+\label{fig:chart}
+\end{figure*}
 
@@
 ~\\
-Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenization system due to the high level of noise in the feature set [citation and more details].
+Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenization system due to the high level of noise in the feature set.
 Tweets are limited to 140 characters, which limits the total number of features possible.
-Some of the many natural language processing dilemmas present in tweets include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, and hashtags, to name a few.\\
+Some of the many natural language processing dilemmas present in tweets include excessive and irregular punctuation, frequent misspellings, emoticons, URLs, and hashtags, as discussed in the introduction.\\
 
-\begin{quote}
-Cool ranch , 4 berry sundae , apple juice \#yessuh \#latenight \#snack http://t.co/ttc3vujp 
-I just poured apple juice on my cereal.. Gah. \#SoTired 
-I hate Siri.. -\_\_\_- 
-\end{quote}
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	Cool ranch , 4 berry sundae , apple juice \textbf{\#yessuh} \\ 
+	\textbf{\#latenight \#snack} http://t.co/ttc3vujp \\ \hline
+	I just poured apple juice on my cereal\textbf{..} Gah. \textbf{\#SoTired} \\ \hline
+	I hate Siri\textbf{.. -\_\_\_-} \\
+	\hline
+\end{tabular}
+\caption{Examples of difficult tokenizations}
+\label{tab:tokenization_examples}
+\end{table}
 
@@
 
-Searching for emoticons in this tweet will extract :/ as an emoticon, effectively breaking up the URL.
-\begin{quote}
-Now on my iphone ?? http://t.co/Rqr1RL2R 
-\end{quote}
-
-Additionally, users often include emoticons or links after text with no delimiting whitespace.
-
-\begin{quote}
-I listen to my iPod every day and it's just broke omg:(!!
-\end{quote}
-
-Extracting tokens using this layered approach eliminates many of these problems.
+Searching for emoticons in the tweet "Now on my iphone ??
+http://t.co/Rqr1RL2R" will extract ":/" as an emoticon, effectively breaking up the URL.
+Additionally, users often include emoticons or links after text with no delimiting whitespace, such as "I listen to my iPod every day and it's just broke \textbf{omg:(!!}." Extracting tokens using our layered approach eliminates many of these problems.\\
 
 After tokenizing these special features in order (URLs, emoticons, usernames, and hashtags) we are left with a fragmented tweet containing myriad punctuation, capitalization, and creative spellings.
-As done by Potts (2011) we normalize the length of all letter sequences greater than two, as in English, these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
-In the following tweet, "loooool" is normalized to "loool".
+As done by \citet{potts2011} we normalize the length of all letter sequences greater than two, as in English these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
+In the following tweet, for instance, "loooool" is normalized to "loool".
 \begin{quote}
-\#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now loooool \#OoRITE2OutNow https://t.co/r4n4cn6C 
+\#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now \textbf{loooool} \#OoRITE2OutNow https://t.co/r4n4cn6C 
 \end{quote}
@@
 
-As presented in our results, because of irregular capitalization, two tokens likely to be semantically identical with respect to company classification may be represented in multiple cases: {Nooo, NOOO, nooo, NoOo} is a prime example.
+As presented in our results, because of irregular capitalization, two tokens likely to be semantically identical with respect to company classification may be represented in multiple cases.
+{Nooo, NOOO, nooo, NoOo} is a prime example.
 To alleviate this, we attempt three different approaches.
@@
 In the second, we lowercase any text that is not in all caps.
-This serves to retain acronyms.
-In the third, we change all remaining tokens to lowercase, leaving the case of all strings containing "apple" (case insensitive) alone.
-We made this decision based on the semantic difference between the capitalization of Apple the company and apple the fruit.
+This serves to retain acronyms and any text specifically place in all caps, while combining words capitalized because of sentence boundaries with their lowercase appearances, for instance.
+In the third approach, we change all remaining tokens to lowercase, except for leaving the case of all strings containing "apple" (case insensitive) alone.
+We made this decision based on the semantic difference between the capitalization of Apple the company and apple the fruit, which is a very significant feature in our dataset.
 While correct capitalization is naturally not always present for this token, this is one case where capitalization serves to disambiguate.
+In our dataset, "Apple" appeared 11784 times in 10500 tweets, "apple" appeared 4765 times in 4508 tweets, and other case-variations appeared 292 times in 237 tweets (all but one of which was "APPLE").
 This same principle can be generalized to a larger set of keywords and applied to other companies in a similar fashion.
+\\
+
+Optionally, our tokenizer will remove the token "RT" from all tweets.
+3986 tweets in our dataset contain this token, signifying a retweet.
+Not knowing whether this feature added discriminatory power to our classifier, we toggled its inclusion during testing and found that removing it did lead to a slight increase in accuracy on our tests.\\
+
+Any tokens remaining at this point during tokenization are very likely to words in phrases.
+In order to focus the feature set, we split by whitespace and remove any non-word characters other than percent and dollar signs, stripping punctuation, quotation marks, parentheses, etc.
+\\
+
+We chose to apply bigramming to only the tokens parsed in this final step.
+Bigramming led to a statistically significant increase in our results over the same tokenization without bigramming, and even moreso over whitespace-split tokenization with or without bigramming applied.
+
+We constructed this tokenizer such that any step in tokenizing can be toggled upon instantiation in order to test the impact of each feature.\\
 
@@
 \section{Results}
+
 ...baseline using priors
@@
 We could test the robustness of this system by applying this process to other companies for a similar-length time slice of training data.
-We could also test this model against tweets from a different time span to determine whether the data is subject to temporal overfitting, and to what degree.
+We could also test this model against tweets from a different time span to determine whether the data is subject to temporal overfitting, and to what degree.\\
 
-[These guys] demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification.
+Yerva et al demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification (\citeauthor{journals/ijcsa/YervaMA12}).\\
 
-Inclusion of background knowledge.
+Wang et al have shown improvements over the bag-of-words approach to text classification using Wikipedia as a thesaurus for term disambiguation.
+We could use this to enrich the feature set found in tweets and relate similar or co-occurring words in tweets (\citeauthor{Wang:2008:UWC:1510528.1511383}, \citeauthor{Wang:2009:UWK:1554488.1554492}).\\
 
-Use of Wikipedia for disambiguation.
+Our tokenization process makes several simplifying assumptions that we could address.
+We assume certain classes of emoticons are not used often enough to be significant, and leave punctuation out of our feature set.
+We could measure the presence of these (and more) features on Twitter data and adjust our tokenization process to reflect that.\\
 
@@
 All code is available through our project website.
-We also provide a corpus of 115,000 tweets selected by Apple-related keyword and our labeled data set of 2000 tweets.
-The bash scripts used to filter the data for near-duplicates and spam are also available for download.
+We also provide a corpus of 100,000 tweets selected by Apple-related keyword and our labeled data set of 2000 tweets.
+The bash scripts used to filter the data for near-duplicates and spam are also available for download.\\
 
 \section{ Acknowledgments}
-Thank you to Dr. Jin Tian and our TA Ru He for their guidance during this research project. We also extend our thanks to our friends for their help in manual labeling of tweets.
+Thank you to Dr.
+Jin Tian and our class teaching assistant, Ru He, for their helpful guidance during this research project.
+We also extend our thanks to our friends for their help in manual labeling of tweets.
 
-\bibliographystyle{plain}
+\bibliographystyle{plainnat}
 \bibliography{paper}

### 2012-12-04 classify/src/main/java/classification/Main.java

@@ -1,9 +1,34 @@
 package classification;
 
+import java.io.File;
 import java.io.IOException;
+import java.util.Scanner;
 
 public class Main {
 	public static void main(String... args) throws IOException {
+
+		Scanner s = new Scanner(new File("/home/curtis/Dropbox/Shared Folders/apple/allsorted"));
+		int i = 0;
+		while (s.hasNextLine()) {
+			String l = s.nextLine();
+
+			String ls[] = l.split("\t");
+			if (i == 0) {
+				System.out.print(ls[1]);
+			} 
+				System.out.print("\t" + ls[2]);
+			if (i == 17) {
+				if (!ls[0].equals("1800")) {
+					System.out.println("FAIL");
+					System.exit(1);
+				}
+				System.out.print("\n");
+				i = -1;
+			} 
+
+			i++;
+
+		}
 		// ModelUpdater m = new ModelUpdater();
 		// Classifier c = m.createNewCompanyWikipediaModel();
 

### 2012-12-04 paper/paper.tex

@@
 It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products.
-Using machine learning techniques, we analyze the accuracy of classifying whether tweets are part of the public opinion about a particular company or merely contain keywords related to the company.
+Using machine learning techniques, we analyze the accuracy of classifying whether tweets directly mention a particular company or mearly contain keywords related to the company.
 %Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
@@
 \includegraphics[height=7cm]{chart}
-\caption{Accuracy Chart}
+\caption{Accuracy vs. Training Corpus Size for All Text Processing Combinations}
 \label{fig:chart}
@@
 
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{chart_twitterVSwhitespace}
+\caption{Accuracy With Stemming and Stopword Removal}
+\label{fig:chart_twitterwhitespace}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{chart_twitterVSwhitespace_detailed}
+\caption{Accuracy For Twitter and Whitespace Tokenizers}
+\label{fig:chart_twitterwhitespace_detailed}
+\end{figure}
+
 \section{Conclusion and Future Work}

### 2012-12-05 paper/paper.tex
updated results

@@
 \section{Results}
+Using whitespace-based tokenization with a Naive Bayes classifier, we achieve a baseline accuracy of 76\% %correct this exactly!
+compared to the prior probability of tweet about Apple of 64\%.
+For simplicity of analysis, we compared the results of every permutation of our pipeline steps, training on 100 through 1800 tweets in increments of 100, in order to find the combinations that exceed or violate our expectations.
+We found that our Twitter-aware tokenizer outperformed whitespace tokenization by [THIS AMOUNT].
+Applying stemming and stop word removal to both pipelines increased the accuracy for almost every case, though widening the gap.
 
-...baseline using priors
-  baseline using whitespace splitting in naive bayes.
   select interesting improvements.
+  Need to mention the performance of each pipe!
   graphs of both validation types
-  most useful features for classification
+  Include most useful features for classification
 

### 2012-12-05 paper/paper.tex
paper

@@
 We aim to survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations.
-Our dataset consists of approximately 2,000 tweets of which 64\% are related to public opinion about the company Apple, Inc. The other 36\% are not, but still contain keywords related to the company.
+Our dataset consists of approximately 2,000 tweets of which 64\% directly mention the company Apple, Inc or one of its products.
+The other 36\% are not, but still contain keywords related to the company.
 Preliminary results have shown significant increases in accuracy % TODO insert actual numbers
@@
 This provides us a smaller set of features in the overall corpus, with a much higher prior confidence that each individual tweet is of interest.
-The keywords used for the company of choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
+The keywords used for the company often choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
 

### 2012-12-07 paper/paper.tex
Small revisions to the paper and added works to the bib

@@
 While this is a fairly small portion of the overall dataset for training purposes, it can be crucial in making decision on novel test instances.
+Pak and Paroubek also noted the need to handle URLs in tweets, however, rather than adding any new text, they chose to remove the link entirely  (\citeauthor{Alexander Pak and Patrick Paroubek}).
+~\\
 \textit{Spell checking}: Twitter's user-generated content contains a large volume of misspelled words (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
@@
 For instance, the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not the true linguistic stem, or a real word.
-We used the standard Porter stemmer to implement this%[CITATION].
+We used the standard Porter stemmer to implement this (\citeauthor{Porter, M.}).
 In some cases, stemming proved to increase our accuracy.

### 2012-12-07 paper/paper.tex
updated paper

--- 2012-12-05 paper/paper.tex
@@
 Yerva et al construct classifiers to disambiguate tweets containing company-related keywords, primarily using profiles containing company background knowledge (\citeauthor{journals/ijcsa/YervaMA12}).
+Sriram et al presented a system that uses features extracted from the tweet author's profile and the tweet text to classify tweets into the categories of News, Events, Opinions, Deals, and Private Messages (\citeauthor{Sriram:2010:STC:1835449.1835643}).
 
@@
 ~\\
+Tokens are atomic symbols in text that we use as features in training a classifier (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
 Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenization system due to the high level of noise in the feature set.
@@
 
-We approach this problem using a layered token extraction system.
-Using regular expressions, we begin by searching for tokens that may include other, more general tokens.
-A prime example of this is an emoticon appearing in a URL.
-
 Searching for emoticons in the tweet "Now on my iphone ??
-http://t.co/Rqr1RL2R" will extract ":/" as an emoticon, effectively breaking up the URL.
-Additionally, users often include emoticons or links after text with no delimiting whitespace, such as "I listen to my iPod every day and it's just broke \textbf{omg:(!!}." Extracting tokens using our layered approach eliminates many of these problems.\\
+http://t.co/Rqr1RL2R" will extract ":/" as an emoticon, effectively breaking up the URL token.
+Additionally, users often include emoticons or links after text with no delimiting whitespace, such as "I listen to my iPod every day and it's just broke \textbf{omg:(!!}." We approach this problem using a layered token extraction system.
+Our goal is that any token pattern which may contain false positives of other tokens (e.g.
+emoticons inside URLS) is extracted before any potential interior false positive tokens.
+Extracting tokens using our layered approach eliminates many problems introduced by Twitter's unique feature space.
+Note that compiling an exhaustive list of all emoticon combinations is difficult, if not impossible, because the landscape of emoticons is very diverse and changes over time (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
+Instead, we focus on capturing a "large enough" set of emoticons by extracting a large number of the most common ones.
+\\
 
@@
 
-Any tokens remaining at this point during tokenization are very likely to words in phrases.
+Any tokens remaining at this point during tokenization are very likely to be words in phrases.
 In order to focus the feature set, we split by whitespace and remove any non-word characters other than percent and dollar signs, stripping punctuation, quotation marks, parentheses, etc.
@@
 
+Sriram et al found that utilizing author profiles provide a good method for further disambiguation of tweets into categories, as authors tend to tweet messages within a limited set of categories.
+They also delineate a set of eight features (8F) used for training, instead of using the Bag-of-Words approach as we do.
+Through further analysis of the most useful features found in our approach, we could also choose a discrete set of binary or n-ary features most relevant to this classification task and explore its accuracy versus BOWc (\citeauthor{Sriram:2010:STC:1835449.1835643}).
+
 \section{Contributions}

### 2012-12-07 paper/paper.tex
replaced quotes

@@
 
-In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interest natural language processing problem in many cases, particularly when the topic in question is a commonplace (and thus ambiguous) word, such as "apple," "blackberry," "android," or "adobe" (\citeauthor{journals/ijcsa/YervaMA12}).
+In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interest natural language processing problem in many cases, particularly when the topic in question is a commonplace (and thus ambiguous) word, such as 'apple,' 'blackberry,' 'android,' or 'adobe' (\citeauthor{journals/ijcsa/YervaMA12}).
 
@@
 \textbf{Nvm} i'll buy you an ipad \textbf{\^-\^} \\ \hline
-\#Apple fires "maps" project manager \textbf{loooool} big \\
+\#Apple fires 'maps' project manager \textbf{loooool} big \\
  news story here in San Francisco! Go figure. \textbf{:-)} \\ \hline
@@
 \subsection{Corpus creation}
-By accessing the Twitter "Firehose" stream through their public API, we harvested 100,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
+By accessing the Twitter 'Firehose' stream through their public API, we harvested 100,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
 This provides us a smaller set of features in the overall corpus, with a much higher prior confidence that each individual tweet is of interest.
@@
 	1 more day whoop plus safari ride yay \\ \hline
-	Ashley staples an apple.  "AHHHH!!!! \\ Apple juice in my eye!" \\ \hline
+	Ashley staples an apple.  'AHHHH!!!! \\ Apple juice in my eye!' \\ \hline
 	I ain't seen uncle Mac in a while \\
@@
 
-We define a tweet to be "about" Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers.
+We define a tweet to be 'about' Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers.
 We make the assumption that spam will be filtered from the testing set.
@@
 We collected our tweets over the course of twelve hours.
-On Twitter, a single message posted is often reposted, or "re-tweeted," many more times in a very short timespan.
+On Twitter, a single message posted is often reposted, or 're-tweeted,' many more times in a very short timespan.
 Because of the small timespan of our data collection, a large number of retweets (effectively duplicates) appeared in the dataset.
@@
 \end{tabular}
-\caption{A retweet, signified by "RT"}
+\caption{A retweet, signified by 'RT'}
 \end{table}
@@
 We do all machine learning with the Mallet library developed by the University of Massachusetts \cite{McCallumMALLET}.
-Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweet text and ending in Mallet's internal FeatureVector format.
+Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing 'Pipes' to transform the data, beginning in our case with raw tweet text and ending in Mallet's internal FeatureVector format.
 We built and tested several Pipes to analyze the effect of different filters and processes on the accuracy of classification.
@@
 For instance, angle brackets are replaced with \&lt; and \&gt; (less-than and greater-than), causing emoticons, for instance, to no longer be parseable.
-The emoticon ">.<", for instance, would be "\&gt;.\&lt;".
+The emoticon '\rangle.\langle', for instance, would be '\&gt;.\&lt;'.
 Necessarily, this Pipe un-escapes all such entities, making them easier to parse.\\
@@
 Links, then, lose any features that may have been parsed from the URL, which often contains a domain name or title that may be useful in discriminating especially ambiguous links.
-Consider, for instance, the tweet "hmmm http://t.co/39D8I3qM" which leaves a parser completely unaware of the true content of the tweet.
+Consider, for instance, the tweet 'hmmm http://t.co/39D8I3qM' which leaves a parser completely unaware of the true content of the tweet.
 Following this URL leads to 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade/', which is clearly related to Apple.
-This pipe replaces the link itself in the tweet with the title of the destination web page: "iPhone 5 vs iPhone 4S: Should You Upgrade?
-| Redmond Pie." In cases where the title is empty, we instead replace the shortened link with the resolved URL, which is 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade' in this case.
+This pipe replaces the link itself in the tweet with the title of the destination web page: 'iPhone 5 vs iPhone 4S: Should You Upgrade?
+| Redmond Pie.' In cases where the title is empty, we instead replace the shortened link with the resolved URL, which is 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade' in this case.
 In many cases like this, there is not other way to distinguish the content of a tweet.
@@
 ~\\
-\textit{Stemming}: Stemming is the process of reducing words to their "stem," in order to group different forms of the same word into a single feature.
+\textit{Stemming}: Stemming is the process of reducing words to their 'stem,' in order to group different forms of the same word into a single feature.
 While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
-For instance, the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not the true linguistic stem, or a real word.
+For instance, the stem of the related words 'argue,' 'argued,' and 'arguing' all have the stem of 'argu,' even though argu is not the true linguistic stem, or a real word.
 We used the standard Porter stemmer to implement this (\citeauthor{Porter, M.}).
@@
 
-Searching for emoticons in the tweet "Now on my iphone ??
-http://t.co/Rqr1RL2R" will extract ":/" as an emoticon, effectively breaking up the URL token.
-Additionally, users often include emoticons or links after text with no delimiting whitespace, such as "I listen to my iPod every day and it's just broke \textbf{omg:(!!}." We approach this problem using a layered token extraction system.
+Searching for emoticons in the tweet 'Now on my iphone ??
+http://t.co/Rqr1RL2R' will extract ':/' as an emoticon, effectively breaking up the URL token.
+Additionally, users often include emoticons or links after text with no delimiting whitespace, such as 'I listen to my iPod every day and it's just broke \textbf{omg:(!!}.' We approach this problem using a layered token extraction system.
 Our goal is that any token pattern which may contain false positives of other tokens (e.g.
@@
 Note that compiling an exhaustive list of all emoticon combinations is difficult, if not impossible, because the landscape of emoticons is very diverse and changes over time (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
-Instead, we focus on capturing a "large enough" set of emoticons by extracting a large number of the most common ones.
+Instead, we focus on capturing a 'large enough' set of emoticons by extracting a large number of the most common ones.
 \\
@@
 As done by \citet{potts2011} we normalize the length of all letter sequences greater than two, as in English these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
-In the following tweet, for instance, "loooool" is normalized to "loool".
+In the following tweet, for instance, 'loooool' is normalized to 'loool'.
 \begin{quote}
@@
 This serves to retain acronyms and any text specifically place in all caps, while combining words capitalized because of sentence boundaries with their lowercase appearances, for instance.
-In the third approach, we change all remaining tokens to lowercase, except for leaving the case of all strings containing "apple" (case insensitive) alone.
+In the third approach, we change all remaining tokens to lowercase, except for leaving the case of all strings containing 'apple' (case insensitive) alone.
 We made this decision based on the semantic difference between the capitalization of Apple the company and apple the fruit, which is a very significant feature in our dataset.
 While correct capitalization is naturally not always present for this token, this is one case where capitalization serves to disambiguate.
-In our dataset, "Apple" appeared 11784 times in 10500 tweets, "apple" appeared 4765 times in 4508 tweets, and other case-variations appeared 292 times in 237 tweets (all but one of which was "APPLE").
+In our dataset, 'Apple' appeared 11784 times in 10500 tweets, 'apple' appeared 4765 times in 4508 tweets, and other case-variations appeared 292 times in 237 tweets (all but one of which was 'APPLE').
 This same principle can be generalized to a larger set of keywords and applied to other companies in a similar fashion.
@@
 
-Optionally, our tokenizer will remove the token "RT" from all tweets.
+Optionally, our tokenizer will remove the token 'RT' from all tweets.
 3986 tweets in our dataset contain this token, signifying a retweet.
@@
 \section{Experimental Setup}
-...constant-size test set with sliced training
-...comparison to n-fold validation
+In order to determine which combination of preprocessing steps would results in the highest performance, we built a custom evaluation platform that iterates through all possible valid combinations of pipes and evaluates their performance.
+This led to nearly one hundred combinations, as each of the six tokenizer variations was run with and without bigramming, with and without stemming, etc.
+For consistency, the disjoint training and test sets used to evaluate each combination were identical for each iteration.
+To best observe the effects of training set size, training sizes of 50 to 1500 were tested in increments of 50, where each set is a superset of the previous set with 50 new randomly chosen instances, as opposed to using n-fold cross validation, which would not display this characteristic evenly across varied training and testing sizes.
+To evaluate this large set of results, we have chosen three relevant evaluation metrics.
+The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label ('apple' or 'none' in our case).
+Higher values for this metric mean fewer false positives for the desired company, which is the overall goal in this classification task.
+The second metric was recall, or the ratio of correctly classified instances out of the full set of instances which should have the label in question.
+This metric is less relevant to our purpose, but still interesting.
+The sheer scale of Twitter means missing even half of the tweets mentioning a company and mislabeling them as about 'none' is of little consequence.
+Finally we use the F1 metric, a standard combination of precision and recall that is useful in determining overall if some pipeline combination is better than another in both precision and recall.
 

### 2012-12-07 paper/paper.tex
quote matching

@@
 
-In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interest natural language processing problem in many cases, particularly when the topic in question is a commonplace (and thus ambiguous) word, such as 'apple,' 'blackberry,' 'android,' or 'adobe' (\citeauthor{journals/ijcsa/YervaMA12}).
+In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interest natural language processing problem in many cases, particularly when the topic in question is a commonplace (and thus ambiguous) word, such as `apple,' `blackberry,' `android,' or `adobe' (\citeauthor{journals/ijcsa/YervaMA12}).
 
@@
 \textbf{Nvm} i'll buy you an ipad \textbf{\^-\^} \\ \hline
-\#Apple fires 'maps' project manager \textbf{loooool} big \\
+\#Apple fires `maps' project manager \textbf{loooool} big \\
  news story here in San Francisco! Go figure. \textbf{:-)} \\ \hline
@@
 \subsection{Corpus creation}
-By accessing the Twitter 'Firehose' stream through their public API, we harvested 100,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
+By accessing the Twitter `Firehose' stream through their public API, we harvested 100,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
 This provides us a smaller set of features in the overall corpus, with a much higher prior confidence that each individual tweet is of interest.
@@
 	1 more day whoop plus safari ride yay \\ \hline
-	Ashley staples an apple.  'AHHHH!!!! \\ Apple juice in my eye!' \\ \hline
+	Ashley staples an apple.  `AHHHH!!!! \\ Apple juice in my eye!' \\ \hline
 	I ain't seen uncle Mac in a while \\
@@
 
-We define a tweet to be 'about' Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers.
+We define a tweet to be `about' Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers.
 We make the assumption that spam will be filtered from the testing set.
@@
 We collected our tweets over the course of twelve hours.
-On Twitter, a single message posted is often reposted, or 're-tweeted,' many more times in a very short timespan.
+On Twitter, a single message posted is often reposted, or `re-tweeted,' many more times in a very short timespan.
 Because of the small timespan of our data collection, a large number of retweets (effectively duplicates) appeared in the dataset.
@@
 \end{tabular}
-\caption{A retweet, signified by 'RT'}
+\caption{A retweet, signified by `RT'}
 \end{table}
@@
 We do all machine learning with the Mallet library developed by the University of Massachusetts \cite{McCallumMALLET}.
-Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing 'Pipes' to transform the data, beginning in our case with raw tweet text and ending in Mallet's internal FeatureVector format.
+Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing `Pipes' to transform the data, beginning in our case with raw tweet text and ending in Mallet's internal FeatureVector format.
 We built and tested several Pipes to analyze the effect of different filters and processes on the accuracy of classification.
@@
 For instance, angle brackets are replaced with \&lt; and \&gt; (less-than and greater-than), causing emoticons, for instance, to no longer be parseable.
-The emoticon '\rangle.\langle', for instance, would be '\&gt;.\&lt;'.
+The emoticon `\textgreater.\textless', for instance, would be `\&gt;.\&lt;'.
 Necessarily, this Pipe un-escapes all such entities, making them easier to parse.\\
@@
 Links, then, lose any features that may have been parsed from the URL, which often contains a domain name or title that may be useful in discriminating especially ambiguous links.
-Consider, for instance, the tweet 'hmmm http://t.co/39D8I3qM' which leaves a parser completely unaware of the true content of the tweet.
-Following this URL leads to 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade/', which is clearly related to Apple.
-This pipe replaces the link itself in the tweet with the title of the destination web page: 'iPhone 5 vs iPhone 4S: Should You Upgrade?
-| Redmond Pie.' In cases where the title is empty, we instead replace the shortened link with the resolved URL, which is 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade' in this case.
+Consider, for instance, the tweet `hmmm http://t.co/39D8I3qM' which leaves a parser completely unaware of the true content of the tweet.
+Following this URL leads to `http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade/', which is clearly related to Apple.
+This pipe replaces the link itself in the tweet with the title of the destination web page: `iPhone 5 vs iPhone 4S: Should You Upgrade?
+| Redmond Pie.' In cases where the title is empty, we instead replace the shortened link with the resolved URL, which is `http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade' in this case.
 In many cases like this, there is not other way to distinguish the content of a tweet.
@@
 ~\\
-\textit{Stemming}: Stemming is the process of reducing words to their 'stem,' in order to group different forms of the same word into a single feature.
+\textit{Stemming}: Stemming is the process of reducing words to their `stem,' in order to group different forms of the same word into a single feature.
 While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
-For instance, the stem of the related words 'argue,' 'argued,' and 'arguing' all have the stem of 'argu,' even though argu is not the true linguistic stem, or a real word.
+For instance, the stem of the related words `argue,' `argued,' and `arguing' all have the stem of `argu,' even though argu is not the true linguistic stem, or a real word.
 We used the standard Porter stemmer to implement this (\citeauthor{Porter, M.}).
@@
 
-Searching for emoticons in the tweet 'Now on my iphone ??
-http://t.co/Rqr1RL2R' will extract ':/' as an emoticon, effectively breaking up the URL token.
-Additionally, users often include emoticons or links after text with no delimiting whitespace, such as 'I listen to my iPod every day and it's just broke \textbf{omg:(!!}.' We approach this problem using a layered token extraction system.
+Searching for emoticons in the tweet `Now on my iphone ??
+http://t.co/Rqr1RL2R' will extract `:/' as an emoticon, effectively breaking up the URL token.
+Additionally, users often include emoticons or links after text with no delimiting whitespace, such as `I listen to my iPod every day and it's just broke \textbf{omg:(!!}.' We approach this problem using a layered token extraction system.
 Our goal is that any token pattern which may contain false positives of other tokens (e.g.
@@
 Note that compiling an exhaustive list of all emoticon combinations is difficult, if not impossible, because the landscape of emoticons is very diverse and changes over time (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
-Instead, we focus on capturing a 'large enough' set of emoticons by extracting a large number of the most common ones.
+Instead, we focus on capturing a `large enough' set of emoticons by extracting a large number of the most common ones.
 \\
@@
 As done by \citet{potts2011} we normalize the length of all letter sequences greater than two, as in English these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
-In the following tweet, for instance, 'loooool' is normalized to 'loool'.
+In the following tweet, for instance, `loooool' is normalized to `loool'.
 \begin{quote}
@@
 This serves to retain acronyms and any text specifically place in all caps, while combining words capitalized because of sentence boundaries with their lowercase appearances, for instance.
-In the third approach, we change all remaining tokens to lowercase, except for leaving the case of all strings containing 'apple' (case insensitive) alone.
+In the third approach, we change all remaining tokens to lowercase, except for leaving the case of all strings containing `apple' (case insensitive) alone.
 We made this decision based on the semantic difference between the capitalization of Apple the company and apple the fruit, which is a very significant feature in our dataset.
 While correct capitalization is naturally not always present for this token, this is one case where capitalization serves to disambiguate.
-In our dataset, 'Apple' appeared 11784 times in 10500 tweets, 'apple' appeared 4765 times in 4508 tweets, and other case-variations appeared 292 times in 237 tweets (all but one of which was 'APPLE').
+In our dataset, `Apple' appeared 11784 times in 10500 tweets, `apple' appeared 4765 times in 4508 tweets, and other case-variations appeared 292 times in 237 tweets (all but one of which was `APPLE').
 This same principle can be generalized to a larger set of keywords and applied to other companies in a similar fashion.
@@
 
-Optionally, our tokenizer will remove the token 'RT' from all tweets.
+Optionally, our tokenizer will remove the token `RT' from all tweets.
 3986 tweets in our dataset contain this token, signifying a retweet.
@@
 To evaluate this large set of results, we have chosen three relevant evaluation metrics.
-The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label ('apple' or 'none' in our case).
+The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label (`apple' or `none' in our case).
 Higher values for this metric mean fewer false positives for the desired company, which is the overall goal in this classification task.
@@
 This metric is less relevant to our purpose, but still interesting.
-The sheer scale of Twitter means missing even half of the tweets mentioning a company and mislabeling them as about 'none' is of little consequence.
+The sheer scale of Twitter means missing even half of the tweets mentioning a company and mislabeling them as about `none' is of little consequence.
 Finally we use the F1 metric, a standard combination of precision and recall that is useful in determining overall if some pipeline combination is better than another in both precision and recall.

### 2012-12-07 paper/paper.tex
paper

@@
 This provides us a smaller set of features in the overall corpus, with a much higher prior confidence that each individual tweet is of interest.
-The keywords used for the company often choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
+The keywords used for the company of choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
 

### 2012-12-07 paper/paper.tex
Fixing sentences

--- 2012-12-07 paper/paper.tex
@@
 Our dataset consists of approximately 2,000 tweets of which 64\% directly mention the company Apple, Inc or one of its products.
-The other 36\% are not, but still contain keywords related to the company.
+The other 36\% do not, but still contain keywords related to the company.
 Preliminary results have shown significant increases in accuracy % TODO insert actual numbers
@@
 
-In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interest natural language processing problem in many cases, particularly when the topic in question is a commonplace (and thus ambiguous) word, such as 'apple,' 'blackberry,' 'android,' or 'adobe' (\citeauthor{journals/ijcsa/YervaMA12}).
+In some domains, filtering tweets based solely on keywords may be appropriate, but disambiguation remains an interesting natural language processing problem in many cases, particularly when the topic in question is a commonplace (and thus ambiguous) word, such as "apple," "blackberry," "android," or "adobe" (\citeauthor{journals/ijcsa/YervaMA12}).
 
@@
 \textbf{Nvm} i'll buy you an ipad \textbf{\^-\^} \\ \hline
-\#Apple fires 'maps' project manager \textbf{loooool} big \\
+\#Apple fires "maps" project manager \textbf{loooool} big \\
  news story here in San Francisco! Go figure. \textbf{:-)} \\ \hline
@@
 Yerva et al construct classifiers to disambiguate tweets containing company-related keywords, primarily using profiles containing company background knowledge (\citeauthor{journals/ijcsa/YervaMA12}).
-Sriram et al presented a system that uses features extracted from the tweet author's profile and the tweet text to classify tweets into the categories of News, Events, Opinions, Deals, and Private Messages (\citeauthor{Sriram:2010:STC:1835449.1835643}).
 
@@
 \subsection{Corpus creation}
-By accessing the Twitter 'Firehose' stream through their public API, we harvested 100,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
+By accessing the Twitter "Firehose" stream through their public API, we harvested 100,000 tweets using broad keyword filters with the goal of collecting a superset of relevant tweets.
 This provides us a smaller set of features in the overall corpus, with a much higher prior confidence that each individual tweet is of interest.
@@
 	1 more day whoop plus safari ride yay \\ \hline
-	Ashley staples an apple.  'AHHHH!!!! \\ Apple juice in my eye!' \\ \hline
+	Ashley staples an apple.  "AHHHH!!!! \\ Apple juice in my eye!" \\ \hline
 	I ain't seen uncle Mac in a while \\
@@
 
-We define a tweet to be 'about' Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers.
+We define a tweet to be "about" Apple if the tweet mentions the company (via direct reference or stock symbol), one of its products, or a service it offers.
 We make the assumption that spam will be filtered from the testing set.
@@
 We collected our tweets over the course of twelve hours.
-On Twitter, a single message posted is often reposted, or 're-tweeted,' many more times in a very short timespan.
+On Twitter, a single message posted is often reposted, or "re-tweeted," many more times in a very short timespan.
 Because of the small timespan of our data collection, a large number of retweets (effectively duplicates) appeared in the dataset.
@@
 \end{tabular}
-\caption{A retweet, signified by 'RT'}
+\caption{A retweet, signified by "RT"}
 \end{table}
@@
 We do all machine learning with the Mallet library developed by the University of Massachusetts \cite{McCallumMALLET}.
-Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing 'Pipes' to transform the data, beginning in our case with raw tweet text and ending in Mallet's internal FeatureVector format.
+Mallet includes abstractions for a data processing pipeline, during which we use both existing and custom processing "Pipes" to transform the data, beginning in our case with raw tweet text and ending in Mallet's internal FeatureVector format.
 We built and tested several Pipes to analyze the effect of different filters and processes on the accuracy of classification.
@@
 For instance, angle brackets are replaced with \&lt; and \&gt; (less-than and greater-than), causing emoticons, for instance, to no longer be parseable.
-The emoticon '\rangle.\langle', for instance, would be '\&gt;.\&lt;'.
+The emoticon ">.<", for instance, would be "\&gt;.\&lt;".
 Necessarily, this Pipe un-escapes all such entities, making them easier to parse.\\
@@
 Links, then, lose any features that may have been parsed from the URL, which often contains a domain name or title that may be useful in discriminating especially ambiguous links.
-Consider, for instance, the tweet 'hmmm http://t.co/39D8I3qM' which leaves a parser completely unaware of the true content of the tweet.
+Consider, for instance, the tweet "hmmm http://t.co/39D8I3qM" which leaves a parser completely unaware of the true content of the tweet.
 Following this URL leads to 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade/', which is clearly related to Apple.
-This pipe replaces the link itself in the tweet with the title of the destination web page: 'iPhone 5 vs iPhone 4S: Should You Upgrade?
-| Redmond Pie.' In cases where the title is empty, we instead replace the shortened link with the resolved URL, which is 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade' in this case.
+This pipe replaces the link itself in the tweet with the title of the destination web page: "iPhone 5 vs iPhone 4S: Should You Upgrade?
+| Redmond Pie." In cases where the title is empty, we instead replace the shortened link with the resolved URL, which is 'http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade' in this case.
 In many cases like this, there is not other way to distinguish the content of a tweet.
@@
 ~\\
-\textit{Stemming}: Stemming is the process of reducing words to their 'stem,' in order to group different forms of the same word into a single feature.
+\textit{Stemming}: Stemming is the process of reducing words to their "stem," in order to group different forms of the same word into a single feature.
 While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
-For instance, the stem of the related words 'argue,' 'argued,' and 'arguing' all have the stem of 'argu,' even though argu is not the true linguistic stem, or a real word.
+For instance, the stem of the related words "argue," "argued," and "arguing" all have the stem of "argu," even though argu is not the true linguistic stem, or a real word.
 We used the standard Porter stemmer to implement this (\citeauthor{Porter, M.}).
@@
 ~\\
-Tokens are atomic symbols in text that we use as features in training a classifier (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
 Twitter data, and user-generated web content in general, provides unique challenges to an automatic tokenization system due to the high level of noise in the feature set.
@@
 
-Searching for emoticons in the tweet 'Now on my iphone ??
-http://t.co/Rqr1RL2R' will extract ':/' as an emoticon, effectively breaking up the URL token.
-Additionally, users often include emoticons or links after text with no delimiting whitespace, such as 'I listen to my iPod every day and it's just broke \textbf{omg:(!!}.' We approach this problem using a layered token extraction system.
-Our goal is that any token pattern which may contain false positives of other tokens (e.g.
-emoticons inside URLS) is extracted before any potential interior false positive tokens.
-Extracting tokens using our layered approach eliminates many problems introduced by Twitter's unique feature space.
-Note that compiling an exhaustive list of all emoticon combinations is difficult, if not impossible, because the landscape of emoticons is very diverse and changes over time (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
-Instead, we focus on capturing a 'large enough' set of emoticons by extracting a large number of the most common ones.
-\\
+We approach this problem using a layered token extraction system.
+Using regular expressions, we begin by searching for tokens that may include other, more general tokens.
+A prime example of this is an emoticon appearing in a URL.
+
+Searching for emoticons in the tweet "Now on my iphone ??
+http://t.co/Rqr1RL2R" will extract ":/" as an emoticon, effectively breaking up the URL.
+Additionally, users often include emoticons or links after text with no delimiting whitespace, such as "I listen to my iPod every day and it's just broke \textbf{omg:(!!}." Extracting tokens using our layered approach eliminates many of these problems.\\
 
@@
 As done by \citet{potts2011} we normalize the length of all letter sequences greater than two, as in English these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
-In the following tweet, for instance, 'loooool' is normalized to 'loool'.
+In the following tweet, for instance, "loooool" is normalized to "loool".
 \begin{quote}
@@
 This serves to retain acronyms and any text specifically place in all caps, while combining words capitalized because of sentence boundaries with their lowercase appearances, for instance.
-In the third approach, we change all remaining tokens to lowercase, except for leaving the case of all strings containing 'apple' (case insensitive) alone.
+In the third approach, we change all remaining tokens to lowercase, except for leaving the case of all strings containing "apple" (case insensitive) alone.
 We made this decision based on the semantic difference between the capitalization of Apple the company and apple the fruit, which is a very significant feature in our dataset.
 While correct capitalization is naturally not always present for this token, this is one case where capitalization serves to disambiguate.
-In our dataset, 'Apple' appeared 11784 times in 10500 tweets, 'apple' appeared 4765 times in 4508 tweets, and other case-variations appeared 292 times in 237 tweets (all but one of which was 'APPLE').
+In our dataset, "Apple" appeared 11784 times in 10500 tweets, "apple" appeared 4765 times in 4508 tweets, and other case-variations appeared 292 times in 237 tweets (all but one of which was "APPLE").
 This same principle can be generalized to a larger set of keywords and applied to other companies in a similar fashion.
@@
 
-Optionally, our tokenizer will remove the token 'RT' from all tweets.
+Optionally, our tokenizer will remove the token "RT" from all tweets.
 3986 tweets in our dataset contain this token, signifying a retweet.
@@
 
-Any tokens remaining at this point during tokenization are very likely to be words in phrases.
+Any tokens remaining at this point during tokenization are very likely to words in phrases.
 In order to focus the feature set, we split by whitespace and remove any non-word characters other than percent and dollar signs, stripping punctuation, quotation marks, parentheses, etc.
@@
 \section{Experimental Setup}
-In order to determine which combination of preprocessing steps would results in the highest performance, we built a custom evaluation platform that iterates through all possible valid combinations of pipes and evaluates their performance.
-This led to nearly one hundred combinations, as each of the six tokenizer variations was run with and without bigramming, with and without stemming, etc.
-For consistency, the disjoint training and test sets used to evaluate each combination were identical for each iteration.
-To best observe the effects of training set size, training sizes of 50 to 1500 were tested in increments of 50, where each set is a superset of the previous set with 50 new randomly chosen instances, as opposed to using n-fold cross validation, which would not display this characteristic evenly across varied training and testing sizes.
-To evaluate this large set of results, we have chosen three relevant evaluation metrics.
-The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label ('apple' or 'none' in our case).
-Higher values for this metric mean fewer false positives for the desired company, which is the overall goal in this classification task.
-The second metric was recall, or the ratio of correctly classified instances out of the full set of instances which should have the label in question.
-This metric is less relevant to our purpose, but still interesting.
-The sheer scale of Twitter means missing even half of the tweets mentioning a company and mislabeling them as about 'none' is of little consequence.
-Finally we use the F1 metric, a standard combination of precision and recall that is useful in determining overall if some pipeline combination is better than another in both precision and recall.
+...constant-size test set with sliced training
+...comparison to n-fold validation
 
@@
 
-Sriram et al found that utilizing author profiles provide a good method for further disambiguation of tweets into categories, as authors tend to tweet messages within a limited set of categories.
-They also delineate a set of eight features (8F) used for training, instead of using the Bag-of-Words approach as we do.
-Through further analysis of the most useful features found in our approach, we could also choose a discrete set of binary or n-ary features most relevant to this classification task and explore its accuracy versus BOWc (\citeauthor{Sriram:2010:STC:1835449.1835643}).
-
 \section{Contributions}

### 2012-12-07 paper/paper.tex
paper

--- 2012-12-07 paper/paper.tex
@@
 \section{Experimental Setup}
-In order to determine which combination of preprocessing steps would results in the highest performance, we built a custom evaluation platform that iterates through all possible valid combinations of pipes and evaluates their performance.
-This led to nearly one hundred combinations, as each of the six tokenizer variations was run with and without bigramming, with and without stemming, etc.
+In order to determine which combination of preprocessing steps would result in the highest performance, we built a custom evaluation utility that iterates through all possible valid combinations of pipes and evaluates their performance.
+This led to nearly one hundred combinations, as each of six tokenizer variations was run with and without bigramming, with and without stemming, etc.
 For consistency, the disjoint training and test sets used to evaluate each combination were identical for each iteration.
@@
 
-\section{Conclusion and Future Work}
+\section{Contributions and Future Work}
+We have presented a pipeline for processing tweets that increases accuracy and precision of the resulting models.
+We introduce a layered approach to tokenization that sees improvements over other rule-based methods.
+We have built several reusable Java components that extend the Mallet API for processing of data from Twitter.
+We created a TweetJsonIterator that accepts a file of Twitter's JSON-formatted tweets and creates training Instances containing their values for easy processing during model training.
+We have implemented several Pipes that can be reused or easily modified to suit a similar Twitter processing purpose.
+These include Link2Title, Stemmer, SpellCheck, and Tokenize, the latter of which serves as a more extensible tokenizer than Mallet's default.
+We release our testing utility as a new way of comparing multiple similar pipelines.
+All code is available through our project website.
+We also provide a corpus of 100,000 tweets selected by Apple-related keyword and our labeled data set of 2000 tweets.
+The bash scripts used to filter the data for near-duplicates and spam are also available for download.\\
 
@@
 
-Yerva et al demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification (\citeauthor{journals/ijcsa/YervaMA12}).\\
+Yerva et al demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification (\citeauthor{journals/ijcsa/YervaMA12}).
+We believe that inclusion of this in our method could allow us to perform more accurate disambiguation.\\
 
@@
 They also delineate a set of eight features (8F) used for training, instead of using the Bag-of-Words approach as we do.
-Through further analysis of the most useful features found in our approach, we could also choose a discrete set of binary or n-ary features most relevant to this classification task and explore its accuracy versus BOWc (\citeauthor{Sriram:2010:STC:1835449.1835643}).
-
-\section{Contributions}
-We have built several reusable Java components that extend the Mallet API for processing of data from Twitter.
-We created a TweetJsonIterator that accepts a file of Twitter's JSON-formatted tweets and creates training Instances containing their values for easy processing during model training.
-We have implemented several Pipes that can be reused or easily modified to suit a similar Twitter processing purpose.
-These include Link2Title, Stemmer, SpellCheck, and Tokenize, the latter of which serves as a more extensible tokenizer than Mallet's default.
-All code is available through our project website.
-We also provide a corpus of 100,000 tweets selected by Apple-related keyword and our labeled data set of 2000 tweets.
-The bash scripts used to filter the data for near-duplicates and spam are also available for download.\\
+Through further analysis of the most useful features found in our approach, we could also choose a discrete set of binary or n-ary features most relevant to this classification task and explore its accuracy versus Bag-of-Words (\citeauthor{Sriram:2010:STC:1835449.1835643}).
 

### 2012-12-07 paper/paper.tex
Edits

--- 2012-12-07 paper/paper.tex
@@
 ~\\
-\textit{Bigrams}: Using n-grams is a common method of increasing the number of features present in short text %[FIND CITATION]
+\textit{Bigrams}: Using n-grams is a common method of increasing the number of features present in short text%[FIND CITATION]
 . Often, this is enough to increase accuracy significantly%CITATION
@@
 While this is a fairly small portion of the overall dataset for training purposes, it can be crucial in making decision on novel test instances.
-Pak and Paroubek also noted the need to handle URLs in tweets, however, rather than adding any new text, they chose to remove the link entirely  (\citeauthor{Alexander Pak and Patrick Paroubek}).
+Pak and Paroubek also noted the need to handle URLs in tweets, however, rather than adding any new text, they chose to remove the link entirely  (\citeauthor{PAK10.385}).
 ~\\
@@
 For instance, the stem of the related words `argue,' `argued,' and `arguing' all have the stem of `argu,' even though argu is not the true linguistic stem, or a real word.
-We used the standard Porter stemmer to implement this (\citeauthor{Porter, M.}).
+We used the standard Porter stemmer to implement this (\citeauthor{porter_1980}).
 In some cases, stemming proved to increase our accuracy.
@@
 In the second, we lowercase any text that is not in all caps.
-This serves to retain acronyms and any text specifically place in all caps, while combining words capitalized because of sentence boundaries with their lowercase appearances, for instance.
+This serves to retain acronyms and any text specifically placed in all caps, while combining words capitalized because of sentence boundaries with their lowercase appearances, for instance.
 In the third approach, we change all remaining tokens to lowercase, except for leaving the case of all strings containing `apple' (case insensitive) alone.
@@
 \section{Experimental Setup}
-In order to determine which combination of preprocessing steps would results in the highest performance, we built a custom evaluation platform that iterates through all possible valid combinations of pipes and evaluates their performance.
+In order to determine which combination of preprocessing steps would result in the highest performance, we built a custom evaluation platform that iterates through all possible valid combinations of pipes and evaluates their performance.
 This led to nearly one hundred combinations, as each of the six tokenizer variations was run with and without bigramming, with and without stemming, etc.

### 2012-12-07 paper/paper.tex
Updated paper

@@
 [INSERT LIST OF KEYWORDS]...\\
+"apple", "itunes", "ipad", "ipod", "mac", "ios", "iphone", "AAPL", "cupertino", "safari", "ilife", "iwork", "garageband", "ibook", "powerbook", "itouch", "app store", "macworld", "facetime", "icloud", "mobileme", "siri", "imovie", "iphoto", "quicktime", "logic pro", "think different" \\
 
@@
 Our intention was to reduce the noise in the feature set by eliminating common misspellings.
-This did not provide any statistically significant change in our results.
-\\
 ~\\
@@
 \centering
-\includegraphics[height=7cm]{chart}
-\caption{Accuracy vs. Training Corpus Size for All Text Processing Combinations}
-\label{fig:chart}
+\includegraphics[height=7cm]{img/all-with-headings}
+\caption{Metrics for all Pipeline combinations, training set sizes 50 through 1500 instances}
+\label{fig:chart_all}
 \end{figure*}
@@
 
-\section{Results}
+\section{Experimental Findings}
+
+Our desired result was a high precision classifier that could be useful gathering a large number of tweets mentioning a company or its products.
+Looking at an overview of the results in Figure~\ref{fig:chart_all}, we can see all Pipeline combinations had over 70\% of ``apple'' labelings correct with only 50 training tweet instances.
+However, given that a baseline strategy of labeling every tweet as ``apple'' would be correct 64\% of the time, this is only an improvement of approximately 9\% in the worst case.
+The more relevant and interesting result is the 43\% improvement from the baseline seen at
+
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|r|}
+	\hline
+	Pipeline Description & Apple Precision \\ \hline
+	Twitter Tokenizer, Lowercased, Stemmed, \\ Stopwords Removed, Bigrams & 0.9224489796 \\ \hline
+	% TODO FIIIIIIIX
+	[Input2CharSequence, UnescapeHTML, CharSequenceLowercase, default twitter tokenizer, TokenSequenceRemoveStopwords, NGRAM2, TokenSequence2FeatureSequence, Target2Label, FeatureSequence2FeatureVector] & 0.9159663866 \\ \hline
+	[Input2CharSequence, UnescapeHTML, default twitter tokenizer, TokenSequenceRemoveStopwords, Stemmed, NGRAM2, TokenSequence2FeatureSequence, Target2Label, FeatureSequence2FeatureVector] & 0.9156626506 \\ \hline
+	[Input2CharSequence, UnescapeHTML, default twitter tokenizer, Stemmed, NGRAM2, TokenSequence2FeatureSequence, Target2Label, FeatureSequence2FeatureVector] & 0.9138576779 \\ \hline
+	[Input2CharSequence, UnescapeHTML, default twitter tokenizer, TokenSequenceRemoveStopwords, NGRAM2, TokenSequence2FeatureSequence, Target2Label, FeatureSequence2FeatureVector] & 0.9135802469 \\
+	\hline
+\end{tabular}
+\caption{Top performing Pipeline combinations for 1500 training instances}
+\label{tab:top_pipelines}
+\end{table}
+
+Intro
+
 Using whitespace-based tokenization with a Naive Bayes classifier, we achieve a baseline accuracy of 76\% %correct this exactly!
@@
   Include most useful features for classification
+
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	Cool ranch , 4 berry sundae , apple juice \textbf{\#yessuh} \\ 
+	\textbf{\#latenight \#snack} http://t.co/ttc3vujp \\ \hline
+	I just poured apple juice on my cereal\textbf{..} Gah. \textbf{\#SoTired} \\ \hline
+	I hate Siri\textbf{.. -\_\_\_-} \\
+	\hline
+\end{tabular}
+\caption{Examples of difficult tokenizations}
+\label{tab:tokenization_examples}
+\end{table}
+
+\subsection{Pipe Breakdown}
+
+\textit{Stopword removal}:
+\textit{Bigrams}:
+\textit{URL Replacement}:
+~\\
+\textit{Spell checking}: Correcting misspelled words provided no statistically significant change in our results. \\
+
+\subsection{}
 

### 2012-12-07 classify/src/main/java/common/PipeFactory.java
pipe updates

@@ -33,14 +33,22 @@ public class PipeFactory {
 						labels.toString());
 			}
 
-		}.add(new SetFactory<Pipe>(true) {
+		}.appendSingle(new SetFactory<Pipe>() {
 			@Override
 			protected void build() {
-//				this.add(new Input2CharSequence("UTF-8"), "Input2CharSequence");
-				this.add(new UnescapeHTML(), "UnescapeHTML");
-//				this.add(new CharSequenceLowercase(), "CharSequenceLowercase");
+				this.add(new Input2CharSequence("UTF-8"), "Input2CharSequence");
 			}
-		}).add(new SetFactory<Pipe>(true) {
+		}).appendSingle(new SetFactory<Pipe>() {
+			@Override
+			protected void build() {
+				this.add(new UnescapeHTML(), "UnescapeHTML");
+			}
+		}).appendAny(new SetFactory<Pipe>() {
+			@Override
+			protected void build() {
+				this.add(new CharSequenceLowercase(), "CharSequenceLowercase");
+			}
+		}).appendSingle(new SetFactory<Pipe>() {
 			@Override
 			protected void build() {
 				this.add(
@@ -59,7 +67,7 @@ public class PipeFactory {
 				this.add(new Tokenizer(false), "default twitter tokenizer");
 			}
 
-		}).add(new SetFactory<Pipe>() {
+		}).appendAny(new SetFactory<Pipe>() {
 			@Override
 			protected void build() {
 				this.add(new TokenSequenceRemoveStopwords(),
@@ -67,26 +75,26 @@ public class PipeFactory {
 				this.add(new Stemmer(), "Stemmed");
 			}
 
-		}).add(new SetFactory<Pipe>(true) {
+		}).appendSingle(new SetFactory<Pipe>() {
 			@Override
 			protected void build() {
 				this.add(new Noop(), "NGRAM1");
 				this.add(new TokenSequenceNGrams(new int[] {1, 2}), "NGRAM2");
 			}
 
-		}).add(new SetFactory<Pipe>(true) {
+		}).appendSingle(new SetFactory<Pipe>() {
 			@Override
 			protected void build() {
 				this.add(new TokenSequence2FeatureSequence(),
 						"TokenSequence2FeatureSequence");
 			}
-		}).add(new SetFactory<Pipe>(true) {
+		}).appendSingle(new SetFactory<Pipe>() {
 			@Override
 			protected void build() {
[…]

### 2012-12-07 classify/src/main/java/common/SetFactory.java

@@ -5,16 +5,6 @@ import java.util.List;
 
 public abstract class SetFactory<T> {
 
-	private boolean single;
-
-	public SetFactory() {
-		this(false);
-	}
-
-	public SetFactory(boolean single) {
-		this.single = single;
-	}
-
 	private List<SetItem<T>> retCache;
 
 	public List<SetItem<T>> produce() {
@@ -27,9 +17,5 @@ public abstract class SetFactory<T> {
 
 	protected void add(T thing, String label) {
 		retCache.add(new SetItem<T>(thing, label));
-	}
-
-	public boolean isSingle() {
-		return single;
 	}
 }

### 2012-12-07 paper/paper.tex
added failing paper
paper
paper updates

@@
 \caption{Hashtags and username references (note that Apple Inc. does not own the handle @Apple, though it is commonly used this way)}
-\label{tab:myfirsttable}
+\label{tab:hashtag_username}
 \end{table}
@@
 \caption{Examples of emoticons and common abbreviations found on Twitter}
-\label{tab:myfirsttable}
+\label{tab:emoticons}
 \end{table}
@@
 Pak and Paroubek also noted the need to handle URLs in tweets, however, rather than adding any new text, they chose to remove the link entirely  (\citeauthor{PAK10.385}).
+\\
 ~\\
@@
 \centering
-\includegraphics[height=7cm]{img/all-with-headings}
+\includegraphics[width=\textwidth]{img/all-with-headings}
 \caption{Metrics for all Pipeline combinations, training set sizes 50 through 1500 instances}
@@
 To best observe the effects of training set size, training sizes of 50 to 1500 were tested in increments of 50, where each set is a superset of the previous set with 50 new randomly chosen instances, as opposed to using n-fold cross validation, which would not display this characteristic evenly across varied training and testing sizes.
+\\
+
 To evaluate this large set of results, we have chosen three relevant evaluation metrics.
@@
 However, given that a baseline strategy of labeling every tweet as ``apple'' would be correct 64\% of the time, this is only an improvement of approximately 9\% in the worst case.
-The more relevant and interesting result is the 43\% improvement from the baseline seen at
+The more relevant and interesting result is the 43\% improvement from the baseline seen with our custom Twitter Tokenizer and all other Pipes like Lowsercasing, Stemming and Bigrams trained on the maximum of 1500 instances.
+This relatively large improvement indicates not only is the tokenization strategy used important, but also that we were relatively successful in creating an effective tokenizer that can be further augmented by standard natural language processing techniques like stemming, removing stop words, applying n-grams, or simply lowercasing the text.
+See in Table \ref{tab:top_pipelines} below that all of top five Pipeline combinations include our twitter tokenizer.
+In fact, one must go down to the 24th and 33rd ranked combinations to find ones that include the Number-Digit and Whitespace based tokenizers respectively.
 
@@
 \centering
-\begin{tabular}{|l|r|}
+\small
+\begin{tabular}{|c|l|r|}
 	\hline
-	Pipeline Description & Apple Precision \\ \hline
-	Twitter Tokenizer, Lowercased, Stemmed, \\ Stopwords Removed, Bigrams & 0.9224489796 \\ \hline
+	\textit{Rank} & \textit{Pipeline Description} & \textit{Precision} \\
+	& & \textit{for Apple} \\ \hline
+	1 & Twitter Tokenizer, Lowercased, & \\ & Stemmed, Stopwords Removed, Bigrams & 92.2\% \\ \hline
 	% TODO FIIIIIIIX
-	[Input2CharSequence, UnescapeHTML, CharSequenceLowercase, default twitter tokenizer, TokenSequenceRemoveStopwords, NGRAM2, TokenSequence2FeatureSequence, Target2Label, FeatureSequence2FeatureVector] & 0.9159663866 \\ \hline
-	[Input2CharSequence, UnescapeHTML, default twitter tokenizer, TokenSequenceRemoveStopwords, Stemmed, NGRAM2, TokenSequence2FeatureSequence, Target2Label, FeatureSequence2FeatureVector] & 0.9156626506 \\ \hline
-	[Input2CharSequence, UnescapeHTML, default twitter tokenizer, Stemmed, NGRAM2, TokenSequence2FeatureSequence, Target2Label, FeatureSequence2FeatureVector] & 0.9138576779 \\ \hline
-	[Input2CharSequence, UnescapeHTML, default twitter tokenizer, TokenSequenceRemoveStopwords, NGRAM2, TokenSequence2FeatureSequence, Target2Label, FeatureSequence2FeatureVector] & 0.9135802469 \\
+	2 & Twitter Tokenizer, Lowercased, & \\ & Stopwords Removed, Bigrams & 91.6\% \\ \hline
+	3 & Twitter Tokenizer, Stopwords Removed, & \\ & Stemmed, Bigrams & 91.6\% \\ \hline
+	4 & Twitter Tokenizer, Stemmed, Bigrams & 91.4\% \\ \hline
+	5 & Twitter Tokenizer, Stopwords Removed, & \\ & Bigrams & 91.3\% \\ \hline
 	\hline
+	24 & Number-Digit Tokenizer, & \\ & Remove Stopwords, Bigrams & 88.2\%
+ \\ \hline
+	\hline
+	33 & Whitespace Tokenizer, Stemmed, & \\ & Remove Stopwords, Bigrams & 87.7\% \\ \hline
+
 \end{tabular}
@@
 
-\begin{table}[h]
-\centering
-\begin{tabular}{|l|}
-	\hline
-	Cool ranch , 4 berry sundae , apple juice \textbf{\#yessuh} \\ 
-	\textbf{\#latenight \#snack} http://t.co/ttc3vujp \\ \hline
-	I just poured apple juice on my cereal\textbf{..} Gah. \textbf{\#SoTired} \\ \hline
-	I hate Siri\textbf{.. -\_\_\_-} \\
-	\hline
-\end{tabular}
-\caption{Examples of difficult tokenizations}
-\label{tab:tokenization_examples}
-\end{table}
+\subsection{Pipe Effectiveness Breakdown}
 
-\subsection{Pipe Breakdown}
-
-\textit{Stopword removal}:
-\textit{Bigrams}:
-\textit{URL Replacement}:
+\textit{Stopword removal}: \\
+~\\
+\textit{Bigrams}: \\
+~\\
+\textit{URL Replacement}: \\
 ~\\
@@
 \end{figure}
+
+\begin{table}[h]
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+        Apple  & i     & Apple     & apple        \\
+        iphone & apple & iphone    & Apple        \\ 
+        i      & the   & ...       & ...          \\ 
+        the    & Apple & ipad      & mac          \\ 
+        to     & and   & ipod      & juice        \\ 
+        my     & to    & rt        & rt           \\ 
+        a      & a     & \#apple    & post        \\ 
+        ...    & ...   & 5         & new\_post    \\ 
+        on     & for   & iphone\_5  & iphone      \\ 
+        for    & new   & my\_iphone & apple\_juice\\
+      \hline
+    \end{tabular}
+\end{table}
 

### 2012-12-07 paper/paper.tex
Fixed keyword table

@@
 	\hline
-	24 & Number-Digit Tokenizer, & \\ & Remove Stopwords, Bigrams & 88.2\%
- \\ \hline
+	24 & Number-Digit Tokenizer, & \\ & Remove Stopwords, Bigrams & 88.2\% \\ \hline
 	\hline
@@
         on     & for   & iphone\_5  & iphone      \\ 
-        for    & new   & my\_iphone & apple\_juice\\
-      \hline
+        for    & new   & my\_iphone & apple\_juice \\ \hline
 \end{tabular}

### 2012-12-07 paper/paper.tex
working draft
working table

@@
 
-\begin{table}[h]
-\begin{tabular}{|l|l|l|l|}
+\begin{table*}[ht]
+\centering
+%\small
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|}
 \hline
-        Apple  & i     & Apple     & apple        \\
-        iphone & apple & iphone    & Apple        \\ 
-        i      & the   & ...       & ...          \\ 
-        the    & Apple & ipad      & mac          \\ 
-        to     & and   & ipod      & juice        \\ 
-        my     & to    & rt        & rt           \\ 
-        a      & a     & \#apple    & post        \\ 
-        ...    & ...   & 5         & new\_post    \\ 
-        on     & for   & iphone\_5  & iphone      \\ 
-        for    & new   & my\_iphone & apple\_juice \\ \hline
+\multicolumn{4}{|c|}{\textbf{Twitter-aware tokenizer}} & \multicolumn{4}{|c|}{\textbf{alphanumeric\_ tokenizer}} & \multicolumn{4}{|c|}{\textbf{whitespace tokenizer}} \\
+\hline
+\multicolumn{2}{|c|}{\textbf{no removal}} & \multicolumn{2}{|c|}{\textbf{stopword removal}} &\multicolumn{2}{|c|}{\textbf{no removal}} & \multicolumn{2}{|c|}{\textbf{stopword removal}} &\multicolumn{2}{|c|}{\textbf{no removal}} & \multicolumn{2}{|c|}{\textbf{stopword removal}}\\
+\hline
+\textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} \\ \hline
+  Apple  & i     & Apple      & apple        & t        & t     & Apple  & http   & Apple  & apple & Apple   & apple  \\
+  iphone & apple & iphone     & Apple        & co       & co    & http   & apple  & to     & I     & iPhone  & Apple  \\
+  i      & the   & ...        & ...          & Apple    & http  & iPhone & Apple  & I      & the   & -       & -      \\
+  the    & Apple & ipad       & mac          & http     & I     & iPad   & Mac    & the    & Apple & RT      & Mac    \\
+  to     & and   & ipod       & juice        & I        & apple & RT     & ED     & my     & to    & iPad    & RT     \\ 
+  my     & to    & rt         & rt           & to       & Apple & apple  & juice  & a      & and   & iPod    & juice  \\
+  a      & a     & \#apple    & post         & the      & the   & iPod   & RT     & iPhone & a     & 5       & \&     \\
+  ...    & ...   & 5          & new\_post    & iPhone   & to    & 5      & iPhone & for    & for   & iphone  & iPhone \\
+  on     & for   & iphone\_5  & iphone       & my       & and   & iphone & post   & on     & -     & apple   & post:  \\
+  for    & new   & my\_iphone & apple\_juice & a        & a     & ED     & A0     & and    & my    & \#apple & I'm    \\ \hline
 \end{tabular}
-\end{table}
+\caption{Ten most common features for various pipelines.}
+\end{table*}
+
+This table of most common features for various pipelines shows the large effect that preprocessing steps like stopword removal, capitalization normalization, bigramming, and tokenization have on the feature distribution.
+It is interesting that `...' appears as a very common feature using our Twitter-aware tokenizer.
 

### 2012-12-07 paper/paper.tex
paper updates

@@
 
-[INSERT LIST OF KEYWORDS]...\\
-"apple", "itunes", "ipad", "ipod", "mac", "ios", "iphone", "AAPL", "cupertino", "safari", "ilife", "iwork", "garageband", "ibook", "powerbook", "itouch", "app store", "macworld", "facetime", "icloud", "mobileme", "siri", "imovie", "iphoto", "quicktime", "logic pro", "think different" \\
+\begin{tabular}{l l l}
+apple & itunes & ipad \\
+ipod & mac & ios \\
+iphone & AAPL & cupertino \\
+safari&ilife&iwork \\
+garageband&ibook&powerbook \\
+itouch&app store&macworld \\
+facetime&icloud&mobileme \\
+siri&imovie&iphoto \\
+quicktime&logic pro&think different
+\end{tabular} \\
+~\\
 
@@
 
-\begin{figure*}[t!]
-\centering
-\includegraphics[width=\textwidth]{img/all-with-headings}
-\caption{Metrics for all Pipeline combinations, training set sizes 50 through 1500 instances}
-\label{fig:chart_all}
-\end{figure*}
-
 \subsubsection{Tokenization}
@@
 To evaluate this large set of results, we have chosen three relevant evaluation metrics.
-The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label (`apple' or `none' in our case).
+The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label (``apple'' or ``none'' in our case).
 Higher values for this metric mean fewer false positives for the desired company, which is the overall goal in this classification task.
@@
 Finally we use the F1 metric, a standard combination of precision and recall that is useful in determining overall if some pipeline combination is better than another in both precision and recall.
+
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=\textwidth]{img/all-with-headings}
+\caption{Metrics for all Pipeline combinations, training set sizes 50 through 1500 instances}
+\label{fig:chart_all}
+\end{figure*}
 
@@
 This relatively large improvement indicates not only is the tokenization strategy used important, but also that we were relatively successful in creating an effective tokenizer that can be further augmented by standard natural language processing techniques like stemming, removing stop words, applying n-grams, or simply lowercasing the text.
-See in Table \ref{tab:top_pipelines} below that all of top five Pipeline combinations include our twitter tokenizer.
+We can see in Table \ref{tab:top_pipelines} below that all of top five Pipeline combinations include our twitter tokenizer.
 In fact, one must go down to the 24th and 33rd ranked combinations to find ones that include the Number-Digit and Whitespace based tokenizers respectively.
@@
 	1 & Twitter Tokenizer, Lowercased, & \\ & Stemmed, Stopwords Removed, Bigrams & 92.2\% \\ \hline
-	% TODO FIIIIIIIX
 	2 & Twitter Tokenizer, Lowercased, & \\ & Stopwords Removed, Bigrams & 91.6\% \\ \hline
@@
 	\hline
-	24 & Number-Digit Tokenizer, & \\ & Remove Stopwords, Bigrams & 88.2\% \\ \hline
+	24 & Alphanumeric Tokenizer, & \\ & Remove Stopwords, Bigrams & 88.2\% \\ \hline
 	\hline
 	33 & Whitespace Tokenizer, Stemmed, & \\ & Remove Stopwords, Bigrams & 87.7\% \\ \hline
-
 \end{tabular}
@@
 \end{table}
-
-Intro
-
-Using whitespace-based tokenization with a Naive Bayes classifier, we achieve a baseline accuracy of 76\% %correct this exactly!
-compared to the prior probability of tweet about Apple of 64\%.
-For simplicity of analysis, we compared the results of every permutation of our pipeline steps, training on 100 through 1800 tweets in increments of 100, in order to find the combinations that exceed or violate our expectations.
-We found that our Twitter-aware tokenizer outperformed whitespace tokenization by [THIS AMOUNT].
-Applying stemming and stop word removal to both pipelines increased the accuracy for almost every case, though widening the gap.
 
@@
 
-\subsection{Pipe Effectiveness Breakdown}
+\subsection{Pipe Effectiveness}
 
+\textit{Stemming}: \\
+~\\
 \textit{Stopword removal}: \\
@@
 
-\subsection{}
+\subsection{Tokenizers}
 
-\begin{figure}[ht]
+\begin{figure}[h]
 \centering
-\includegraphics[width=\linewidth]{chart_twitterVSwhitespace}
-\caption{Accuracy With Stemming and Stopword Removal}
-\label{fig:chart_twitterwhitespace}
+\includegraphics[]{img/tokenizers}
+\caption{Precision of main tokenizers}
+\label{fig:tokenizer_precision}
 \end{figure}
 
-\begin{figure}[ht]
-\centering
-\includegraphics[width=\linewidth]{chart_twitterVSwhitespace_detailed}
-\caption{Accuracy For Twitter and Whitespace Tokenizers}
-\label{fig:chart_twitterwhitespace_detailed}
-\end{figure}
+We found that our Twitter-aware tokenizer outperformed whitespace tokenization by [THIS AMOUNT] on average across the .
+Applying stemming and stop word removal to both pipelines increased the accuracy for almost every case, though widening the gap.
+
+% \begin{figure}[ht]
+% \centering
+% \includegraphics[width=\linewidth]{chart_twitterVSwhitespace}
+% \caption{Accuracy With Stemming and Stopword Removal}
+% \label{fig:chart_twitterwhitespace}
+% \end{figure}
 
@@
   for    & new   & my\_iphone & apple\_juice & a        & a     & ED     & A0     & and    & my    & \#apple & I'm    \\ \hline
+
 \end{tabular}
@@
 
+\section{Team Contributions}
+Specific team member contributions followed from what we originally stated when the project began.
+Brandon was in charge of writing some of the Java classes that would be used by the Mallet solftware to push and pull tweets to and from the server where they were stored.
+He also wrote and researched about different Pipes that could be used by Mallet to transform the tweets being classified.
+Finally, Brandon had a hand in defining the project structure, and helped edit the project's paper and website.
+Curtis, being the resident expert in the Mallet software, was tasked with integrating it into the project.
+He also wrote the majority of the paper and did extensive work, writing Pipes to manipulate tweet data.
+Dan initally set up a server to pull tweets from Twitter so we would have a large data set to work with.
+From there he hand built a testing suite to analyze the impact each of the Pipes had on classification.
+Because of this, Dan also compiled the majority of the statistical results that came from running his test suite.
+
+We, Brandon Maxwell, Curtis Ullerich, and Daniel Stiner, hereby concur with the contents of this report, in the knowledge that it is an accurate representation of the work we did and the results we found, for our term project.
+
 \section{ Acknowledgments}

### 2012-12-07 paper/paper.tex
Added individual contributions... :O

--- 2012-12-07 paper/paper.tex
@@
 \caption{Hashtags and username references (note that Apple Inc. does not own the handle @Apple, though it is commonly used this way)}
-\label{tab:hashtag_username}
+\label{tab:myfirsttable}
 \end{table}
@@
 \caption{Examples of emoticons and common abbreviations found on Twitter}
-\label{tab:emoticons}
+\label{tab:myfirsttable}
 \end{table}
@@
 [INSERT LIST OF KEYWORDS]...\\
-"apple", "itunes", "ipad", "ipod", "mac", "ios", "iphone", "AAPL", "cupertino", "safari", "ilife", "iwork", "garageband", "ibook", "powerbook", "itouch", "app store", "macworld", "facetime", "icloud", "mobileme", "siri", "imovie", "iphoto", "quicktime", "logic pro", "think different" \\
 
@@
 Pak and Paroubek also noted the need to handle URLs in tweets, however, rather than adding any new text, they chose to remove the link entirely  (\citeauthor{PAK10.385}).
-\\
 ~\\
@@
 Our intention was to reduce the noise in the feature set by eliminating common misspellings.
+This did not provide any statistically significant change in our results.
+\\
 ~\\
@@
 \centering
-\includegraphics[width=\textwidth]{img/all-with-headings}
-\caption{Metrics for all Pipeline combinations, training set sizes 50 through 1500 instances}
-\label{fig:chart_all}
+\includegraphics[height=7cm]{chart}
+\caption{Accuracy vs. Training Corpus Size for All Text Processing Combinations}
+\label{fig:chart}
 \end{figure*}
@@
 To best observe the effects of training set size, training sizes of 50 to 1500 were tested in increments of 50, where each set is a superset of the previous set with 50 new randomly chosen instances, as opposed to using n-fold cross validation, which would not display this characteristic evenly across varied training and testing sizes.
-\\
-
 To evaluate this large set of results, we have chosen three relevant evaluation metrics.
@@
 
-\section{Experimental Findings}
-
-Our desired result was a high precision classifier that could be useful gathering a large number of tweets mentioning a company or its products.
-Looking at an overview of the results in Figure~\ref{fig:chart_all}, we can see all Pipeline combinations had over 70\% of ``apple'' labelings correct with only 50 training tweet instances.
-However, given that a baseline strategy of labeling every tweet as ``apple'' would be correct 64\% of the time, this is only an improvement of approximately 9\% in the worst case.
-The more relevant and interesting result is the 43\% improvement from the baseline seen with our custom Twitter Tokenizer and all other Pipes like Lowsercasing, Stemming and Bigrams trained on the maximum of 1500 instances.
-This relatively large improvement indicates not only is the tokenization strategy used important, but also that we were relatively successful in creating an effective tokenizer that can be further augmented by standard natural language processing techniques like stemming, removing stop words, applying n-grams, or simply lowercasing the text.
-See in Table \ref{tab:top_pipelines} below that all of top five Pipeline combinations include our twitter tokenizer.
-In fact, one must go down to the 24th and 33rd ranked combinations to find ones that include the Number-Digit and Whitespace based tokenizers respectively.
-
-\begin{table}[h]
-\centering
-\small
-\begin{tabular}{|c|l|r|}
-	\hline
-	\textit{Rank} & \textit{Pipeline Description} & \textit{Precision} \\
-	& & \textit{for Apple} \\ \hline
-	1 & Twitter Tokenizer, Lowercased, & \\ & Stemmed, Stopwords Removed, Bigrams & 92.2\% \\ \hline
-	% TODO FIIIIIIIX
-	2 & Twitter Tokenizer, Lowercased, & \\ & Stopwords Removed, Bigrams & 91.6\% \\ \hline
-	3 & Twitter Tokenizer, Stopwords Removed, & \\ & Stemmed, Bigrams & 91.6\% \\ \hline
-	4 & Twitter Tokenizer, Stemmed, Bigrams & 91.4\% \\ \hline
-	5 & Twitter Tokenizer, Stopwords Removed, & \\ & Bigrams & 91.3\% \\ \hline
-	\hline
-	24 & Number-Digit Tokenizer, & \\ & Remove Stopwords, Bigrams & 88.2\% \\ \hline
-	\hline
-	33 & Whitespace Tokenizer, Stemmed, & \\ & Remove Stopwords, Bigrams & 87.7\% \\ \hline
-
-\end{tabular}
-\caption{Top performing Pipeline combinations for 1500 training instances}
-\label{tab:top_pipelines}
-\end{table}
-
-Intro
-
+\section{Results}
 Using whitespace-based tokenization with a Naive Bayes classifier, we achieve a baseline accuracy of 76\% %correct this exactly!
@@
   Include most useful features for classification
-
-\subsection{Pipe Effectiveness Breakdown}
-
-\textit{Stopword removal}: \\
-~\\
-\textit{Bigrams}: \\
-~\\
-\textit{URL Replacement}: \\
-~\\
-\textit{Spell checking}: Correcting misspelled words provided no statistically significant change in our results. \\
-
-\subsection{}
 
@@
 \end{figure}
-
-\begin{table}[h]
-\begin{tabular}{|l|l|l|l|}
-    \hline
-        Apple  & i     & Apple     & apple        \\
-        iphone & apple & iphone    & Apple        \\ 
-        i      & the   & ...       & ...          \\ 
-        the    & Apple & ipad      & mac          \\ 
-        to     & and   & ipod      & juice        \\ 
-        my     & to    & rt        & rt           \\ 
-        a      & a     & \#apple    & post        \\ 
-        ...    & ...   & 5         & new\_post    \\ 
-        on     & for   & iphone\_5  & iphone      \\ 
-        for    & new   & my\_iphone & apple\_juice \\ \hline
-\end{tabular}
-\end{table}
 

### 2012-12-07 paper/paper.tex
paper

@@
 
-[INSERT LIST OF KEYWORDS]...\\
-"apple", "itunes", "ipad", "ipod", "mac", "ios", "iphone", "AAPL", "cupertino", "safari", "ilife", "iwork", "garageband", "ibook", "powerbook", "itouch", "app store", "macworld", "facetime", "icloud", "mobileme", "siri", "imovie", "iphoto", "quicktime", "logic pro", "think different" \\
+\quote{\textit{apple, itunes, ipad, ipod, mac, ios, iphone, AAPL, cupertino, safari, ilife, iwork, garageband, ibook, powerbook, itouch, app store, macworld, facetime, icloud, mobileme, siri, imovie, iphoto, quicktime, logic pro, think different}} \\
 
@@
 This table of most common features for various pipelines shows the large effect that preprocessing steps like stopword removal, capitalization normalization, bigramming, and tokenization have on the feature distribution.
-It is interesting that `...' appears as a very common feature using our Twitter-aware tokenizer.
+The bigrams iphone\_5 and my\_iphone prove to be useful when finding tweets about Apple and the bigrams new\_post and apple\_juice are useful when finding tweets not about Apple.
+Note the case of the word `apple' in its various forms.
+It appears most commonly as `Apple' in tweets about apple and lowercased in other tweets.
+This is expected, but there is also a high incidence of the word `Apple' in tweets not about the company.
+It is interesting that `...' appears as a very common feature using our Twitter-aware tokenizer, as well as the token `rt'.
+These appear with equal weight in tweets both about and not about Apple, so we may benefit from removal them during tokenization.\\
 
@@
 
-\section{Team Contributions}
-Specific team member contributions followed from what we originally stated when the project began.
-Brandon was in charge of writing some of the Java classes that would be used by the Mallet solftware to push and pull tweets to and from the server where they were stored.
-He also wrote and researched about different Pipes that could be used by Mallet to transform the tweets being classified.
-Finally, Brandon had a hand in defining the project structure, and helped edit the project's paper and website.
-Curtis, being the resident expert in the Mallet software, was tasked with integrating it into the project.
-He also wrote the majority of the paper and did extensive work, writing Pipes to manipulate tweet data.
-Dan initally set up a server to pull tweets from Twitter so we would have a large data set to work with.
-From there he hand built a testing suite to analyze the impact each of the Pipes had on classification.
-Because of this, Dan also compiled the majority of the statistical results that came from running his test suite.
-
-We, Brandon Maxwell, Curtis Ullerich, and Daniel Stiner, hereby concur with the contents of this report, in the knowledge that it is an accurate representation of the work we did and the results we found, for our term project.
-
 \section{ Acknowledgments}

### 2012-12-07 paper/paper.tex
paper

--- 2012-12-07 paper/paper.tex
@@
 
+\section{Individual Contributions}
+Specific team member contributions follow from what we originally stated in our project proposal.
+Brandon implemented utilities to push and pull tweets from our database in Java.
+He also researched about and wrote different Pipes that could be used by Mallet to transform the tweets during training.
+Brandon architected the project structure, and helped edit the project's paper and website.
+Curtis integrated Mallet into the project, prototyped the testing utilities, and wrote the JsonTweetIterator.
+He also wrote the majority of the paper, implemented the Twitter-aware tokenizer, and wrote bash scripts to process corpora for testing and analysis.
+Dan harvested tweets from Twitter and managed a database to store all our content.
+He designed and implemented the testing utility to compare all combinations of Pipes.
+Dan performed the statistical analysis and generated the graphs for the paper.
+
+We, Brandon Maxwell, Curtis Ullerich, and Daniel Stiner, hereby concur with the contents of this report, in the knowledge that it is an accurate representation of the work we did and the results we found, for our term project.
+
 \section{ Acknowledgments}

### 2012-12-07 paper/paper.tex

@@
 
-\quote{\textit{apple, itunes, ipad, ipod, mac, ios, iphone, AAPL, cupertino, safari, ilife, iwork, garageband, ibook, powerbook, itouch, app store, macworld, facetime, icloud, mobileme, siri, imovie, iphoto, quicktime, logic pro, think different}} \\
+%\quote{\textit{apple, itunes, ipad, ipod, mac, ios, iphone, AAPL, cupertino, safari, ilife, iwork, garageband, ibook, powerbook, itouch, app store, macworld, facetime, icloud, mobileme, siri, imovie, iphoto, quicktime, logic pro, think different}} \\
+\begin{tabular}{l l l}
+apple & itunes & ipad \\
+ipod & mac & ios \\
+iphone & AAPL & cupertino \\
+safari&ilife&iwork \\
+garageband&ibook&powerbook \\
+itouch&app store&macworld \\
+facetime&icloud&mobileme \\
+siri&imovie&iphoto \\
+quicktime&logic pro&think different
+\end{tabular} \\
+~\\
 

### 2012-12-07 paper/paper.tex
paper

@@
 \begin{quote}
-Twitter is a popular source for data mining due to its massive scale and inclusivity of current trends.
+Twitter is a popular source for data mining due to its massive scale and inclusion of current trends.
 It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products.
-Using machine learning techniques, we analyze the accuracy of classifying whether tweets directly mention a particular company or mearly contain keywords related to the company.
-%Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
+Using machine learning techniques, we analyze the accuracy of classifying whether tweets directly mention a particular company or merely contain keywords related to the company.
+Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
 %Classification purely by keyword filtering often suffers from a
@@
 The other 36\% do not, but still contain keywords related to the company.
-Preliminary results have shown significant increases in accuracy % TODO insert actual numbers
-by using domain-specific tokenizers, while surprisingly showing decreases in classification accuracy for other standard preprocessing methods such as n-grams.%maybe?
+Preliminary results have shown increases of greater than 10\% in accuracy by using Twitter-aware tokenization during preprocessing.\\
 \end{quote}
@@
 Tweets are used as a source of data mining for applications ranging from predicting future stock price changes based on user sentiment (\citeauthor{Ruiz}) and identifying characteristics of Twitter users (\citeauthor{conf/icwsm/PennacchiottiP11}) to tracking political protests and uncovering scams (\citeauthor{ICWSM101540}).
-In many cases, the problem of determining which tweets are relevant for a particular application is prerequisite to meaningful results.
+In many cases, the problem of determining which tweets are relevant for a particular application is prerequisite to obtaining meaningful results.
 Use of hashtags and username references on Twitter through syntax conventions (prepending with \# and @, respectively) can be used to select a subset of the tweets about a particular topic.
@@
 	\hline
-\textbf{Nvm} i'll buy you an ipad \textbf{\^-\^} \\ \hline
+\textbf{Nvm} i'll buy you an ipad \textbf{\^{}-\^{}} \\ \hline
 \#Apple fires `maps' project manager \textbf{loooool} big \\
@@
 
-We present a system to disambiguate tweets about the company Apple using a Naive Bayes model, increasing its baseline accuracy by 8\% through use of specialized, Twitter-aware tokenization.
+We present a system to disambiguate tweets about the company Apple using a Naive Bayes model, increasing its baseline accuracy by over 10\% through use of specialized, Twitter-aware tokenization.
 
@@
 A good deal of research has been done into sentiment classification of tweets, which requires very similar text processing and tokenization \cite{Pak10}.
-Laboreiro et al focus on the problem of tokenizing, using support vector machines (SVM) to improve upon the accuracy of rule-based tokenization, succeeded in improving from 85\% to 96\% token accuracy (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
-Yerva et al construct classifiers to disambiguate tweets containing company-related keywords, primarily using profiles containing company background knowledge (\citeauthor{journals/ijcsa/YervaMA12}).
-Sriram et al presented a system that uses features extracted from the tweet author's profile and the tweet text to classify tweets into the categories of News, Events, Opinions, Deals, and Private Messages (\citeauthor{Sriram:2010:STC:1835449.1835643}).
+Laboreiro et al.
+focus on the problem of tokenizing, using support vector machines (SVM) to improve upon the accuracy of rule-based tokenization, succeeded in improving from 85\% to 96\% token accuracy (\citeauthor{Laboreiro:2010:TMM:1871840.1871853}).
+Yerva et al.
+construct classifiers to disambiguate tweets containing company-related keywords, primarily using profiles containing company background knowledge (\citeauthor{journals/ijcsa/YervaMA12}).
+Sriram et al.
+presented a system that uses features extracted from the tweet author's profile and the tweet text to classify tweets into the categories of News, Events, Opinions, Deals, and Private Messages (\citeauthor{Sriram:2010:STC:1835449.1835643}).
 
@@
 This provides us a smaller set of features in the overall corpus, with a much higher prior confidence that each individual tweet is of interest.
-The keywords used for the company of choice during this round of testing, Apple, were collected manually from information on the company's website and the Wikipedia page about Apple:\\
+We collected the keywords we used manually from information on the company's website and the Wikipedia page about Apple:\\
 
-%\quote{\textit{apple, itunes, ipad, ipod, mac, ios, iphone, AAPL, cupertino, safari, ilife, iwork, garageband, ibook, powerbook, itouch, app store, macworld, facetime, icloud, mobileme, siri, imovie, iphoto, quicktime, logic pro, think different}} \\
 \begin{tabular}{l l l}
@@
 We make the assumption that spam will be filtered from the testing set.
-This could be done via an existing Naive Bayes classifier %[INSERT REFERENCE FOR TWEET SPAM FILTERING]
-, but we simply did not include instances of spam in our corpus during the manual labeling process.
+This could be done via an existing Naive Bayes classifier, %[INSERT REFERENCE FOR TWEET SPAM FILTERING]
+ but we simply did not include instances of spam in our corpus during the manual labeling process.
 We collected our tweets over the course of twelve hours.
@@
 
-We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set. \\
-Data sets and scripts used for processing text data are available on the project website. (http://tweets.curtisullerich.com/)\\
+We hand labeled 2000 tweets for use in training and testing, including only English-language tweets in our training set.
+Data sets and scripts used for processing text data are available on the project website.\\
+ (http://tweets.curtisullerich.com/)\\
 
@@
 We remove these words because of the high likelihood of many tweets containing these words, without contributing significant discriminatory features to the tweets.
-%TODO [REFERENCE NLP PAPER ABOUT STOPWORD REMOVAL]
 \\
@@
 \textit{URL replacement}: In our dataset, 60\% of the 100,000 tweets we collected contained a link.
-As the vast majority of these are unique, and shortened using a URL shortener, often Twitter's own t.co.
+The vast majority of these are unique, and shortened using a URL shortener, often Twitter's own t.co.
 Links, then, lose any features that may have been parsed from the URL, which often contains a domain name or title that may be useful in discriminating especially ambiguous links.
@@
 | Redmond Pie.' In cases where the title is empty, we instead replace the shortened link with the resolved URL, which is `http://www.redmondpie.com/iphone-5-vs-iphone-4s-should-you-upgrade' in this case.
-In many cases like this, there is not other way to distinguish the content of a tweet.
+In many cases like this, there is no other way to distinguish the content of a tweet.
 From our dataset of 100,000 tweets, 102 tweets contained \textit{only} a link, while 608 tweets contained only a link and fewer than 20 other characters.
@@
 While this stem does not necessarily have to be the root of the word, it should satisfy the property that related words have the same stem.
-For instance, the stem of the related words `argue,' `argued,' and `arguing' all have the stem of `argu,' even though argu is not the true linguistic stem, or a real word.
+For instance, the stem of the related words `argue,' `argued,' and `arguing' all have the stem of `argu,' even though argu is not the true linguistic stem, nor a real word.
 We used the standard Porter stemmer to implement this (\citeauthor{porter_1980}).
@@
 As presented in our results, because of irregular capitalization, two tokens likely to be semantically identical with respect to company classification may be represented in multiple cases.
-{Nooo, NOOO, nooo, NoOo} is a prime example.
+\{Nooo, NOOO, nooo, NoOo\} is a prime example.
 To alleviate this, we attempt three different approaches.
@@
 Any tokens remaining at this point during tokenization are very likely to be words in phrases.
-In order to focus the feature set, we split by whitespace and remove any non-word characters other than percent and dollar signs, stripping punctuation, quotation marks, parentheses, etc.
+In order to focus the feature set, we split by whitespace and trim any non-word characters other than percent and dollar signs from token boundaries, stripping punctuation, quotation marks, parentheses, etc.
 \\
@@
 We chose to apply bigramming to only the tokens parsed in this final step.
-Bigramming led to a statistically significant increase in our results over the same tokenization without bigramming, and even moreso over whitespace-split tokenization with or without bigramming applied.
+Bigramming led to a statistically significant increase in our results over the same tokenization without bigramming, and even moreso over whitespace-split tokenization with or without bigramming applied.\\
 
@@
 
-To evaluate this large set of results, we have chosen three relevant evaluation metrics.
+To evaluate this large set of results, we chose three relevant evaluation metrics.
 The first is precision, or the ratio of correctly labeled tweet instances to the number of instances assigned a particular label (``apple'' or ``none'' in our case).
@@
 
-Our desired result was a high precision classifier that could be useful gathering a large number of tweets mentioning a company or its products.
-Looking at an overview of the results in Figure~\ref{fig:chart_all}, we can see all Pipeline combinations had over 70\% of ``apple'' labelings correct with only 50 training tweet instances.
+Our desired result was a high precision classifier that could be useful for gathering a large number of tweets mentioning a company or its products.
+Looking at an overview of the results in Figure~\ref{fig:chart_all}, we can see all pipeline combinations had over 70\% of ``apple'' labelings correct with only 50 training tweet instances.
 However, given that a baseline strategy of labeling every tweet as ``apple'' would be correct 64\% of the time, this is only an improvement of approximately 9\% in the worst case.
-The more relevant and interesting result is the 43\% improvement from the baseline seen with our custom Twitter Tokenizer and all other Pipes like Lowsercasing, Stemming and Bigrams trained on the maximum of 1500 instances.
-This relatively large improvement indicates not only is the tokenization strategy used important, but also that we were relatively successful in creating an effective tokenizer that can be further augmented by standard natural language processing techniques like stemming, removing stop words, applying n-grams, or simply lowercasing the text.
-We can see in Table \ref{tab:top_pipelines} below that all of top five Pipeline combinations include our twitter tokenizer.
-In fact, one must go down to the 24th and 33rd ranked combinations to find ones that include the Number-Digit and Whitespace based tokenizers respectively.
+The more relevant and interesting result is the 43\% improvement in precision from the baseline seen with our custom Twitter-aware tokenizer and all other Pipes like lowercasing, Stemming and Bigrams trained on the maximum of 1500 instances.
+This relatively large improvement indicates not only if the tokenization strategy used important, but also that we were relatively successful in creating an effective tokenizer that can be further augmented by standard natural language processing techniques like stemming, removing stop words, applying n-grams, or simply lowercasing the text.
+We can see in Table \ref{tab:top_pipelines} below that all of top five pipeline combinations include our Twitter-aware tokenizer.
+In fact, one must go down to the 24th and 33rd ranked combinations to find ones that include the Number-Digit and Whitespace based tokenizers, respectively.
 
@@
 \end{tabular}
-\caption{Top performing Pipeline combinations for 1500 training instances}
+\caption{Top performing pipeline combinations for 1500 training instances}
 \label{tab:top_pipelines}
 \end{table}
-
-  select interesting improvements.
-  Need to mention the performance of each pipe!
-  graphs of both validation types
-  Include most useful features for classification
 
@@
 Applying stemming and stop word removal to both pipelines increased the accuracy for almost every case, though widening the gap.
+\\
 
@@
 \caption{Ten most common features for various pipelines.}
+\label{tab:features}
 \end{table*}
 
-This table of most common features for various pipelines shows the large effect that preprocessing steps like stopword removal, capitalization normalization, bigramming, and tokenization have on the feature distribution.
+Table~\ref{tab:features}, the most common features for various pipelines, shows the large effect that preprocessing steps like stopword removal, capitalization normalization, bigramming, and tokenization have on the feature distribution.
 The bigrams iphone\_5 and my\_iphone prove to be useful when finding tweets about Apple and the bigrams new\_post and apple\_juice are useful when finding tweets not about Apple.
@@
 
-Yerva et al demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification (\citeauthor{journals/ijcsa/YervaMA12}).
+Yerva et al.
+demonstrate a system of using background knowledge and relatedness, in which current information in the Twitter stream is used to more accurately estimate the priors for a Naive Bayes classification (\citeauthor{journals/ijcsa/YervaMA12}).
 We believe that inclusion of this in our method could allow us to perform more accurate disambiguation.\\
 
-Wang et al have shown improvements over the bag-of-words approach to text classification using Wikipedia as a thesaurus for term disambiguation.
+Wang et al.
+have shown improvements over the bag-of-words approach to text classification using Wikipedia as a thesaurus for term disambiguation.
 We could use this to enrich the feature set found in tweets and relate similar or co-occurring words in tweets (\citeauthor{Wang:2008:UWC:1510528.1511383}, \citeauthor{Wang:2009:UWK:1554488.1554492}).\\
@@
 
-Sriram et al found that utilizing author profiles provide a good method for further disambiguation of tweets into categories, as authors tend to tweet messages within a limited set of categories.
-They also delineate a set of eight features (8F) used for training, instead of using the Bag-of-Words approach as we do.
-Through further analysis of the most useful features found in our approach, we could also choose a discrete set of binary or n-ary features most relevant to this classification task and explore its accuracy versus Bag-of-Words (\citeauthor{Sriram:2010:STC:1835449.1835643}).
+Sriram et al.
+found that utilizing author profiles provides a good method for further disambiguation of tweets into categories, as authors tend to compose tweets within a limited set of categories.
+They also delineate a set of eight features (`8F') used for training, instead of using the bag-of-words approach as we do.
+Through further analysis of the most useful features found in our approach, we could also choose a discrete set of binary or n-ary features most relevant to this classification task and explore its accuracy versus bag-of-words (\citeauthor{Sriram:2010:STC:1835449.1835643}).
 
@@
 He designed and implemented the testing utility to compare all combinations of Pipes.
-Dan performed the statistical analysis and generated the graphs for the paper.
+Dan performed the statistical analysis and generated the graphs for the paper.\\
 

### 2012-12-07 classify/src/main/java/common/Constants.java
tweaked regexes

@@ -17,7 +17,7 @@ public class Constants {
 	public static final String VERIFIED_COUNTS_URL = "http://danielstiner.com:9001/verified/companies";
 
 	// Http regex
-	public static final String HTTP_REGEX = "http\\:\\/\\/([^\\s]+)";
+	public static final String HTTP_REGEX = "\\b(((ht|f)tp(s?)\\:\\/\\/|~\\/|\\/)|www.)(\\w+:\\w+@)?(([-\\w]+\\.)+(com|org|net|gov|mil|biz|info|mobi|name|aero|jobs|museum|travel|[a-z]{2}))(:[\\d]{1,5})?(((\\/([-\\w~!$+|.,=]|%[a-f\\d]{2})+)+|\\/)+|\\?|#)?((\\?([-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)(&(?:[-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)*)*(#([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)?\\b";
 
 	// Classifier constant literals
 	public static final String COMPANY_MODEL = "companyModel";

### 2012-12-07 classify/src/main/java/pipe/Stemmer.java

@@ -33,7 +33,7 @@ public class Stemmer extends Pipe {
 	public Instance pipe(Instance carrier) {
 		TokenSequence tokenSequence = (TokenSequence) carrier.getData();
 		TokenSequence stemmedTokenSequence = new TokenSequence();
-
+		System.out.println("Stemming:");
 		for (int i = 0; i < tokenSequence.size(); i++) {
 			Token token = tokenSequence.get(i);
 			stemmer.setCurrent(token.getText());
@@ -44,6 +44,8 @@ public class Stemmer extends Pipe {
 			// System.out.println(token.getText() + "   :   " + s);
 			// }
 		}
+		System.out.println(stemmedTokenSequence);
+		
 		carrier.setData(stemmedTokenSequence);
 		return carrier;
 	}

### 2012-12-07 classify/src/main/java/pipe/Tokenizer.java

@@ -19,7 +19,7 @@ public class Tokenizer extends Pipe {
 	private static final String emoticons = "([<>]?[:;=8][\\-o\\*\\']?[\\)\\]\\(\\[dDpP/\\:\\}\\{@\\|\\\\]|[\\)\\]\\(\\[dDP/\\:\\}\\{@\\|\\\\][\\-o\\*\\']?[:;=8][<>]?)";
 	private static final String usernames = "@[\\w_]+";
 	private static final String hashtags = "\\#[\\w_]+[\\w\\'_\\-]*[\\w_]+";
-	private static final String links = "\\b(((ht|f)tp(s?)\\:\\/\\/|~\\/|\\/)|www.)(\\w+:\\w+@)?(([-\\w]+\\.)+(com|org|net|gov|mil|biz|info|mobi|name|aero|jobs|museum|travel|[a-z]{2}))(:[\\d]{1,5})?(((\\/([-\\w~!$+|.,=]|%[a-f\\d]{2})+)+|\\/)+|\\?|#)?((\\?([-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)(&(?:[-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)*)*(#([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)?\\b"; // "http\\:\\/\\/.*?\\s";
+	private static final String links = "(((ht|f)tp(s?)\\:\\/\\/|~\\/|\\/)|www.)(\\w+:\\w+@)?(([-\\w]+\\.)+(com|org|net|gov|mil|biz|info|mobi|name|aero|jobs|museum|travel|[a-z]{2}))(:[\\d]{1,5})?(((\\/([-\\w~!$+|.,=]|%[a-f\\d]{2})+)+|\\/)+|\\?|#)?((\\?([-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)(&(?:[-\\w~!$+|.,*:]|%[a-f\\d{2}])+=?([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)*)*(#([-\\w~!$+|.,*:=]|%[a-f\\d]{2})*)?\\b"; // "http\\:\\/\\/.*?\\s";
 
[…]

### 2012-12-07 paper/paper.tex
paper

@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \centering
@@
 As done by \citet{potts2011} we normalize the length of all letter sequences greater than two, as in English these are invariably due to user-added emphasis, and condensing the larger set of tokens focuses the feature set.
-In the following tweet, for instance, `loooool' is normalized to `loool'.
-\begin{quote}
-\#news can't wait for my signed \#OoRITE2OutNow it's emotional here right now \textbf{loooool} \#OoRITE2OutNow https://t.co/r4n4cn6C 
-\end{quote}
+In the following tweet, for instance, `loooool' would be normalized to `loool'.
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|}
+	\hline
+	\#news can't wait for my signed \#OoRITE2OutNow it's \\ emotional here right now \textbf{loooool} \\ \#OoRITE2OutNow https://t.co/r4n4cn6C \\
+	\hline
+\end{tabular}
+\caption{Example of normalizing repeated characters}
+\label{tab:normalize_characters_example}
+\end{table}
 
@@
 Looking at an overview of the results in Figure~\ref{fig:chart_all}, we can see all pipeline combinations had over 70\% of ``apple'' labelings correct with only 50 training tweet instances.
-However, given that a baseline strategy of labeling every tweet as ``apple'' would be correct 64\% of the time, this is only an improvement of approximately 9\% in the worst case.
-The more relevant and interesting result is the 43\% improvement in precision from the baseline seen with our custom Twitter-aware tokenizer and all other Pipes like lowercasing, Stemming and Bigrams trained on the maximum of 1500 instances.
+However, given that a simple strategy of labeling every tweet as ``apple'' would be correct 64\% of the time, this is only an improvement in precision of approximately 9\%.
+The more relevant and interesting result is the 43\% improvement in precision from the simple strategy seen with our custom Twitter-aware tokenizer and all other Pipes like lowercasing, Stemming and Bigrams trained on the maximum of 1500 instances.
+Futhermore, we observed 12\% and 13\% increases in precision versus plain Whitespace and Alphanumeric based tokenizers respectively.
 This relatively large improvement indicates not only if the tokenization strategy used important, but also that we were relatively successful in creating an effective tokenizer that can be further augmented by standard natural language processing techniques like stemming, removing stop words, applying n-grams, or simply lowercasing the text.
 We can see in Table \ref{tab:top_pipelines} below that all of top five pipeline combinations include our Twitter-aware tokenizer.
-In fact, one must go down to the 24th and 33rd ranked combinations to find ones that include the Number-Digit and Whitespace based tokenizers, respectively.
+In fact, one must go down to the 24th and 33rd ranked combinations to find ones that utilize the Alphanumeric and Whitespace based tokenizers, respectively.
 
-\begin{table}[h]
+\begin{table}[ht]
 \centering
@@
 
-\subsection{Pipe Effectiveness}
+% \subsection{Pipe Effectiveness}
 
-\textit{Stemming}: \\
-~\\
-\textit{Stopword removal}: \\
-~\\
-\textit{Bigrams}: \\
-~\\
-\textit{URL Replacement}: \\
-~\\
-\textit{Spell checking}: Correcting misspelled words provided no statistically significant change in our results. \\
+% \textit{Stemming}: \\
+% ~\\
+% \textit{Stopword removal}: \\
+% ~\\
+% \textit{Bigrams}: \\
+% ~\\
+% \textit{URL Replacement}: \\
+% ~\\
+% \textit{Spell checking}: Correcting misspelled words provided no statistically significant change in our results. \\
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
@@
 
-We found that our Twitter-aware tokenizer outperformed whitespace tokenization by [THIS AMOUNT] on average across the .
-Applying stemming and stop word removal to both pipelines increased the accuracy for almost every case, though widening the gap.
-\\
+We found that our Twitter-aware tokenizer with the full suite of stemming, stopword removal and bigramming outperformed the whitespace tokenization with comparable stemming, stopword removal and bigramming by 5.2\% in the precision metric when trained on 1500 instances.
+A similar comparison applies to the alphanumeric tokenizer, our Twitter-aware tokenizer was 4.5\% more percise labeling tweets as mentioning Apple.
+Applying stemming and stop word removal to both pipelines increased each metric slightly, giving rise to the well distributed set of results seen in Figure \ref{fig:chart_all}.
+Bigramming and other pipes had some effect, but compared to the multiple percentage point increases from changing the tokenization method, they had relatively minor effects individually.
 

### 2012-12-07 classify/src/main/java/classification/Main.java
main

@@ -1,35 +1,95 @@
 package classification;
 
 import java.io.File;
+import java.io.FileWriter;
 import java.io.IOException;
 import java.util.Scanner;
 
 public class Main {
 	public static void main(String... args) throws IOException {
 
-		Scanner s = new Scanner(new File("/home/curtis/git/twittertrader/paper/allsorted"));
+		Scanner s = new Scanner(new File(
+				"/home/curtis/Dropbox/Shared Folders/apple/thenewstats2/allsorted"));
 		int i = 0;
+
+		FileWriter accuracyW = new FileWriter(new File(
+				"/home/curtis/Dropbox/Shared Folders/apple/thenewstats2/accuracy.tsv"));
+		FileWriter applePrecisionW = new FileWriter(
+				new File(
+						"/home/curtis/Dropbox/Shared Folders/apple/thenewstats2/applePrecision.tsv"));
+		FileWriter nonePrecisionW = new FileWriter(
+				new File(
+						"/home/curtis/Dropbox/Shared Folders/apple/thenewstats2/nonePrecision.tsv"));
+		FileWriter appleRecallW = new FileWriter(new File(
+				"/home/curtis/Dropbox/Shared Folders/apple/thenewstats2/appleRecal.tsv"));
+		FileWriter noneRecallW = new FileWriter(new File(
+				"/home/curtis/Dropbox/Shared Folders/apple/thenewstats2/noneRecall.tsv"));
+		FileWriter appleF1W = new FileWriter(new File(
+				"/home/curtis/Dropbox/Shared Folders/apple/thenewstats2/appleF1.tsv"));
+		FileWriter noneF1W = new FileWriter(new File(
+				"/home/curtis/Dropbox/Shared Folders/apple/thenewstats2/noneF1.tsv"));
+
 		while (s.hasNextLine()) {
 			String l = s.nextLine();
 
 			String ls[] = l.split("\t");
 			if (i == 0) {
 				System.out.print(ls[1]);
-			} 
-			
-			//Replace 2 with the index of the field you actually want. You could write them out to individual files if you want as well.
+				accuracyW.append(ls[1]);
+				applePrecisionW.append(ls[1]);
+				nonePrecisionW.append(ls[1]);
+				appleRecallW.append(ls[1]);
+				noneRecallW.append(ls[1]);
+				appleF1W.append(ls[1]);
[…]

### 2013-03-31 paper/ieee/oldpaper.tex
added ieee paper

--- 2012-12-07 paper/paper.tex
@@
 /Title (Classification of Tweets by Company)
-/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
+}
 \setcounter{secnumdepth}{0}  
@@
 \title{Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets}
-\author{
-Curtis Ullerich, Daniel Stiner, Brandon Maxwell\\
-Department of Computer Science and Engineering\\
-Iowa State University
-Ames, Iowa, USA\\
-\{curtisu,stiner,bmaxwell\}@iastate.edu\\
-}
 \maketitle

### 2013-03-31 paper/ieee/paper.tex
added ieee paper

--- 2013-03-31 paper/ieee/oldpaper.tex
@@
 \maketitle
+
+\tableofcontents
+
+\vspace{10 mm}
 \begin{abstract}
@@
 Twitter is a popular source for data mining due to its massive scale and inclusion of current trends.
-It is also a veritable goldmine of useful data for businesses seeking to discover public opinion about themselves or their products.
-Using machine learning techniques, we analyze the accuracy of classifying whether tweets directly mention a particular company or merely contain keywords related to the company.
-Tweets present interesting classification challenges due to their irregular formatting and relatively small number of features.
-%Classification purely by keyword filtering often suffers from a
-%high accuracy and low recall, or low accuracy and high recall. % Q: Daniel - What does recall mean in this context? Also, list low accuracy first I think.
-We aim to survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations.
-Our dataset consists of approximately 2,000 tweets of which 64\% directly mention the company Apple, Inc or one of its products.
-The other 36\% do not, but still contain keywords related to the company.
-Preliminary results have shown increases of greater than 10\% in accuracy by using Twitter-aware tokenization during preprocessing.\\
+It can also present a goldmine of useful data for businesses seeking to discover public opinion.
+Using machine learning techniques, we disambiguate the classification of tweets based on the presence company-specific keywords.
+Tweets present interesting classification challenges due to irregular formatting and sparsity of features.
+We survey a variety of text processing steps combined with a Naive Bayes classifier, focusing on the effects of different tokenizations.
+Preliminary results show increases of greater than 10\% in accuracy by using Twitter-aware tokenization during preprocessing.
 \end{quote}
 \end{abstract}
-
 \section{Introduction}
@@
 Data sets and scripts used for processing text data are available on the project website.\\
- (http://tweets.curtisullerich.com/)\\
+ (URL withheld per submission guidelines)\\
 
@@
 
-\section{Individual Contributions}
-Specific team member contributions follow from what we originally stated in our project proposal.
-Brandon implemented utilities to push and pull tweets from our database in Java.
-He also researched about and wrote different Pipes that could be used by Mallet to transform the tweets during training.
-Brandon architected the project structure, and helped edit the project's paper and website.
-Curtis integrated Mallet into the project, prototyped the testing utilities, and wrote the JsonTweetIterator.
-He also wrote the majority of the paper, implemented the Twitter-aware tokenizer, and wrote bash scripts to process corpora for testing and analysis.
-Dan harvested tweets from Twitter and managed a database to store all our content.
-He designed and implemented the testing utility to compare all combinations of Pipes.
-Dan performed the statistical analysis and generated the graphs for the paper.\\
-
-We, Brandon Maxwell, Curtis Ullerich, and Daniel Stiner, hereby concur with the contents of this report, in the knowledge that it is an accurate representation of the work we did and the results we found, for our term project.
-
-\section{ Acknowledgments}
-Thank you to Dr.
-Jin Tian and our class teaching assistant, Ru He, for their helpful guidance during this research project.
-We also extend our thanks to our friends for their help in manual labeling of tweets.
-
 \bibliographystyle{plainnat}
